### 2024-08-08 Codes/0_1_energy_water_merge.rmd
Initial commit. Branching out from the original repository of Energy Regulation Welfare Loss.

---
title: Match energy and water datasets
---

# Preparation

```{r}
#--- set working directory ---#
setwd("~/Dropbox/NebraskaWaterProjectsData")

#--- libraries ---#
source("~/Dropbox/R_libraries_load/library.R")

# ===================================
# Import datasets
# ===================================
#--------------------------
# Well registration
#--------------------------
# Notes:
# When subsec has four letters,
# The first two letters represent subsubseciton
# The last two letters represent subseciton

wells <- fread("./Data/WellRegistrationRaw/Reg08_26_2016_Raw/all_rrb_wells.csv") %>%
  setnames(names(.), tolower(names(.))) %>%
  filter(useid == "I") %>% # irrigation wells	only
  select( # keep the relevant variables
    wellid, twnid, rngid, rngdir, section, subsecmnemonic,
    subsecid, nrdname, swl, pwl, totaldepth, regdate, pumprate, pumpdepth, decommissiondate,
    pumpcoldia, ownerid, wellstatusid, lastname, longdd, latdd
  ) %>%
  rename(township = twnid, range = rngid, subsec = subsecmnemonic) %>%
  mutate(
    trs = paste(township, range, section, sep = "_"),
    subsection = ifelse(str_length(subsec) == 2, subsec, str_sub(subsec, 3, 4)),
    trs_s = paste(trs, subsection, sep = "_"),
    subsubsection = ifelse(str_length(subsec) == 2, NA, str_sub(subsec, 1, 2)),
    trs_ss = paste(trs_s, subsubsection, sep = "_")
  ) %>%
  arrange(township, range, section) %>%
  data.table() %>%
  .[, N_sec := .N, by = .(trs)] %>%
  .[, N_sub := .N, by = .(trs_s)] %>%
  .[, N_subsub := .N, by = .(trs_ss)]

# wells[N_sub>4,]
# wells[trs=='1_7_29',]

#++++++++++++++++
# decommission date
#++++++++++++++++
wells <- wells %>%
  mutate(
    dec_date = as.Date(decommissiondate, "%m/%d/%y"),
    dec_year = year(dec_date),
    dec_month = month(dec_date),
    inactive_not_dec = ifelse(is.na(dec_year) & wellstatusid == "X", 1, 0)
  ) %>%
  data.table()

# Notes
# There are wells that are inactive even though they have not been decommissioned
# I probably should get rid of them

#--- visualization of wells per section and subsection ---#
# ggplot(data=wells) +
# 	geom_histogram(aes(x=N_sub),color='blue',fill='white')

#--------------------------
# Water use data
#--------------------------
gw <- readRDS("./Data/Pumping/Processed/pumping.rds") %>%
  mutate(source_txt = as.character(source)) %>%
  data.table() %>%
  .[source_txt %in% c("Meter", "METER", "metered"), ] %>%
  .[, extended_id := paste(volaf, acres, year, county)] %>%
  .[, count_id := .N, by = extended_id] %>% # get rid of duplicate records
  .[count_id == 1, ]

# ===================================
# with Midwest
# ===================================
Midwest <- readRDS("./Data/Energy/Processed/Midwest.rds") %>%
  select(year, district, rate, township, range, section, subsection, subsubsection, hp, kwh) %>%
  mutate(
    trs = paste(township, range, section, sep = "_"),
    trs_s = paste(trs, subsection, sep = "_")
  ) %>%
  arrange(township, range, section, subsection, year) %>%
  data.table() %>%
  .[, N_sec := .N, by = .(trs, year)] %>%
  .[, N_sub := .N, by = .(trs_s, year)]

#--- find wells within the Midwest PPD ---#
MW_trs_ls <- Midwest[, trs] %>% unique()
wells_MW <- wells %>%
  filter(trs %in% MW_trs_ls) %>%
  data.table()

#--------------------------
# single trs-trs
#--------------------------
# pick observations that are the only record at the section level (not many)
MW_sec <- Midwest[N_sec == 1, ] %>%
  left_join(., wells_MW[N_sec == 1, ], by = "trs") %>%
  mutate(matched = ifelse(!is.na(wellid), 1, 0)) %>%
  rename(trs_s = trs_s.x) %>%
  select(
    wellid, nrdname, swl, pwl, totaldepth, trs, trs_s, year, district, rate, hp, kwh, regdate, pumprate, pumpdepth, decommissiondate,
    pumpcoldia, ownerid, wellstatusid, lastname, longdd, latdd
  ) %>%
  data.table()

# MW_sec[!is.na(wellid),]

#--------------------------
# single trs_s-trs_s
#--------------------------
# pick observations that are the only record at the subsection level
#--- the only energy record at the subsection level ---#
MW_sub <- Midwest[N_sub == 1 & N_sec > 1, ] %>%
  left_join(., wells_MW[N_sub == 1 & N_sec > 1, ], by = "trs_s") %>%
  mutate(matched = ifelse(!is.na(wellid), 1, 0)) %>%
  rename(trs = trs.x) %>%
  select(
    wellid, nrdname, swl, pwl, totaldepth, trs, trs_s, year, district, rate, hp, kwh, regdate, pumprate, pumpdepth, decommissiondate,
    pumpcoldia, ownerid, wellstatusid, lastname, longdd, latdd
  ) %>%
  data.table()

# matched_sub <- MW_sub[!is.na(wellid),]
# unmatched_sub <- MW_sub[is.na(wellid),]

#--------------------------
# merge with pumping data
#--------------------------
# only MW_sub and MW_sec for now. later add MW_sub_2
MW_we <- rbind(MW_sec, MW_sub) %>%
  left_join(gw, ., by = c("wellid", "year")) %>%
  filter(!is.na(district)) %>%
  data.table()

#--------------------------
# Matching accuracy check
#--------------------------
MW_we <- MW_we %>%
  .[, w_to_e := volaf * 12 / kwh] %>%
  .[is.infinite(w_to_e), w_to_e := NA] %>%
  .[, coef_var := var(w_to_e, na.rm = TRUE) / mean(w_to_e, na.rm = TRUE), by = .(wellid)]

well_ls <- MW_we[, wellid] %>% unique()
well_len <- length(well_ls)

#--- visualization ---#
# for (i in 1:well_len){
# 	temp_data <- MW_we[wellid==well_ls[i],]
# 	temp_cv <- temp_data[,coef_var*1e5] %>%
# 		unique() %>%
# 		round(3)
# 	ggplot(data=temp_data) +
# 		geom_line(aes(y=w_to_e,x=year)) +
# 		ylim(0,0.1) +
# 		annotate('text',label=paste('Coef Var = ',temp_cv,sep=''),y=0.075,x=temp_data[,mean(year)])
# 	ggsave(paste('./Graphs/w_to_e/Midwest/consistency_',well_ls[i],'.pdf',sep=''))
# }

# Notes:
# According to visual inspections, coef_var<7e-4 seems acceptable
MW_matched_1st <- MW_we[coef_var < 7e-4, ] %>%
  select(
    wellid, nrdname, swl, pwl, totaldepth, year, acres, volaf, source, source_txt,
    trs, trs_s, district, rate, hp, kwh, regdate, pumprate, pumpdepth,
    decommissiondate, pumpcoldia, ownerid, wellstatusid,
    lastname, longdd, latdd, w_to_e, coef_var
  ) %>%
  data.table()

#--------------------------
# multiple wells and multiple energy records in the same trs
#--------------------------
matched_well_ls <- MW_matched_1st[, wellid] %>% unique()
matched_trs_s_ls <- MW_matched_1st[, trs_s] %>% unique()

wells_2nd <- wells_MW[!(wellid %in% matched_well_ls), ]
e_2nd <- Midwest[!(trs_s %in% matched_trs_s_ls), ]

temp_match_2nd <- e_2nd[N_sub == 1, ] %>%
  left_join(., wells_2nd, by = "trs") %>%
  left_join(., gw, by = c("wellid", "year")) %>%
  mutate(matched = ifelse(!is.na(wellid), 1, 0)) %>%
  filter(matched == 1) %>%
  rename(trs_s = trs_s.x) %>%
  select(
    wellid, nrdname, swl, pwl, totaldepth, trs, trs_s, year, volaf, acres, source_txt, source, hp,
    kwh, regdate, pumprate, pumpdepth, decommissiondate, district, rate,
    pumpcoldia, ownerid, wellstatusid, lastname, longdd, latdd, matched
  ) %>%
  mutate(well_trs_s = paste(wellid, trs_s, sep = "_")) %>%
  mutate(w_to_e = volaf * 12 / kwh) %>%
  filter(!is.na(volaf)) %>%
  arrange(well_trs_s, year) %>%
  data.table() %>%
  .[is.infinite(w_to_e), w_to_e := NA] %>%
  .[, coef_var := var(w_to_e, na.rm = TRUE) / mean(w_to_e, na.rm = TRUE), by = .(well_trs_s)]

#--- list of the trs ---#
trs_ls <- temp_match_2nd[, trs] %>% unique()
trs_len <- length(trs_ls)

#++++++++++++++++
# loop over trs to find matches
#++++++++++++++++
matched_store_all <- list()

for (i in 1:trs_len) { # loop over trs
  #--- select well-energy records combinations in the temporary trs ---#
  temp_match <- temp_match_2nd[trs == trs_ls[i] & !is.na(coef_var), .(well_trs_s, wellid, trs_s, coef_var)] %>%
    unique(by = "well_trs_s")
  well_len <- temp_match[, wellid] %>%
    unique() %>%
    length()

  matched_store_i <- list()
  for (j in 1:well_len) { # loop over wells
    if (min(temp_match[, coef_var]) < 7e-4) { # if there is a match
      #--- identify the best matching well-energy combination ---#
      min_index <- which.min(temp_match[, coef_var])
      get_well <- temp_match[min_index, wellid]
      get_trs_s <- temp_match[min_index, trs_s]

      #--- extract the matched data and store in the temporary storage ---#
      matched_store_i[[j]] <- temp_match_2nd %>%
        filter(wellid == get_well & trs_s == get_trs_s) %>%
        data.table()

      #--- exclude the matched wellid and energy records  ---#
      temp_match <- temp_match %>%
        filter(!(wellid == get_well | trs_s == get_trs_s)) %>%
        data.table()
    } else { # if no good enough matches
      break # end the loop
    }
  }
  matched_store_all[[i]] <- rbindlist(matched_store_i)
}

MW_matched_2nd <- rbindlist(matched_store_all) %>%
  select(
    wellid, nrdname, swl, pwl, totaldepth, year, acres, volaf, source, source_txt,
    trs, trs_s, district, rate, hp, kwh, regdate, pumprate, pumpdepth,
    decommissiondate, pumpcoldia, ownerid, wellstatusid,
    lastname, longdd, latdd, w_to_e, coef_var
  ) %>%
  data.table()

# ggplot(data=temp_match_2nd[trs==trs_ls[i],]) +
# 	geom_line(aes(y=w_to_e,x=year,color=trs_s)) +
# 	geom_point(aes(y=w_to_e,x=year,color=trs_s)) +
# 	facet_wrap(~wellid,nrow=3) +
# 	ylim(0,0.1) +
# 	theme(
# 		legend.position = 'bottom'
# 		)

#--------------------------
# combine the 1st and 2nd matches and save
#--------------------------
MW_we <- rbind(MW_matched_1st, MW_matched_2nd) %>%
  .[, hours := kwh / (hp * 0.746)] %>%
  .[, gpm := (volaf * 12 * 27154) / (hours * 60)]

saveRDS(MW_we, "./Data/Water_Energy/MW_energy_water.rds")

# ggplot(data=MW_we[w_to_e>0.008 & pwl <500,]) +
# 	geom_point(aes(y=1/w_to_e,x=pumpdepth),size=0.4) +
# 	geom_smooth(aes(y=1/w_to_e,x=pumpdepth))

# ggplot(data=MW_we[w_to_e>0.008 & pwl <500,]) +
# 	geom_point(aes(y=gpm,x=pumprate),size=0.4)

# ggplot(data=MW_we[w_to_e>0.008 & pwl <500,]) +
# 	geom_point(aes(y=gpm,x=hours),size=0.4)

# ggplot(data=MW_we[w_to_e>0.008 & pwl <500,]) +
# 	geom_point(aes(y=1/w_to_e,x=pwl),size=0.4) +
# 	geom_smooth(aes(y=1/w_to_e,x=pwl)) +
# 	xlab('Pumping Water Level (feet)') +
# 	ylab('Energy Use Efficiency (kwh/acre-inch)')

# ggplot(data=MW_we[w_to_e>0.008,]) +
# 	geom_point(aes(y=gpm,x=hp),size=0.4) +
# 	geom_smooth(aes(y=gpm,x=hp))

ggplot(data = MW_we[w_to_e > 0.008, ]) +
  geom_boxplot(aes(y = gpm, x = factor(year)))

# ggplot(data=MW_we[w_to_e>0.008,]) +
# 	geom_density(aes(x=gpm)) +
# 	facet_wrap(~year,nrow=3)

# ===================================
# with McCook
# ===================================
# 2010 data not reliable (too small numbers of kwh)
#--- import energy data ---#
McCook <- readRDS("./Data/Energy/Raw/McCook/Processed/McCook.rds") %>%
  select(year, district, township, range, section, subsection, subsubsection, hp, kwh) %>%
  filter(year != 2010) %>%
  mutate(
    trs = paste(township, range, section, sep = "_"),
    trs_s = paste(trs, subsection, sep = "_"),
    trs_ss = paste(trs_s, subsubsection, sep = "_")
  ) %>%
  arrange(township, range, section, subsection, subsubsection, year) %>%
  data.table() %>%
  .[, N_sec := .N, by = .(trs, year)] %>%
  .[, N_sub := .N, by = .(trs_s, year)] %>%
  .[, N_subsub := .N, by = .(trs_ss, year)]

#--- find wells within the McCook PPD ---#
MC_trs_ls <- McCook[, trs] %>% unique()
wells_MC <- wells %>%
  filter(trs %in% MC_trs_ls) %>%
  data.table()

#--------------------------
# single trs-trs
#--------------------------
# pick observations that are the only record at the section level (not many)
MC_sec <- McCook[N_sec == 1, ] %>%
  left_join(., wells_MC[N_sec == 1, ], by = "trs") %>%
  rename(trs_s = trs_s.x, trs_ss = trs_ss.x) %>%
  mutate(matched = ifelse(!is.na(wellid), 1, 0)) %>%
  select(
    wellid, nrdname, swl, pwl, totaldepth, trs, trs_s, trs_ss, year, district, hp, kwh, regdate, pumprate, pumpdepth, decommissiondate,
    pumpcoldia, ownerid, wellstatusid, lastname, longdd, latdd, matched
  ) %>%
  data.table()

# MC_sec[matched==1,]

#--------------------------
# single trs_s-trs_s
#--------------------------
# pick observations that are the only record at the subsection level
MC_sub <- McCook[N_sub == 1 & N_sec > 1, ] %>%
  left_join(., wells_MC[N_sub == 1 & N_sec > 1, ], by = "trs_s") %>%
  rename(trs = trs.x, trs_ss = trs_ss.x) %>%
  mutate(matched = ifelse(!is.na(wellid), 1, 0)) %>%
  select(
    wellid, nrdname, swl, pwl, totaldepth, trs, trs_s, trs_ss, year, district, hp, kwh, regdate, pumprate, pumpdepth, decommissiondate,
    pumpcoldia, ownerid, wellstatusid, lastname, longdd, latdd, matched
  ) %>%
  data.table()

# MC_sub[matched==1,]

#--------------------------
# single trs_ss-trs_ss
#--------------------------
# pick observations that are the only record at the subsubsection level
MC_subsub <- McCook[N_subsub == 1 & N_sub > 1, ] %>%
  left_join(., wells_MC[N_subsub == 1 & N_sub > 1, ], by = "trs_ss") %>%
  rename(trs = trs.x, trs_s = trs_s.x) %>%
  mutate(matched = ifelse(!is.na(wellid), 1, 0)) %>%
  select(
    wellid, nrdname, swl, pwl, totaldepth, trs, trs_s, trs_ss, year, district, hp, kwh, regdate, pumprate, pumpdepth, decommissiondate,
    pumpcoldia, ownerid, wellstatusid, lastname, longdd, latdd, matched
  ) %>%
  data.table()

# MC_subsub[matched==1,]

#--------------------------
# Merge
#--------------------------
MC_we <- rbind(MC_sec, MC_sub, MC_subsub) %>%
  filter(matched == 1) %>%
  left_join(gw, ., by = c("wellid", "year")) %>%
  filter(!is.na(district)) %>%
  data.table()

#--------------------------
# Matching accuracy check
#--------------------------
MC_we <- MC_we %>%
  .[, w_to_e := volaf * 12 / kwh] %>%
  .[is.infinite(w_to_e), w_to_e := NA] %>%
  .[, coef_var := var(w_to_e, na.rm = TRUE) / mean(w_to_e, na.rm = TRUE), by = .(wellid)]

# #--- visualization ---#
# well_ls <- MC_we[,wellid] %>% unique()
# well_len <- length(well_ls)
# for (i in 1:well_len){
# 	temp_data <- MC_we[wellid==well_ls[i],]
# 	temp_cv <- temp_data[,coef_var*1e5] %>%
# 		unique() %>%
# 		round(3)
# 	ggplot(data=temp_data) +
# 		geom_line(aes(y=w_to_e,x=year)) +
# 		ylim(0,0.1) +
# 		annotate('text',label=paste('Coef Var = ',temp_cv,sep=''),y=0.075,x=temp_data[,mean(year)])
# 	ggsave(paste('./Graphs/w_to_e/McCook/consistency_',well_ls[i],'.pdf',sep=''))
# }

# Notes:
# According to visual inspections, coef_var<7e-4 seems acceptable
MC_matched_1st <- MC_we[coef_var < 7e-4, ] %>%
  select(
    wellid, nrdname, swl, pwl, totaldepth, year, acres, volaf, source, source_txt,
    trs, trs_s, trs_ss, district, hp, kwh, regdate, pumprate, pumpdepth,
    decommissiondate, pumpcoldia, ownerid, wellstatusid,
    lastname, longdd, latdd, w_to_e, coef_var
  ) %>%
  data.table()

#--------------------------
# multiple wells and multiple energy records in the same trs
#--------------------------
matched_well_ls <- MC_matched_1st[, wellid] %>% unique()
matched_trs_ss_ls <- MC_matched_1st[, trs_ss] %>% unique()

wells_2nd <- wells_MC[!(wellid %in% matched_well_ls), ]
e_2nd <- McCook[!(trs_s %in% matched_trs_ss_ls), ]

temp_match_2nd <- e_2nd[N_sub == 1, ] %>%
  left_join(., wells_2nd, by = "trs") %>%
  left_join(., gw, by = c("wellid", "year")) %>%
  mutate(matched = ifelse(!is.na(wellid), 1, 0)) %>%
  filter(matched == 1) %>%
  rename(trs_s = trs_s.x, trs_ss = trs_ss.x) %>%
  select(
    wellid, nrdname, swl, pwl, totaldepth, trs, trs_s, trs_ss, year, volaf, acres, source_txt, source, hp,
    kwh, regdate, pumprate, pumpdepth, decommissiondate, district,
    pumpcoldia, ownerid, wellstatusid, lastname, longdd, latdd, matched
  ) %>%
  mutate(well_trs_ss = paste(wellid, trs_ss, sep = "_")) %>%
  mutate(w_to_e = volaf * 12 / kwh) %>%
  filter(!is.na(volaf)) %>%
  arrange(well_trs_ss, year) %>%
  data.table() %>%
  .[is.infinite(w_to_e), w_to_e := NA] %>%
  .[, coef_var := var(w_to_e, na.rm = TRUE) / mean(w_to_e, na.rm = TRUE), by = .(well_trs_ss)]

#--- visual inspection ---#
# i=17
# ggplot(data=temp_match_2nd[trs==trs_ls[i],]) +
# 	geom_line(aes(y=w_to_e,x=year,color=trs_s)) +
# 	geom_point(aes(y=w_to_e,x=year,color=trs_s)) +
# 	facet_wrap(~wellid,nrow=3) +
# 	ylim(0,0.1) +
# 	theme(
# 		legend.position = 'bottom'
# 		)

# head(temp_match_2nd[trs==trs_ls[i],],50)

#++++++++++++++++
# loop over trs to find matches
#++++++++++++++++
#--- list of the trs ---#
trs_ls <- temp_match_2nd[, trs] %>% unique()
trs_len <- length(trs_ls)

matched_store_all <- list()
for (i in 1:trs_len) { # loop over trs
  #--- select well-energy records combinations in the temporary trs ---#
  temp_match <- temp_match_2nd[trs == trs_ls[i] & !is.na(coef_var), .(well_trs_ss, wellid, trs_ss, coef_var)] %>%
    unique(by = "well_trs_ss")
  well_len <- temp_match[, wellid] %>%
    unique() %>%
    length()

  matched_store_i <- list()
  for (j in 1:well_len) { # loop over wells
    if (min(temp_match[, coef_var]) < 7e-4) { # if there is a match
      #--- identify the best matching well-energy combination ---#
      min_index <- which.min(temp_match[, coef_var])
      get_well <- temp_match[min_index, wellid]
      get_trs_ss <- temp_match[min_index, trs_ss]

      #--- extract the matched data and store in the temporary storage ---#
      matched_store_i[[j]] <- temp_match_2nd %>%
        filter(wellid == get_well & trs_ss == get_trs_ss) %>%
        data.table()

      #--- exclude the matched wellid and energy records  ---#
      temp_match <- temp_match %>%
        filter(!(wellid == get_well | trs_ss == get_trs_ss)) %>%
        data.table()
    } else { # if no good enough matches
      break # end the loop
    }
  }
  matched_store_all[[i]] <- rbindlist(matched_store_i)
}

MC_matched_2nd <- rbindlist(matched_store_all) %>%
  select(
    wellid, nrdname, swl, pwl, totaldepth, year, acres, volaf, source, source_txt,
    trs, trs_s, trs_ss, district, hp, kwh, regdate, pumprate, pumpdepth,
    decommissiondate, pumpcoldia, ownerid, wellstatusid,
    lastname, longdd, latdd, w_to_e, coef_var
  ) %>%
  data.table() %>%
  .[, count := .N, by = wellid] %>%
  .[count > 4, ] %>%
  .[, count := NULL]

#--------------------------
# combine the 1st and 2nd matches and save
#--------------------------
MC_we <- rbind(MC_matched_1st, MC_matched_2nd) %>%
  .[, hours := kwh / (hp * 0.746)] %>%
  .[, gpm := (volaf * 12 * 27154) / (hours * 60)] %>%
  .[w_to_e < 0.1 & w_to_e > 0.008, ]

saveRDS(MC_we, "./Data/Water_Energy/MC_energy_water.rds")

# ===================================
# with Southern
# ===================================
Southern <- readRDS("./Data/Energy/Processed/Southern.rds") %>%
  .[, district := "Southern"]

#--- find wells within the Midwest PPD ---#
SO_trs_ls <- Southern[, trs] %>% unique()
wells_SO <- wells %>%
  filter(trs %in% SO_trs_ls) %>%
  data.table()

#--------------------------
# single trs-trs
#--------------------------
# pick observations that are the only record at the section level (not many)
SO_sec <- Southern[N_trs == 1, ] %>%
  left_join(., wells_SO[N_sec == 1, ], by = "trs") %>%
  rename(trs_s = trs_s.x, trs_ss = trs_ss.x) %>%
  mutate(matched = ifelse(!is.na(wellid), 1, 0)) %>%
  select(
    wellid, nrdname, swl, pwl, totaldepth, trs, trs_s, trs_ss, year,
    district, hp, kwh, regdate, pumprate, pumpdepth, decommissiondate,
    pumpcoldia, ownerid, wellstatusid, lastname, longdd, latdd, matched
  ) %>%
  data.table()

#--------------------------
# single trs_s-trs_s
#--------------------------
# pick observations that are the only record at the subsection level
SO_sub <- Southern[N_trs_s == 1 & N_trs > 1, ] %>%
  left_join(., wells_SO[N_sub == 1 & N_sec > 1, ], by = "trs_s") %>%
  rename(trs = trs.x, trs_ss = trs_ss.x) %>%
  mutate(matched = ifelse(!is.na(wellid), 1, 0)) %>%
  select(
    wellid, nrdname, swl, pwl, totaldepth, trs, trs_s, trs_ss, year,
    district, hp, kwh, regdate, pumprate, pumpdepth, decommissiondate,
    pumpcoldia, ownerid, wellstatusid, lastname, longdd, latdd, matched
  ) %>%
  data.table()

# MC_sub[matched==1,]

#--------------------------
# single trs_ss-trs_ss
#--------------------------
# pick observations that are the only record at the subsubsection level
SO_subsub <- Southern[N_trs_ss == 1 & N_trs_s > 1, ] %>%
  left_join(., wells_SO[N_subsub == 1 & N_sub > 1, ], by = "trs_ss") %>%
  rename(trs = trs.x, trs_s = trs_s.x) %>%
  mutate(matched = ifelse(!is.na(wellid), 1, 0)) %>%
  select(
    wellid, nrdname, swl, pwl, totaldepth, trs, trs_s, trs_ss, year,
    district, hp, kwh, regdate, pumprate, pumpdepth, decommissiondate,
    pumpcoldia, ownerid, wellstatusid, lastname, longdd, latdd, matched
  ) %>%
  data.table()

SO_subsub[matched == 1, ]

#--------------------------
# Merge
#--------------------------
SO_we <- rbind(SO_sec, SO_sub, SO_subsub) %>%
  filter(matched == 1) %>%
  left_join(gw, ., by = c("wellid", "year")) %>%
  filter(!is.na(district)) %>%
  data.table()

SO_matched_1st <- SO_we %>%
  .[, w_to_e := volaf * 12 / kwh] %>%
  .[is.infinite(w_to_e), w_to_e := NA] %>%
  .[, coef_var := var(w_to_e, na.rm = TRUE) / mean(w_to_e, na.rm = TRUE), by = .(wellid)] %>%
  .[coef_var < 7e-4, ] %>%
  .[, count := .N, by = wellid] %>%
  .[count > 4, ] %>%
  .[, count := NULL] %>%
  select(
    wellid, nrdname, swl, pwl, totaldepth, year, acres, volaf, source, source_txt,
    trs, trs_s, trs_ss, district, hp, kwh, regdate, pumprate, pumpdepth,
    decommissiondate, pumpcoldia, ownerid, wellstatusid,
    lastname, longdd, latdd, w_to_e, coef_var
  ) %>%
  data.table()

#--- visualization ---#
# well_ls <- SO_matched_1st[,wellid] %>% unique()
# well_len <- length(well_ls)
# for (i in 1:well_len){
# 	temp_data <- SO_matched_1st[wellid==well_ls[i],]
# 	temp_cv <- temp_data[,coef_var*1e5] %>%
# 		unique() %>%
# 		round(3)
# 	ggplot(data=temp_data) +
# 		geom_line(aes(y=w_to_e,x=year)) +
# 		ylim(0,0.1) +
# 		annotate('text',label=paste('Coef Var = ',temp_cv,sep=''),y=0.075,x=temp_data[,mean(year)])
# 	ggsave(paste('./Graphs/w_to_e/Southern/consistency_',well_ls[i],'.pdf',sep=''))
# }

#--------------------------
# multiple wells and multiple energy records in the same trs
#--------------------------
matched_well_ls <- SO_matched_1st[, wellid] %>% unique()
matched_trs_ss_ls <- SO_matched_1st[, trs_ss] %>% unique()

wells_2nd <- wells_SO[!(wellid %in% matched_well_ls), ]
e_2nd <- Southern[!(trs_s %in% matched_trs_ss_ls), ]

temp_match_2nd <- e_2nd[N_trs_ss == 1, ] %>%
  left_join(., wells_2nd, by = "trs") %>%
  left_join(., gw, by = c("wellid", "year")) %>%
  mutate(matched = ifelse(!is.na(wellid), 1, 0)) %>%
  filter(matched == 1) %>%
  rename(trs_s = trs_s.x, trs_ss = trs_ss.x) %>%
  select(
    wellid, nrdname, swl, pwl, totaldepth, trs, trs_s, trs_ss, year, volaf, acres, source_txt, source, hp,
    kwh, regdate, pumprate, pumpdepth, decommissiondate, district,
    pumpcoldia, ownerid, wellstatusid, lastname, longdd, latdd, matched
  ) %>%
  mutate(well_trs_ss = paste(wellid, trs_ss, sep = "_")) %>%
  mutate(w_to_e = volaf * 12 / kwh) %>%
  filter(!is.na(volaf)) %>%
  arrange(well_trs_ss, year) %>%
  data.table() %>%
  .[is.infinite(w_to_e), w_to_e := NA] %>%
  .[, coef_var := var(w_to_e, na.rm = TRUE) / mean(w_to_e, na.rm = TRUE), by = .(well_trs_ss)]

#--- visual inspection ---#
# i=17
# ggplot(data=temp_match_2nd[trs==trs_ls[i],]) +
# 	geom_line(aes(y=w_to_e,x=year,color=trs_s)) +
# 	geom_point(aes(y=w_to_e,x=year,color=trs_s)) +
# 	facet_wrap(~wellid,nrow=3) +
# 	ylim(0,0.1) +
# 	theme(
# 		legend.position = 'bottom'
# 		)

# head(temp_match_2nd[trs==trs_ls[i],],50)

#++++++++++++++++
# loop over trs to find matches
#++++++++++++++++
#--- list of the trs ---#
trs_ls <- temp_match_2nd[, trs] %>% unique()
trs_len <- length(trs_ls)

matched_store_all <- list()
for (i in 1:trs_len) { # loop over trs
  print(i)
  #--- select well-energy records combinations in the temporary trs ---#
  temp_match <- temp_match_2nd[trs == trs_ls[i] & !is.na(coef_var), .(well_trs_ss, wellid, trs_s, trs_ss, coef_var)] %>%
    unique(by = "well_trs_ss")
  well_len <- temp_match[, wellid] %>%
    unique() %>%
    length()

  matched_store_i <- list()
  for (j in 1:well_len) { # loop over wells
    if (min(temp_match[, coef_var]) < 7e-4) { # if there is a match
      #--- identify the best matching well-energy combination ---#
      min_index <- which.min(temp_match[, coef_var])
      get_well <- temp_match[min_index, wellid]
      get_trs_ss <- temp_match[min_index, trs_ss]

      #--- extract the matched data and store in the temporary storage ---#
      matched_store_i[[j]] <- temp_match_2nd %>%
        filter(wellid == get_well & trs_ss == get_trs_ss) %>%
        data.table()

      #--- exclude the matched wellid and energy records  ---#
      temp_match <- temp_match %>%
        filter(!(wellid == get_well | trs_ss == get_trs_ss)) %>%
        data.table()
    } else { # if no good enough matches
      break # end the loop
    }
  }
  matched_store_all[[i]] <- rbindlist(matched_store_i)
}

SO_matched_2nd <- rbindlist(matched_store_all) %>%
  select(
    wellid, nrdname, swl, pwl, totaldepth, year, acres, volaf, source, source_txt,
    trs, trs_s, trs_ss, district, hp, kwh, regdate, pumprate, pumpdepth,
    decommissiondate, pumpcoldia, ownerid, wellstatusid,
    lastname, longdd, latdd, w_to_e, coef_var
  ) %>%
  data.table() %>%
  .[, count := .N, by = wellid] %>%
  .[count > 4, ] %>%
  .[, count := NULL]

#--------------------------
# combine the 1st and 2nd matches and save
#--------------------------
SO_we <- rbind(SO_matched_1st, SO_matched_2nd) %>%
  .[, hours := kwh / (hp * 0.746)] %>%
  .[, gpm := (volaf * 12 * 27154) / (hours * 60)] %>%
  .[coef_var < 7e-4 & coef_var != 0, ] %>%
  .[w_to_e < 0.1 & w_to_e > 0.008, ]

saveRDS(SO_we, "./Data/Water_Energy/SO_energy_water.rds")

# #--- visualization ---#
# well_ls <- SO_we[,wellid] %>% unique()
# well_len <- length(well_ls)
# for (i in 1:well_len){
# 	temp_data <- SO_we[wellid==well_ls[i],]
# 	temp_cv <- temp_data[,coef_var*1e5] %>%
# 		unique() %>%
# 		round(3)
# 	ggplot(data=temp_data) +
# 		geom_line(aes(y=w_to_e,x=year)) +
# 		ylim(0,0.1) +
# 		annotate('text',label=paste('Coef Var = ',temp_cv,sep=''),y=0.075,x=temp_data[,mean(year)])
# 	ggsave(paste('./Graphs/w_to_e/Southern/consistency_',well_ls[i],'.pdf',sep=''))
# }

# ggplot(data=SO_we[w_to_e>0.008 & pwl <500,]) +
# 	geom_point(aes(y=1/w_to_e,x=pwl),size=0.4) +
# 	geom_smooth(aes(y=1/w_to_e,x=pwl)) +
# 	xlab('Pumping Water Level (feet)') +
# 	ylab('Energy Use Efficiency (kwh/acre-inch)')

# ===================================
# with Twin-Valley
# ===================================
TwinValley <- fread("./Data/Energy/EnergyProcessedByJames/TwinValley/ProcessedJames/TwinValley.csv") %>%
  setnames(names(.), tolower(names(.))) %>%
  data.tanble()

```

### 2024-08-08 Codes/1_1_illustrative_analysis.qmd
Initial commit. Branching out from the original repository of Energy Regulation Welfare Loss.

---
title: Illustrative analysis of the impact of measurement errors
---

Initial analysis of the impact of measurement errors in water on welfare under quota and permit market. Farmers are assumed to be homogeneous (a special case of the analysis run later).

# Set up

## Parameters

```{r}
#| include: false

corn_price <- 6 # (bu/acre)
w_price <- 0 # water itself is free
e_price <- 0.15 # ($/kwh)
other_cost <- 800 # ($/acre)

#--- energy use efficiency ---#
# factor converting water use to energy use (kwh/acre-inch)
eta_ls <- c(300, 700)

farmer_data <-
  data.table(
    farmer = c("A", "B"),
    eta = eta_ls # kwh/inch
  )
#--- water use target ---#
w_lim <- 20
```

Water is in inches. $\eta$ converts water in feet to kwh.

$$
E = \eta \times W / 12
$$

## Production data

Generate yield as a functio of water use. It is assumed that the two farmers have the same yield response function.

$$
Yield = ymax \times (1 - \alpha * e^{-\beta \times w})
$$

```{r}
ymax <- 200
alpha <- 0.8
beta <- 0.3
```

Generate a dataset of yield, water use, energy use, energy use efficiency, energy cost, and profit by farmer.

```{r}
prod_data <-
  data.table(w = seq(0, 16, by = 0.01)) %>%
  #--- yield response function ---#
  .[, yield := ymax * (1 - alpha * exp(-beta * w))] %>%
  expand_grid_df(., farmer_data) %>%
  .[, e := measurements::conv_unit(w, "inch", "ft") * eta] %>%
  .[, e_only_cost := e_price * e] %>%
  .[, w_only_cost := w_price * w] %>%
  .[, profit := corn_price * yield - e_only_cost - w_only_cost - other_cost] %>%
  .[, eta_ratio := eta / sum(eta_ls)] %>%
  .[, marginal_cost_w := w_price + e_price * eta / 12] %>%
  .[, marginal_prod_w := ymax * alpha * beta * exp(-beta * w)] %>%
  .[, marginal_profit_w := marginal_prod_w * corn_price - marginal_cost_w] %>%
  .[, marginal_cost_e := e_price] %>%
  .[, marginal_prod_e := ymax * alpha * beta * exp(-beta * w) / eta * 12] %>%
  .[, marginal_profit_e := marginal_prod_e * corn_price - marginal_cost_e]
```

Find profit-maximizing water (energy) use by farmer under no constraint

```{r}
opt_we <- prod_data[, .SD[which.max(profit), .(w, e)], by = farmer]
```

## Quick visualization

### Profit

```{r}
ggplot(data = prod_data) +
  geom_line(aes(y = profit, x = w)) +
  facet_grid(farmer ~ .)
```

### Marginal profit

```{r}
ggplot(data = prod_data) +
  geom_line(aes(y = marginal_profit_w, x = w)) +
  facet_grid(farmer ~ .) +
  geom_hline(yintercept = 0, color = "red")
```

# Analysis: Quota

## Water-based

```{r}
w_quota_res <-
  prod_data %>%
  nest_by(farmer) %>%
  dplyr::mutate(w_quota = list(
    data.table(data)[which.min(abs(w - w_lim / 2)), ]
  )) %>%
  dplyr::select(farmer, w_quota) %>%
  unnest(cols = w_quota) %>%
  data.table() %>%
  .[, instrument_type := "Water-based"]
```

## Energy-based

Same energy quota for both farmers, which results in total water use of 20.

```{r}
e_quota_res <-
  prod_data %>%
  nest_by(farmer) %>%
  dplyr::mutate(e_quota = list(
    data.table(data)[which.min(abs(w - w_lim * (1 - eta_ratio))), ]
  )) %>%
  dplyr::select(farmer, e_quota) %>%
  unnest(cols = e_quota) %>%
  data.table() %>%
  .[, instrument_type := "Energy-based"]
```

## Combined

```{r}
quota_res <- 
  rbind(e_quota_res, w_quota_res) %>%
  .[, reg_type := "Quota"]
```

```{r}
g_quota_res <- 
ggplot() +
  #--- profit-water curve ---#
  geom_line(
    data = prod_data,
    aes(y = profit, x = w)
  ) +
  #--- water use points ---#
  # geom_point(
  #   data = quota_data,
  #   aes(y = profit, x = w),
  #   size = 3
  # ) +
  facet_grid(instrument_type ~ farmer) +
  #--- vertical line indicating water use ---#
  geom_vline(
    data = quota_res,
    aes(xintercept = w),
    color = "red",
    linetype = "dotted"
  ) +
  #--- water use lable ---#
  geom_text(
    data = quota_res,
    aes(y = 205, x = w + 0.8, label = w),
    color = "red",
    size = 3
  ) +
  #--- horizontal line indicating profit ---#
  geom_hline(
    data = quota_res,
    aes(yintercept = profit),
    color = "blue",
    linetype = "dotted"
  ) +
  #--- profit lable ---#
  geom_text(
    data = quota_res,
    aes(
      y = profit + 20,
      x = 4.5,
      label = round(profit, digits = 1)
    ),
    color = "blue",
    size = 3
  ) +
  scale_x_continuous(breaks = 4:16, limits = c(4, NA)) +
  xlab("Water Use (inches)") +
  ylim(100, NA) +
  ylab("Profit ($/acre)") +
  theme_bw()

ggsave("Results/figures/g_quota_res.pdf", g_quota_res, height = 4, width = 6.5)
```

# Analysis: permit trading

## Water permit trading

```{r}
w_results <-
  lapply(
    seq(0, prod_data[, max(marginal_profit_w)], by = 0.1),
    \(x) {
      prod_data[, .SD[which.min(abs(marginal_profit_w - x)), ], by = farmer] %>%
        .[, permit_price := x]
    }
  ) %>%
  rbindlist() %>%
  .[, tot_w := sum(w), by = permit_price]

permit_price_eq <- w_results[which.min(abs(tot_w - w_lim)), permit_price]

w_res <-
  w_results[permit_price == permit_price_eq, ] %>%
  .[, instrument_type := "Water-based"]
```

## Energy permit trading

```{r}
e_results <-
  lapply(
    seq(0, prod_data[, max(marginal_profit_e)], length = 5000),
    \(x) {
      prod_data[marginal_profit_e > 0, .SD[which.min(abs(marginal_profit_e - x)), ], by = farmer] %>%
        .[, permit_price := x]
    }
  ) %>%
  rbindlist() %>%
  .[, tot_w := sum(w), by = permit_price]

permit_price_eq <- e_results[which.min(abs(tot_w - w_lim)), permit_price]

e_res <-
  e_results[permit_price == permit_price_eq, ] %>%
  .[, instrument_type := "Energy-based"]
```

## Results visualization

```{r}
trade_res <- 
  rbind(w_res, e_res) %>%
  .[, reg_type := "Permit Trading"]

(
g_trade_res <- 
  ggplot() +
  geom_point(
    data = trade_res,
    aes(y = profit, x = w),
    size = 3
  ) +
  geom_line(
    data = prod_data,
    aes(
      x = w,
      y = profit
    )
  ) +
  #--- vertical line indicating water use ---#
  geom_vline(
    data = trade_res,
    aes(xintercept = w),
    color = "red",
    linetype = "dotted"
  ) +
  #--- water use lable ---#
  geom_text(
    data = trade_res,
    aes(y = 205, x = w + 1.1, label = w),
    color = "red",
    size = 3
  ) +
  #--- horizontal line indicating profit ---#
  geom_hline(
    data = trade_res,
    aes(yintercept = profit),
    color = "blue",
    linetype = "dotted"
  ) +
  #--- profit lable ---#
  geom_text(
    data = trade_res,
    aes(
      y = profit + 40,
      x = 4.5,
      label = round(profit, digits = 1)
    ),
    color = "blue",
    size = 3
  ) +
  facet_grid(instrument_type ~ farmer) +
  xlab("Water Use (inches)") +
  ylab("profit (bushel/acre)") +
  theme_bw()
)

ggsave("Results/figures/g_trade_res.pdf", g_trade_res, height = 4, width = 6.5)
```

# Save the results

```{r}
parameters <- 
  list(
  corn_price = corn_price, # (bu/acre)
  w_price = w_price, # water itself is free
  e_price = e_price, # ($/kwh)
  other_cost = other_cost, # ($/acre)
  w_lim = w_lim, # water use target
  ymax = ymax,
  alpha = alpha,
  beta = beta
  )

analysis_results <- 
  rbind(
    quota_res, 
    trade_res, 
    fill = TRUE
  )
```

```{r}
save(parameters, farmer_data, prod_data, analysis_results, file = "Results/illustration_results.Rdata")
```

### 2024-08-08 Codes/1_3_proxy_quota_analysis.qmd
Initial commit. Branching out from the original repository of Energy Regulation Welfare Loss.

---
title: Welfare analysis of quota and trading system with heterogeneous production functions
---

# Objectives

This program analyzes the performance of the quota system where quota is determined randomly for a given level of target water use. This quota system imitates a quota system based on water use proxy where the measurement error exists.

+ Checks how correlation between optimal water use and measurement error affects the effectiveness of the quota system (though the answer is obvious).

# Setup

## Theoretical setup

$$
\pi = P_c \cdot f(w) - P_w \cdot w 
$$

$$
\frac{\partial\pi}{\partial w} = P_c \cdot \frac{\partial f(w)}{\partial w} - P_w 
$$

$$
\pi = P_c \cdot f(\eta \cdot p) - P_w \cdot \eta \cdot p
$$

$$
\frac{\partial \pi}{\partial p} = P_c \cdot \frac{\partial f(w)}{\partial w}\cdot \frac{\partial w}{\partial p} - P_w \cdot \eta
= \eta\cdot\frac{\partial\pi}{\partial w}
$$

What to vary:

+ variance of the measurement error 
+ direction of correlation of the measurement error and optimal water use
+ water allocation

+ positive: $\eta := \frac{w^*}{\bar{w^*}}\cdot \varepsilon$
+ negative: $\eta := \frac{\bar{w^*}}{w^*}\cdot \varepsilon$
+ independent: $\eta := \frac{\bar{w^*}}{w^*}\cdot \varepsilon$

## Prices and costs
```{r}
corn_price <- 6 # (bu/acre)
e_price <- 0.15 # ($/kwh)
w_price <- e_price * 500 / 12 # ($/inch)
other_cost <- 800 # ($/acre)
```

## Farmers yield response functions

```{r}
#--- number of farmers ---#
num_farmers <- 1000

#--- parameter heterogeneity ---#
parameters <-
  list(
    #--- ymax ---#
    # determines the maximum yield attainable
    ymax_min = 160,
    ymax_max = 250,
    #--- alpha [0, 1] ---#
    # determines rainfed yield. The higher, the lower rainfed yield.
    alpha_min = 0.4,
    alpha_max = 0.9,
    #--- beta ---#
    # determines how fast yield hits plateau as a function of water
    beta_min = 0.1,
    beta_max = 0.7
  )

#--- generate farmer data ---#
farmer_data <- gen_farmer_data_p(num_farmers, parameters)

#--- generate production data ---#
prod_data <- gen_prod_data_p(farmer_data)
```

```{r}
ggplot(farmer_data) +
  geom_histogram(aes(x = opt_w))

farmer_data[, mean(opt_w)]
```

# Simulation

Set up a parameter space to loop over.

+ `target_w`: target water use
+ `u_dev`: maximum deviation from 1 (determines the variance of measurement error)
+ `dir_cor`: direction of the correlation between (unconstrained) optimal water use and measurement error

```{r}
par_data <-
  data.table::CJ(
    target_w = seq(7, 13, by = 0.25),
    u_dev = c(0, 0.1, 0.3, 0.5),
    dir_cor = c("+", "-", "0")
  )
```

When `dir_cor = -` and `u_dev = 0`, measurement error is set so that the ratio of effective water use to proxy (`target_w`) is the same across farmers. For example, when `target_w` is the same as the average optimal water use, effective water use limit allocation maximizes social welfare (same as proxy permit trading). When `dir_cor = 0` and `u_dev = 0`, the quota system is simply a uniform quota system.

For a given value of `target_w`, `u_dev`, and `dir_cor`,

+ Create a set of quota (different quota values for different farmers) system for the number of rounds specified by the user using `make_quota_data()`
  + This function first assigns the effective water use limit and then calculate what the water to proxy conversion rate should have been
+ Conduct quota analysis using `quota_analysis_het()`

## Base case (water use quota)

The quota system with `dir_cor = 0` and `u_dev = 0` is equivalent to water quota (no measurement error).

```{r}
par_sets_w <- par_data[u_dev == 0 & dir_cor == "0", ]

results_w <- run_analysis(cases = par_sets_w, farmer_data, prod_data)
```

## Proxy quota (with measurement errors)

```{r, eval = FALSE}
par_sets_p <- par_data[!(u_dev == 0 & dir_cor == "0"), ]

results_p <- run_analysis(cases = par_sets_p, farmer_data, prod_data)

saveRDS(quota_results, "Results/quota_results_comp_stat.rds")
```

Modify the results for presentation.

```{r}
quota_results <- readRDS(here::here("Results/quota_results_comp_stat.rds"))

quota_results_het <-
  quota_results[!(dir_cor == "0" & sd == 0), ] %>%
  .[, dir_cor_txt := paste0("Correlation: ", dir_cor)] %>%
  .[, dir_cor_txt := factor(dir_cor_txt, levels = paste0("Correlation: ", c("-", "0", "+")))] %>%
  .[, sd_txt := paste0("SD: ", sd)] %>%
  .[, sd_txt := factor(sd_txt, levels = paste0("SD: ", unique(sd)))]

quota_results_no_me <-
  quota_results[dir_cor == "0" & sd == 0, ] %>%
  .[, .(w, target_w, profit)]
```

# Results Presentation

## Water use slack

Water use slack always exists when a uniform water quota is used and farmers are heterogeneous in production function.

The figure below shows water use under a range of water use limit values (x-axis) under different circumstances characterized by two parameters:

1. correlation between measurement error and unconstrained optimal water use and 
2. standard deviation of measurement error

The blue solid lines represent the water use without any measurement error. The red solid lines represent the water use with measurement error. The black solid lines represent 1 to 1 line. The vertical distance from the black line is the "slack" in water use: how much less water is used relative to the water use limit.

```{r}
ggplot() +
  geom_line(data = quota_results_het, aes(y = w, x = target_w), color = "red") +
  geom_line(data = quota_results_no_me, aes(y = w, x = target_w), color = "blue") +
  geom_abline(slope = 1) +
  facet_grid(sd_txt ~ dir_cor_txt) +
  coord_equal()
```

+ As the standard deviation of measurement error increases, water use slack becomes larger. 
+ When the correlation between measurement error and unconstrained water use is positive, water use slack with measurement error can be smaller compared to the case without measurement error. 
+ Positive correlation between them can happen in the case where energy use is used as a proxy for water use. This means that more (effective) water is allocated to those who use more water.

**Note:** For the $SD = 0$ and $Correlation = +$ case, it is programmed so that quota perfectly matches with unconstrained optimal water use.

### <span style = "color: red;"> What is the problem with water use slack? </span>

When <span style = "color: blue;"> unbiased (in estimating water use) </span> proxy is used, policy makers may unintentionally make the quota too stringent.

## Profitability

```{r}
ggplot() +
  geom_line(data = quota_results_het, aes(y = profit, x = w), color = "red") +
  geom_line(data = quota_results_no_me, aes(y = profit, x = w), color = "blue") +
  facet_grid(sd_txt ~ dir_cor_txt)
```

Given an actual water use level, farming profitability is lower with measurement error except under a small parameter space where measurement error is positively correlated with unconstrained water use and the variance of measurement error is small.

# What does water permit trading do?

Introducing trading to a water quota system increases water use if total quota stays the same (URNRD).

Reduces unfairness.

# Unfairness measure

How much loss relative to uniform water use restriction? Compare between quota and trading.

### 2024-08-08 Codes/1_5_sensitivity_to_sample_size.qmd
Initial commit. Branching out from the original repository of Energy Regulation Welfare Loss.

---
title: Examine the sensitivity of the results to the sample size of water-energy data
---

# Objective

Administrator of the quota system needs to learn the relationship between water and energy use to set the right quota to achieve water conservation target.

# Estimate energy use efficiency

```{r}
ne_data <-
  readRDS(here::here("Data/water_energy_MW.rds")) %>%
  .[nrdname != "Twin Platte", ] %>%
  .[, me := water_est - volaf] %>%
  .[, w_to_e := kwh / volaf] %>% # (kwh/feet)
  .[, region := paste0(nrdname, " (Nebraska)")] %>%
  .[w_to_e > 250, ] %>%
  .[w_to_e < 1000, ]

```

```{r}

unique_wells <- ne_data[, wellid] %>% unique()
unique_years <- ne_data[, unique(year)]

parameters <-
  data.table::CJ(
    case = 1:100,
    well_nums = length(unique_wells) * c(0.01, 0.03, 0.05, 0.1, 0.2, 0.5),
    year_nums = c(1, 3, 5, length(unique_years))
  ) %>%
  rowwise() %>%
  dplyr::mutate(sample_wells = list(
    sample(unique_wells, well_nums, replace = FALSE)
  )) %>%
  dplyr::mutate(sample_years = list(
    sample(unique_years, year_nums, replace = FALSE)
  )) %>%
  dplyr::mutate(w_to_e_estimate = list(
    ne_data[wellid %in% sample_wells, ] %>%
    .[year %in% sample_years, ] %>%
    .[, mean(w_to_e, na.rm = TRUE)]
  )) %>%
  dplyr::select(- sample_wells, - sample_years) %>%
  unnest() %>%
  data.table()
```

### 2024-08-08 Codes/1_analysis.qmd
Initial commit. Branching out from the original repository of Energy Regulation Welfare Loss.

---
title: Welfare analysis of quota and trading system
format:
  html:
    embed-resources: true
---

# Objectives

This program analyzes the performance of the quota and trading system where quota is determined randomly for a given level of target water use.

+ examine how correlation between optimal water use and measurement error affects the effectiveness of the quota system (though the answer is obvious).
  + 3 cases: independent, positive, and negative
+ examine how the heterogeneity in production function affects the effectiveness of  **proxy** quota and trading system with measurement errors relative to **water** quota and trading
  + 3 cases: no, medium, high  heterogeneity

Outcomes to look at:

+ profitability
+ water use slack
+ fairness

# Setup

## Theoretical setup

$$
w_i = \eta_i \cdot p_i
$$

+ $w$: water use 
+ $p$: energy use 
+ $eta$: energy use efficiency (convert energy use to water use)

$$
\pi = P_c \cdot f(w) - P_w \cdot w 
$$

$$
\frac{\partial\pi}{\partial w} = P_c \cdot \frac{\partial f(w)}{\partial w} - P_w 
$$

$$
\pi = P_c \cdot f(\eta \cdot p) - P_w \cdot \eta \cdot p
$$

$$
\frac{\partial \pi}{\partial p} = P_c \cdot \frac{\partial f(w)}{\partial w}\cdot \frac{\partial w}{\partial p} - P_w \cdot \eta
= \eta\cdot\frac{\partial\pi}{\partial w}
$$

What to vary:

+ variance of the measurement error 
+ direction of correlation of the measurement error and optimal water use
+ water allocation

+ positive: $\eta := \frac{w^*}{\bar{w^*}}\cdot \varepsilon$
+ negative: $\eta := \frac{\bar{w^*}}{w^*}\cdot \varepsilon$
+ independent: $\eta := \frac{\bar{w^*}}{w^*}\cdot \varepsilon$

## Prices and costs
```{r}
corn_price <- 6 # (bu/acre)
e_price <- 0.15 # ($/kwh)
w_price <- e_price * 500 / 12 # ($/inch)
other_cost <- 800 # ($/acre)
```

## Farmers yield response functions

Production function:

$$
y = f(w) = ymax (1 - \alpha \cdot e^{-\beta\cdot w})
$$

$$
\pi = P_c \cdot f(w) - P_w\cdot w
$$

$$
\frac{\partial\pi}{\partial w} = P_c \cdot (ymax\cdot
\alpha\cdot\beta\cdot e^{-\beta\cdot w}) - P_w
$$

$$
w^* = -log(P_w / (P_c \cdot ymax \cdot \alpha \cdot \beta)) / \beta
$$

### Create three production heterogeneity cases

```{r}
#--- number of farmers ---#
num_farmers <- 1000
```

**Completely homogeneous**

Determine optimal water use ($w^*$), $ymax$, and $\alpha$.

```{r}
par_set_zero <- list(
  opt_w = 12,
  ymax_min = 230,
  ymax_max = 230,
  alpha_min = 0.7,
  alpha_max = 0.7
)
```

**Medium heterogeneity**

```{r}
set.seed(328954)
par_set_med <- list(
  opt_w = rlnorm(num_farmers, mean = log(11.8525), sdlog = 0.2),
  ymax_min = 210,
  ymax_max = 250,
  alpha_min = 0.7,
  alpha_max = 0.7
)
```

Check the distribution:

```{r}
mean(par_set_med$opt_w)
hist(par_set_med$opt_w)
```

**High heterogeneity**

```{r}
set.seed(328954)
par_set_high <- list(
  opt_w = rlnorm(num_farmers, mean = log(11.266), sdlog = 0.4),
  ymax_min = 210,
  ymax_max = 250,
  alpha_min = 0.6,
  alpha_max = 0.8
)
```

Check the distribution:

```{r}
mean(par_set_high$opt_w)
hist(par_set_high$opt_w)
```

```{r}
par_set <-
  data.table(
    prod_het = c("zero", "medium", "high"),
    par_set = list(par_set_zero, par_set_med, par_set_high)
  )
```

Generate production data where yield, profit, marginal profit of water (and others) are calculated at a sequence of water use levels for each farmer. In the process, the value of $\beta$ is calculated so that the optimal water use is indeed `opt_w`.

```{r}
#| eval: false
system_data <-
  par_set %>%
  rowwise() %>%
  dplyr::mutate(farmer_data = list(
    gen_farmer_data(par_set, num_farmers)
  )) %>%
  dplyr::mutate(prod_data = list(
    #--- generate production data ---#
    gen_prod_data(farmer_data)
  ))

saveRDS(system_data, here::here("Results/quota_results_comp_stat.rds"))
```

# Simulation

Set up a parameter space to loop over.

+ `target_w`: target water use
+ `u_dev`: maximum deviation from 1 (determines the variance of measurement error)
+ `dir_cor`: direction of the correlation between (unconstrained) optimal water use and measurement error

```{r}
#| eval: FALSE
par_data <-
  data.table::CJ(
    target_w = seq(7, 13, by = 0.25),
    u_dev = c(0, 0.1, 0.3, 0.5),
    dir_cor = c("+", "-", "0")
  )
```

When `dir_cor = -` and `u_dev = 0`, measurement error is set so that the ratio of effective water use to proxy (`target_w`) is the same across farmers. For example, when `target_w` is the same as the average optimal water use, effective water use limit allocation maximizes social welfare (same as proxy permit trading). When `dir_cor = 0` and `u_dev = 0`, the quota system is simply a uniform quota system.

For a given value of `target_w`, `u_dev`, and `dir_cor`,

+ Create a set of quota (different quota values for different farmers) system for the number of rounds specified by the user using `make_quota_data()`
  + This function first assigns the effective water use limit and then calculate what the water to proxy conversion rate should have been
+ Conduct quota analysis using `quota_analysis_het()`

## Base case (water use quota)

The quota system with `dir_cor = 0` and `u_dev = 0` is equivalent to water quota (no measurement error).

```{r}
#| eval: FALSE
par_sets_w <- par_data[u_dev == 0 & dir_cor == "0", ]

# farmer_data <- system_data$farmer_data[[1]]
# prod_data <- system_data$prod_data[[1]]

results_w <-
  system_data %>%
  dplyr::mutate(results = list(
    run_analysis(parameter_sets = par_sets_w, farmer_data, prod_data, num_it = 1)
  )) %>%
  dplyr::select(prod_het, results) %>%
  unnest(cols = c(results)) %>%
  data.table()

saveRDS(results_w, "Results/results_water.rds")
```

## Proxy quota (with measurement errors)

```{r, eval = FALSE}
#| eval: FALSE

par_sets_p <- par_data[!(u_dev == 0 & dir_cor == "0"), ]

set.seed(7845239)

results_p <-
  system_data %>%
  dplyr::mutate(results = list(
    run_analysis(parameter_sets = par_sets_p, farmer_data, prod_data, num_it = 100, num_cores = 8)
  )) %>%
  dplyr::select(prod_het, results) %>%
  unnest(cols = c(results)) %>%
  data.table()

saveRDS(results_p, "Results/results_proxy.rds")
```

# Results Presentation

## Summarize the results for presentation.

```{r, eval = FALSE}
#--- proxy ---#
results_p <- readRDS("Results/results_proxy.rds")

sum_proxy_res <-
  results_p %>%
  .[, .(profit = mean(profit), w = mean(w)), by = .(target_w, instrument_type, dir_cor, u_dev, prod_het)] %>%
  .[, measure_type := "Proxy"]

saveRDS(sum_proxy_res, here::here("Results/proxy_results_summary.rds"))

#--- water ---#
results_w <- readRDS(here::here("Results/results_water.rds"))

sum_water_res <-
  results_w %>%
  .[, .(profit = mean(profit), w = mean(w)), by = .(target_w, instrument_type, dir_cor, u_dev, prod_het)] %>%
  .[, measure_type := "Water"]

saveRDS(sum_water_res, here::here("Results/water_results_summary.rds"))
```

```{r}
sum_res <-
  rbind(
    readRDS(here::here("Results/proxy_results_summary.rds")),
    readRDS(here::here("Results/water_results_summary.rds"))
  ) %>%
  .[, dir_cor_txt := paste0("Correlation: ", dir_cor)] %>%
  .[, dir_cor_txt := factor(dir_cor_txt, levels = paste0("Correlation: ", c("-", "0", "+")))] %>%
  .[, prod_het := str_to_title(prod_het)] %>%
  .[, prod_het := factor(prod_het, c("Zero", "Medium", "High"))]
```

## Profitability: Water vs Proxy Quota (with comparative statistics wrt heterogeneity of farmers)

Figure below compares agricultural profitability as a function of actual water use between water and proxy quota across different production heterogeneity levels. When there is no heterogeneity in farmers' production function, water quota is the most cost effective way to achieve a water use reduction goal (highest profit achievable for a given level of actual water use). Under this circumstance, proxy quota with unbiased measurement errors achieves worse than water quota due to asymmetry in downside and upside risk of water use. (add illustrative figure).

However, as heterogeneity of farmers increases, comparative advantage of water quota over proxy quota declines. While the performance of both systems declines as the level of heterogeneity increases, water quota is affected more so than proxy quota.

```{r}
(
  g_profit_quota_w_vs_p <-
    sum_res %>%
    .[instrument_type == "Quota", ] %>%
    .[(dir_cor == "0" & u_dev == 0.3 & measure_type == "Proxy") | measure_type == "Water", ] %>%
    ggplot(data = .) +
    geom_line(aes(y = profit, x = w, color = measure_type)) +
    facet_grid(. ~ prod_het) +
    ylab("Target Water Use (inches)") +
    xlab("Realized Water Use (inches)") +
    scale_color_discrete(name = "Measurement Type") +
    theme_bw() +
    theme(
      legend.position = "bottom"
    )
)

ggsave("Writing/figures/g_profit_quota_w_vs_p.pdf", g_profit_quota_w_vs_p, height = 3.5, width = 6)
```

```{r}
#| echo: false

system_data <- readRDS(here::here("Results/quota_results_comp_stat.rds"))

farm_data <-
  data.table(system_data)[prod_het == "medium", farmer_data][[1]] %>%
  #--- use farmer 1 ---#
  .[farmer == 1, ] %>%
  .[, farmer := NULL] %>%
  expand_grid_df(., data.table(w = seq(0, 15, by = 0.1))) %>%
  .[, yield := ymax * (1 - alpha * exp(-beta * w))] %>%
  .[, w_cost := w_price * w] %>%
  .[, profit := corn_price * yield - w_cost - other_cost] %>%
  .[, marginal_cost_w := w_price] %>%
  .[, marginal_prod_w := ymax * alpha * beta * exp(-beta * w)] %>%
  .[, marginal_profit_w := marginal_prod_w * corn_price - marginal_cost_w]

opt_w <- unique(farm_data$opt_w)

quota_data <-
  data.table(
    farmer = c(1, 2, 1, 2),
    measure_type = c("Water", "Water", "Proxy", "Proxy"),
    quota = c(7, 7, 4, 10)
  ) %>%
  .[, w := quota] %>%
  .[quota > opt_w, w := opt_w] %>%
  farm_data[., on = .(w), roll = "nearest"]

pi_dif_2 <- quota_data[farmer == 2 & measure_type == "Proxy", profit] - quota_data[farmer == 2 & measure_type == "Water", profit]
pi_dif_1 <- quota_data[farmer == 1 & measure_type == "Proxy", profit] - quota_data[farmer == 1 & measure_type == "Water", profit]
```

The red dotted lines indicate the effective water use quota. Under the water quota system, both farmers receive 7 inches of water quota. Since the unconstrained profit maximizing water use is `r round(opt_w, digits = 2)` inches, both farmers use up all the allocated quota and use 10 inches of water. Under the proxy quota system, they are allocated the same amount of proxy quota. However, measurement error in proxy quota resulted in effective water quota of 4 and 10 inches for farmer A and B, respectively. Both farmers use their allocated amout of water. Under both proxy and water quota systems, the total water use is 14 inches. Farmer B makes `r pi_dif_2` less under the water quota system compared to the proxy quota system. However, Farmer A makes `r -pi_dif_1` more under the water quota system compared to the proxy quota system. This comes from an important nature of crop production with respsect to water: declining marginal impact of water on crop yield. As can be seen in the profit-water relationship, removing an inch of water from 6 inches has much larger negative impact compared to revmoing an inch of water from 10 inches.

```{r}
#| warning: false
(
  g_illustration_homogeneous <-
    ggplot() +
    geom_line(
      data = farm_data,
      aes(y = profit, x = w)
    ) +
    geom_vline(
      data = quota_data,
      aes(xintercept = quota),
      linetype = 2,
      color = "red"
    ) +
    geom_point(
      data = quota_data,
      aes(y = profit, x = w),
      color = "blue",
      size = 2
    ) +
    facet_grid(measure_type ~ farmer) +
    ylim(0, NA) +
    xlab("Water Use (inches)") +
    ylab("Profit ($/acre)") +
    theme_bw()
)

ggsave("Writing/figures/g_illustration_homogeneous.pdf", g_illustration_homogeneous, height = 3.5, width = 6)
```

However, when production function becomes heterogeneous, water quota starts to lose its advantage. Uniform quota now acts like heterogeneous quota under homogeneous production function because the same quota is given to farmers with heterogeneous quota. In the example presented in the figure below, farmer A needs less water than farmer B. Water and proxy quota allocated to the farmers are exactly the same as the previous case. In this example, errors in proxy happened to realize so that more effective water quota is given to farmer B than farmer A. Consequently, proxy quota produces a higher total profit than water quota. Of course, if error happened to go the opposite way, then the performance of proxy quota relative to water quota is even worse compared to the homogeneous case. This is a big contrast to the homogeneous case because water quota is always better than proxy quota in that case. Consequently, proxy quota performs relatively better under heterogeneous cases. On average, the positive and negative effects of measurement errors tend to even out. However, proxy quota is never better than water quota **on average** (see Appendix ... for mathematical proof).

```{r}
#| echo: false
#| warning: false

farm_data <-
  data.table(system_data)[prod_het == "medium", farmer_data][[1]] %>%
  .[, dev_from_7 := abs(opt_w - 7)] %>%
  .[, dev_from_13 := abs(opt_w - 13)] %>%
  .[(dev_from_7 == min(dev_from_7) | dev_from_13 == min(dev_from_13)), ] %>%
  expand_grid_df(., data.table(w = seq(0, 15, by = 0.1))) %>%
  .[, yield := ymax * (1 - alpha * exp(-beta * w))] %>%
  .[, w_cost := w_price * w] %>%
  .[, profit := corn_price * yield - w_cost - other_cost] %>%
  .[, marginal_cost_w := w_price] %>%
  .[, marginal_prod_w := ymax * alpha * beta * exp(-beta * w)] %>%
  .[, marginal_profit_w := marginal_prod_w * corn_price - marginal_cost_w] %>%
  .[, farmer_txt := "A"] %>%
  .[opt_w == max(opt_w), farmer_txt := "B"]

opt_w <- farm_data[, .(opt_w = unique(opt_w)), by = farmer_txt]

quota_data_het <-
  data.table(
    farmer_txt = c("A", "B", "A", "B"),
    measure_type = c("Water", "Water", "Proxy", "Proxy"),
    quota = c(7, 7, 4, 10)
  ) %>%
  opt_w[., on = .(farmer_txt)] %>%
  .[, w := quota] %>%
  .[quota > opt_w, w := opt_w] %>%
  setnames("farmer_txt", "farmer_id") %>%
  nest_by(farmer_id) %>%
  dplyr::mutate(merged = list(
    farm_data[farmer_txt == farmer_id, ][data.table(data), on = .(w), roll = "nearest"]  
  )) %>%
  dplyr::select(farmer_id, merged) %>%
  unnest(cols = c(merged)) %>%
  data.table() %>%
  .[, .(farmer, farmer_txt, w, opt_w, profit, measure_type, quota)]

```

```{r}
#| warning: false
(
  g_illustration_het <-
    ggplot() +
    geom_line(
      data = farm_data,
      aes(y = profit, x = w)
    ) +
    geom_vline(
      data = quota_data_het,
      aes(xintercept = quota),
      linetype = 2,
      color = "red"
    ) +
    geom_point(
      data = quota_data_het,
      aes(y = profit, x = w),
      color = "blue",
      size = 2
    ) +
    facet_grid(measure_type ~ farmer_txt) +
    ylim(0, NA) +
    xlab("Water Use (inches)") +
    ylab("Profit ($/acre)") +
    theme_bw()
)

ggsave("Writing/figures/g_illustration_het.pdf", g_illustration_het, height = 3.5, width = 6)
```

When measurement error is independent and production function is concave, water quota always outperforms proxy quota (show proof in appendix).

## Water Use Slack:

### <span style = "color: red;"> What is the problem with water use slack? </span>

+ When <span style = "color: blue;"> unbiased (in estimating water use) </span> proxy is used, policy makers may unintentionally make the quota too stringent.  
+ Being aware of this problem, policy makers need to set a quota that is higher than the target water use. But, it is hard to know how much higher.

```{r}
(
  g_slack_quota_w_vs_p <-
    sum_res %>%
    .[instrument_type == "Quota", ] %>%
    .[(dir_cor == "0" & u_dev == 0.3 & measure_type == "Proxy") | measure_type == "Water", ] %>%
    ggplot(data = .) +
    geom_line(aes(y = w, x = target_w, color = measure_type)) +
    facet_grid(. ~ prod_het) +
    geom_abline(slope = 1, color = "black") +
    xlab("Realized Water Use (inches)") +
    ylab("Profit from Agricultural Production ($/acre)") +
    coord_equal()
)
```

Water use slack always exists when a uniform water quota is used and farmers are heterogeneous in production function.

The figure below shows water use under a range of water use limit values (x-axis) under different circumstances characterized by two parameters:

1. correlation between measurement error and unconstrained optimal water use and 
2. standard deviation of measurement error

The blue solid lines represent the water use without any measurement error. The red solid lines represent the water use with measurement error. The black solid lines represent 1 to 1 line. The vertical distance from the black line is the "slack" in water use: how much less water is used relative to the water use limit.

As the standard deviation of measurement error increases, water use slack becomes larger. 
+ When the correlation between measurement error and unconstrained water use is positive, water use slack with measurement error can be smaller compared to the case without measurement error. 
+ Positive correlation between them can happen in the case where energy use is used as a proxy for water use. This means that more (effective) water is allocated to those who use more water.

**Note:** For the $SD = 0$ and $Correlation = +$ case, it is programmed so that quota perfectly matches with unconstrained optimal water use.

## The effect of increasing the size of measurement error

```{r}
q_udev <- sum_res[(dir_cor == "0" & measure_type == "Proxy"), ]
w_udev <-
  sum_res[measure_type == "Water", ] %>%
  .[, u_dev := NULL] %>%
  expand_grid_df(., data.table(u_dev = c(0.1, 0.3, 0.5)))

quota_plot_data_comp_stat <-
  rbind(q_udev, w_udev) %>%
  .[instrument_type == "Quota", ]
```

Profit loss increases as the degree of measurement error increases.

```{r}
(
  g_profit_quota_comp_stat <-
    ggplot(data = quota_plot_data_comp_stat) +
    geom_line(aes(y = profit, x = w, color = measure_type)) +
    facet_grid(u_dev ~ prod_het) +
    ylab("Profit ($/acre)") +
    xlab("Realized Water Use (inches)")
)
```

```{r}
(
  g_slack_quota_comp_stat <-
    ggplot(data = quota_plot_data_comp_stat) +
    geom_line(aes(y = w, x = target_w, color = measure_type)) +
    geom_abline(slope = 1, color = "black") +
    facet_grid(u_dev ~ prod_het) +
    ylab("Target Water Use (inches)") +
    xlab("Realized Water Use (inches)")
)
```

## The effect of allowing trading quota

```{r}
#| echo: false
q_temp <- sum_res[(dir_cor == "0" & u_dev != 0 & measure_type == "Proxy"), ]
w_temp <-
  sum_res[measure_type == "Water", ] %>%
  .[, u_dev := NULL] %>%
  expand_grid_df(., data.table(u_dev = c(0.1, 0.3, 0.5)))

trading_plot_data <-
  rbind(w_temp, q_temp) %>%
  .[, type := paste0(measure_type, "-", instrument_type)]
```

### Trading reduces welfare loss associated with the use of proxy

+ Using proxy under the quota system instead of water can hurt welfare severely
+ The disadvantage of using proxy almost disappears when trading of quota is allowed
+ Proxy trading will never be as profitable as water trading (provide mathematical proof), but the economic loss seems to be very small

```{r}
#| echo: false

(
  g_trade_effect_profit <-
    ggplot(data = trading_plot_data) +
    geom_line(aes(y = profit, x = w, color = type)) +
    facet_grid(u_dev ~ prod_het) +
    scale_color_brewer(palette = "Set1") +
    ylab("Profit ($/acre)") +
    xlab("Realized Water Use (inches)") +
    scale_color_discrete(name = "Measurement Type") +
    theme_bw() +
    theme(legend.position = "bottom")
)

ggsave("Writing/figures/g_trade_effect_profit.pdf", g_trade_effect_profit, height = 3.5, width = 6)
```

### Trading reduces uncertainty in water use slack

As long as proxy is an unbiased estimation of water use, trading of quota eliminates uncertainty in water use slack for policy makers.

```{r}
#| echo: false

(
  g_trade_effect_slack <-
    ggplot(data = trading_plot_data) +
    geom_line(aes(y = w, x = target_w, color = type)) +
    facet_grid(u_dev ~ prod_het) +
    scale_color_brewer(palette = "Set1") +
    xlab("Target Water Use (inches)") +
    ylab("Realized Water Use (inches)")
)
```

Introducing trading to a water quota system can increases water use substantially if total quota stays the same (URNRD).

## Profit Distribution

Figure below presents the ratio of profit under quota-based relative to water-based system for quota (red) and permit trading (blue). Ratio of less than 1 indicates making less profit under the quota-based system compared to the water-based system.

```{r}
#| eval: false

#! Nearest matching based on water use (not target water use).

sum_proxy_res <- readRDS(here::here("Results/proxy_results_summary.rds"))
sum_water_res <- readRDS(here::here("Results/water_results_summary.rds"))

sum_water_res_quota <- 
  sum_water_res[instrument_type == "Quota", ] %>%
  setnames("target_w", "target_w_water") %>%
  .[, .(target_w_water, w)]

sum_proxy_res_quota <- 
  sum_proxy_res[instrument_type == "Quota", ] %>%
  setnames("target_w", "target_w_proxy") %>%
  .[, .(target_w_proxy, w, dir_cor, u_dev, prod_het)]

quota_match <-
  sum_water_res_quota[sum_proxy_res_quota, on = .(w), roll = "nearest"] %>%
  unique(by = c("target_w_proxy", "dir_cor", "u_dev", "prod_het"))
```

### Quota

```{r}
#| eval: false

results_p_slim <- 
  results_p[instrument_type == "Quota", .(target_w, profit, dir_cor, u_dev, prod_het, farmer, case)] %>%
  setnames("target_w", "target_w_proxy") %>%
  setnames("profit", "profit_proxy") %>%
  quota_match[., on = .(target_w_proxy, dir_cor, u_dev, prod_het)]

results_w_slim <- 
  results_w[instrument_type == "Quota", .(target_w, profit, prod_het, farmer)] %>%
  setnames("target_w", "target_w_water") %>%
  setnames("profit", "profit_water")

prob_ls <- seq(0.01, 0.99, by = 0.01)

profit_ratio_quota <- 
  results_w_slim[results_p_slim, on = .(target_w_water, prod_het, farmer)] %>%
  .[, ratio := profit_proxy / profit_water] %>%
  .[, .(ratio = quantile(ratio, prob = prob_ls)), by = .(w, dir_cor, u_dev, prod_het)] %>%
  .[, prob := rep(prob_ls, .N / length(prob_ls))]

saveRDS(profit_ratio_quota, here::here("Results/profit_ratio_quota.rds"))
```

### Trading

```{r}
#| eval: false

results_p_slim <- 
  results_p[instrument_type == "Trading", .(target_w, profit, dir_cor, u_dev, prod_het, farmer, case)] %>%
  setnames("profit", "profit_proxy")

results_w_slim <- 
  results_w[instrument_type == "Trading", .(target_w, profit, prod_het, farmer)] %>%
  setnames("profit", "profit_water")

profit_ratio_trading <- 
  results_w_slim[results_p_slim, on = .(target_w, prod_het, farmer)] %>%
  .[, ratio := profit_proxy / profit_water] %>%
  .[, .(ratio = quantile(ratio, prob = prob_ls)), by = .(target_w, dir_cor, u_dev, prod_het)] %>%
  .[, prob := rep(prob_ls, .N / length(prob_ls))]

saveRDS(profit_ratio_trading, here::here("Results/profit_ratio_trading.rds"))
```

### Visualization

```{r}
#| eval: false

profit_ratio_trading <- 
  readRDS(here::here("Results/profit_ratio_trading.rds")) %>%
  .[dir_cor == "0" & target_w == 8 & ratio > 0 & ratio < 3, ] %>%
  .[, .(u_dev, prod_het, ratio, prob)] %>%
  .[, instrument_type := "Trading"]

profit_ratio_quota <- 
  readRDS(here::here("Results/profit_ratio_quota.rds")) %>%
  .[dir_cor == "0" & ratio > 0 & ratio < 3, ] %>%
  .[, dev_w := abs(w-8), by = .(prod_het, u_dev)] %>%
  .[, .SD[dev_w == min(dev_w)], by = .(prod_het, u_dev)] %>%
  .[, .(u_dev, prod_het, ratio, prob)] %>%
  .[, instrument_type := "Quota"]

profit_ratio <- 
  rbind(profit_ratio_trading, profit_ratio_quota) %>%
  .[, prod_het := str_to_title(prod_het)] %>%
  .[, prod_het := factor(prod_het, c("Zero", "Medium", "High"))]

saveRDS(profit_ratio, here::here("Results/profit_ratio.rds"))
```

```{r}
profit_ratio <- readRDS(here::here("Results/profit_ratio.rds"))

g_profit_ratio <-
  ggplot(profit_ratio) +
  geom_line(aes(x = ratio, y = prob, color = instrument_type)) +
  facet_grid(prod_het ~ u_dev) +
  xlab("Ratio of Profit under Proxy-based to Water-based systems") +
  ylab("Cumulative Probability") +
  scale_color_discrete(name = "Insturment Type") +
  theme_bw() +
  theme(legend.position = "bottom")

ggsave("Writing/figures/g_profit_ratio.pdf", g_profit_ratio, height = 3.5, width = 6)
```

# Appendix

## The impact of correlation between measurement error and water use

Two dimensions of measurement error:

+ cross-sectional (this is what we have focused on so far)
+ temporal (due to weather)
  + implications on dynamically adjusting proxy quota (underestimation of proper quota).

### Temporal Correlation

The use of proxy quota system, irrespective or whether water or its proxy is used, water use is less than the quota. The degree of water use slack is not known to

Given, they do not observe water use and the decision variable for water manager is quota,

$$
A_i = f(\bar{W_i})
$$

In aquifer management, it is not necessary to observe water use.

### 2024-08-08 Codes/2_make_figures.rmd
Initial commit. Branching out from the original repository of Energy Regulation Welfare Loss.

# Observed measurement errors

## Data Preparation

```{r}
#--- NE data ---#
ne_data <-
  readRDS(here::here("Data/water_energy_MW.rds")) %>%
  .[nrdname != "Twin Platte", ] %>%
  .[, me := water_est - volaf] %>%
  .[, w_to_e := kwh / volaf] %>% # (kwh/feet)
  .[, region := paste0(nrdname, " (Nebraska)")]

#--- CO data ---#
# Colorado data provided by Aaron Hrozencik. Pumping tests to measure kwh/acre-feet (not throughout the season like NE data).
co_data <-
  fread(here::here("Data/CO_price_data.csv")) %>%
  setnames(c("PCC", "pumpingAF"), c("w_to_e", "volaf")) %>%
  setnames(names(.), tolower(names(.))) %>%
  .[, .(wdid, year, w_to_e, volaf)] %>%
  .[, region := "Eastern Colorado"]

data <- rbind(ne_data, co_data, fill = TRUE)
```

## Distribution of energy use efficiency

```{r}
g_hist_eta <-
  ggplot(data = data[w_to_e < 1000 & w_to_e > 100, ]) +
  geom_histogram(aes(x = w_to_e), fill = NA, color = "blue", bins = 100) +
  facet_grid(region ~ .) +
  xlab("Energy use efficiency (kwh/acre-feet)") +
  ylab("Count") +
  theme_bw() +
  theme(legend.position = "bottom")

ggsave("Results/figures/g_hist_eta.pdf", g_hist_eta, height = 4, width = 6.5)
```

## Measurement error in water use estimates

```{r, fig.dim = c(6.5, 5)}
g_me <-
  ggplot(data = data[water_est < 400, ]) +
  geom_point(aes(y = volaf, x = water_est), size = 0.1) +
  facet_grid(. ~ nrdname) +
  geom_abline(intercept = 0, slope = 1) +
  xlab("Water Use Estimates Based on Energy Use (acre-feet)") +
  ylab("Observed Water Use (acre-feet)") +
  theme_bw() +
  theme(legend.position = "bottom") +
  coord_equal() +
  scale_x_continuous(breaks = (1:9) * 100) +
  scale_y_continuous(breaks = (1:9) * 100)

ggsave("Results/figures/g_me.pdf", g_me, height = 4, width = 6.5)
```

### 2024-08-08 Codes/exploratory/exp_analysis.rmd
Initial commit. Branching out from the original repository of Energy Regulation Welfare Loss.

# Load the data
```{r}
data <-
  readRDS(here::here("Data/water_energy_MW.rds")) %>%
  .[, me := water_est - volaf] %>%
  .[me < 200, ]
```

# Map

```{r}
data %>%
  unique(by = "wellid") %>%
  sf::st_as_sf(coords = c("longdd", "latdd"), crs = 4269) %>%
  ggplot(data = .) +
  geom_sf()
```

# Water vs Energy

```{r}
w_e_reg <-
  data %>%
  nest_by(nrdname) %>%
  dplyr::filter(nrdname != "Twin Platte") %>%
  dplyr::mutate(reg_ga = list(
    mgcv::gam(volaf ~ s(kwh), data = data)
  ))
```

## Middle
```{r}
w_e_reg$reg[[1]] %>% plot()
```

## Upper

```{r}
w_e_reg$reg[[2]] %>% plot()
```

Both linear.

## Yearly energy use efficiency by NRD

Significant difference in energy use efficiency between URNRD and MRNRD. What are potential causes?

+ depth to water table
+ pumping efficiency
+ water use

```{r}
data[nrdname != "Twin Platte", ] %>%
  .[kwh != 0, ] %>%
  .[, mean(volaf / kwh, na.rm = TRUE), by = .(year, nrdname)]
```

Not sure what is going on in 2008.

# Measurement error

Water use was estimated based on enegy use by multyplying energy use with a single coefficient to all the data.

## Yearly measurement errors

```{r}
data[nrdname != "Twin Platte", ] %>%
  .[me < 200, ] %>%
  ggplot(data = .) +
  geom_point(aes(y = volaf, x = water_est), size = 0.1) +
  geom_smooth(aes(y = volaf, x = water_est), size = 0.1, method = "lm") +
  facet_grid(nrdname ~ year) +
  geom_abline(intercept = 0, slope = 1) +
  xlab("Water Use Estimates Based on Energy Use (acre-feet)") +
  ylab("Observed Water Use (acre-feet)") +
  theme_bw() +
  theme(legend.position = "bottom") +
  coord_equal() +
  scale_x_continuous(breaks = (1:9) * 100) +
  scale_y_continuous(breaks = (1:9) * 100)
```

You can observe that water use tend to be overestimated for high-water use observations.

## Yearly ME (histogram)

```{r}
data[nrdname != "Twin Platte", ] %>%
  .[, me := water_est - volaf] %>%
  .[me < 250, ] %>%
  ggplot(data = .) +
  geom_histogram(aes(x = me)) +
  geom_vline(xintercept = 0, color = "red") +
  facet_grid(year ~ nrdname)
```

### 2024-08-08 Codes/match_energy_water.rmd
Initial commit. Branching out from the original repository of Energy Regulation Welfare Loss.

# Preparation

```{r}
setwd("NebraskaWaterProjectsData")
```

# Import datasets

```{r}
#--------------------------
# Well registration
#--------------------------
# Notes:
# When subsec has four letters,
# The first two letters represent subsubseciton
# The last two letters represent subseciton
wells <- 
  fread("./Data/WellRegistrationRaw/Reg08_26_2016_Raw/all_rrb_wells.csv") %>%
  setnames(names(.), tolower(names(.))) %>%
  .[useid == "I", ] %>%
  .[, .(
    wellid, twnid, rngid, rngdir, section, subsecmnemonic,
    subsecid, nrdname, swl, pwl, totaldepth, regdate, pumprate, pumpdepth, decommissiondate,
    pumpcoldia, ownerid, wellstatusid, lastname, longdd, latdd
  )] %>%
  setnames(c("twnid", "rngid", "subsecmnemonic"), c("township", "range", "subsec")) %>%
  .[, `:=`(
    trs = paste(township, range, section, sep = "_"),
    subsection = ifelse(str_length(subsec) == 2, subsec, str_sub(subsec, 3, 4)),
    subsubsection = ifelse(str_length(subsec) == 2, NA, str_sub(subsec, 1, 2))
  )] %>%
  .[, trs_s := paste(trs, subsection, sep = "_")] %>%
  .[, trs_ss := paste(trs_s, subsubsection, sep = "_")] %>%
  setorder(township, range, section) %>%
  .[, N_sec := .N, by = .(trs)] %>%
  .[, N_sub := .N, by = .(trs_s)] %>%
  .[, N_subsub := .N, by = .(trs_ss)]

wells <- wells %>%
  mutate(
    dec_date = as.Date(decommissiondate, "%m/%d/%y"),
    dec_year = year(dec_date),
    dec_month = month(dec_date),
    inactive_not_dec = ifelse(is.na(dec_year) & wellstatusid == "X", 1, 0)
  ) %>%
  data.table()
```

```{r}
gw <-
  readRDS("./Data/Pumping/Processed/pumping.rds") %>%
  mutate(source_txt = as.character(source)) %>%
  data.table() %>%
  .[source_txt %in% c("Meter", "METER", "metered"), ] %>%
  .[, extended_id := paste(volaf, acres, year, county)] %>%
  .[, count_id := .N, by = extended_id] %>% # get rid of duplicate records
  .[count_id == 1, ]
```

## Midwest

```{r}
Midwest <- 
  readRDS("./Data/Energy/Processed/Midwest.rds") %>%
  select(year, district, rate, township, range, section, subsection, subsubsection, hp, kwh) %>%
  mutate(
    trs = paste(township, range, section, sep = "_"),
    trs_s = paste(trs, subsection, sep = "_")
  ) %>%
  arrange(township, range, section, subsection, year) %>%
  data.table() %>%
  .[, N_sec := .N, by = .(trs, year)] %>%
  .[, N_sub := .N, by = .(trs_s, year)]
#--- find wells within the Midwest PPD ---#
MW_trs_ls <- Midwest[, trs] %>% unique()
wells_MW <- wells %>%
  filter(trs %in% MW_trs_ls) %>%
  data.table()

#-----------------
# single trs-trs
#--------------------------
# pick observations that are the only record at the section level (not many)
MW_sec <- Midwest[N_sec == 1, ] %>%
  left_join(., wells_MW[N_sec == 1, ], by = "trs") %>%
  mutate(matched = ifelse(!is.na(wellid), 1, 0)) %>%
  rename(trs_s = trs_s.x) %>%
  select(
    wellid, nrdname, swl, pwl, totaldepth, trs, trs_s, year, district, rate, hp, kwh, regdate, pumprate, pumpdepth, decommissiondate,
    pumpcoldia, ownerid, wellstatusid, lastname, longdd, latdd
  ) %>%
  data.table()
# MW_sec[!is.na(wellid),]

#--------------------------
# single trs_s-trs_s
#--------------------------
# pick observations that are the only record at the subsection level
#--- the only energy record at the subsection level ---#
MW_sub <- Midwest[N_sub == 1 & N_sec > 1, ] %>%
  left_join(., wells_MW[N_sub == 1 & N_sec > 1, ], by = "trs_s") %>%
  mutate(matched = ifelse(!is.na(wellid), 1, 0)) %>%
  rename(trs = trs.x) %>%
  select(
    wellid, nrdname, swl, pwl, totaldepth, trs, trs_s, year, district, rate, hp, kwh, regdate, pumprate, pumpdepth, decommissiondate,
    pumpcoldia, ownerid, wellstatusid, lastname, longdd, latdd
  ) %>%
  data.table()
# matched_sub <- MW_sub[!is.na(wellid),]
# unmatched_sub <- MW_sub[is.na(wellid),]

#--------------------------
# merge with pumping data
#--------------------------
# only MW_sub and MW_sec for now. later add MW_sub_2
MW_we <- rbind(MW_sec, MW_sub) %>%
  left_join(gw, ., by = c("wellid", "year")) %>%
  filter(!is.na(district)) %>%
  data.table()
#-------------------
# pick observations that are the only record at the section level (not many)
MW_sec <- Midwest[N_sec == 1, ] %>%
  left_join(., wells_MW[N_sec == 1, ], by = "trs") %>%
  mutate(matched = ifelse(!is.na(wellid), 1, 0)) %>%
  rename(trs_s = trs_s.x) %>%
  select(
    wellid, nrdname, swl, pwl, totaldepth, trs, trs_s, year, district, rate, hp, kwh, regdate, pumprate, pumpdepth, decommissiondate,
    pumpcoldia, ownerid, wellstatusid, lastname, longdd, latdd
  ) %>%
  data.table()
```

# Midwest
```{r}
Midwest <- 
  readRDS("./Data/Energy/Processed/Midwest.rds") %>%
  select(year, district, rate, township, range, section, subsection, subsubsection, hp, kwh) %>%
  mutate(
    trs = paste(township, range, section, sep = "_"),
    trs_s = paste(trs, subsection, sep = "_")
  ) %>%
  arrange(township, range, section, subsection, year) %>%
  data.table() %>%
  .[, N_sec := .N, by = .(trs, year)] %>%
  .[, N_sub := .N, by = .(trs_s, year)]

#--- find wells within the Midwest PPD ---#
MW_trs_ls <- Midwest[, trs] %>% unique()

wells_MW <- wells %>%
  filter(trs %in% MW_trs_ls) %>%
  data.table()

#--------------------------
# single trs-trs
#--------------------------
# pick observations that are the only record at the section level (not many)
MW_sec <- 
  Midwest[N_sec == 1, ] %>%
  left_join(., wells_MW[N_sec == 1, ], by = "trs") %>%
  mutate(matched = ifelse(!is.na(wellid), 1, 0)) %>%
  rename(trs_s = trs_s.x) %>%
  dplyr::select(
    wellid, nrdname, swl, pwl, totaldepth, trs, trs_s, year, district, rate, hp, kwh, regdate, pumprate, pumpdepth, decommissiondate,
    pumpcoldia, ownerid, wellstatusid, lastname, longdd, latdd
  ) %>%
  data.table()
# MW_sec[!is.na(wellid),]
#--------------------------
# single trs_s-trs_s
#--------------------------
# pick observations that are the only record at the subsection level
#--- the only energy record at the subsection level ---#
MW_sub <- 
  Midwest[N_sub == 1 & N_sec > 1, ] %>%
  left_join(., wells_MW[N_sub == 1 & N_sec > 1, ], by = "trs_s") %>%
  mutate(matched = ifelse(!is.na(wellid), 1, 0)) %>%
  rename(trs = trs.x) %>%
  dplyr::select(
    wellid, nrdname, swl, pwl, totaldepth, trs, trs_s, year, district, rate, hp, kwh, regdate, pumprate, pumpdepth, decommissiondate,
    pumpcoldia, ownerid, wellstatusid, lastname, longdd, latdd
  ) %>%
  data.table()

# only MW_sub and MW_sec for now. later add MW_sub_2
MW_we <- 
  rbind(MW_sec, MW_sub) %>%
  left_join(gw, ., by = c("wellid", "year")) %>%
  filter(!is.na(district)) %>%
  data.table()
#--------------------------
MW_we <- MW_we %>%
  .[, w_to_e := volaf * 12 / kwh] %>%
  .[is.infinite(w_to_e), w_to_e := NA] %>%
  .[, coef_var := var(w_to_e, na.rm = TRUE) / mean(w_to_e, na.rm = TRUE), by = .(wellid)]

well_ls <- MW_we[, wellid] %>% unique()
well_len <- length(well_ls)

# According to visual inspections, coef_var<7e-4 seems acceptable
MW_matched_1st <- 
  MW_we[coef_var < 7e-4, ] %>%
  select(
    wellid, nrdname, swl, pwl, totaldepth, year, acres, volaf, source, source_txt,
    trs, trs_s, district, rate, hp, kwh, regdate, pumprate, pumpdepth,
    decommissiondate, pumpcoldia, ownerid, wellstatusid,
    lastname, longdd, latdd, w_to_e, coef_var
  ) %>%
  data.table()

```

# multiple wells and multiple energy records in the same trs

```{r}
matched_well_ls <- MW_matched_1st[, wellid] %>% unique()
matched_trs_s_ls <- MW_matched_1st[, trs_s] %>% unique()
wells_2nd <- wells_MW[!(wellid %in% matched_well_ls), ]
e_2nd <- Midwest[!(trs_s %in% matched_trs_s_ls), ]
temp_match_2nd <- e_2nd[N_sub == 1, ] %>%
  left_join(., wells_2nd, by = "trs") %>%
  left_join(., gw, by = c("wellid", "year")) %>%
  mutate(matched = ifelse(!is.na(wellid), 1, 0)) %>%
  filter(matched == 1) %>%
  rename(trs_s = trs_s.x) %>%
  select(
    wellid, nrdname, swl, pwl, totaldepth, trs, trs_s, year, volaf, acres, source_txt, source, hp,
    kwh, regdate, pumprate, pumpdepth, decommissiondate, district, rate,
    pumpcoldia, ownerid, wellstatusid, lastname, longdd, latdd, matched
  ) %>%
  mutate(well_trs_s = paste(wellid, trs_s, sep = "_")) %>%
  mutate(w_to_e = volaf * 12 / kwh) %>%
  filter(!is.na(volaf)) %>%
  arrange(well_trs_s, year) %>%
  data.table() %>%
  .[is.infinite(w_to_e), w_to_e := NA] %>%
  .[, coef_var := var(w_to_e, na.rm = TRUE) / mean(w_to_e, na.rm = TRUE), by = .(well_trs_s)]
#--- list of the trs ---#
trs_ls <- temp_match_2nd[, trs] %>% unique()
trs_len <- length(trs_ls)
#++++++++++++++++
matched_store_all <- list()
for (i in 1:trs_len) { # loop over trs
  #--- select well-energy records combinations in the temporary trs ---#
  temp_match <- temp_match_2nd[trs == trs_ls[i] & !is.na(coef_var), .(well_trs_s, wellid, trs_s, coef_var)] %>%
    unique(by = "well_trs_s")
  well_len <- temp_match[, wellid] %>%
    unique() %>%
    length()
  matched_store_i <- list()
  for (j in 1:well_len) { # loop over wells
    if (min(temp_match[, coef_var]) < 7e-4) { # if there is a match
      #--- identify the best matching well-energy combination ---#
      min_index <- which.min(temp_match[, coef_var])
      get_well <- temp_match[min_index, wellid]
      get_trs_s <- temp_match[min_index, trs_s]
      #--- extract the matched data and store in the temporary storage ---#
      matched_store_i[[j]] <- temp_match_2nd %>%
        filter(wellid == get_well & trs_s == get_trs_s) %>%
        data.table()
      #--- exclude the matched wellid and energy records  ---#
      temp_match <- temp_match %>%
        filter(!(wellid == get_well | trs_s == get_trs_s)) %>%
        data.table()
    } else { # if no good enough matches
      break # end the loop
    }
  }
  matched_store_all[[i]] <- rbindlist(matched_store_i)
}

MW_matched_2nd <- rbindlist(matched_store_all) %>%
  select(
    wellid, nrdname, swl, pwl, totaldepth, year, acres, volaf, source, source_txt,
    trs, trs_s, district, rate, hp, kwh, regdate, pumprate, pumpdepth,
    decommissiondate, pumpcoldia, ownerid, wellstatusid,
    lastname, longdd, latdd, w_to_e, coef_var
  ) %>%
  data.table()

# Notes:
# According to visual inspections, coef_var<7e-4 seems acceptable

MW_matched_1st <- MW_we[coef_var < 7e-4, ] %>%
  dplyr::select(
    wellid, nrdname, swl, pwl, totaldepth, year, acres, volaf, source, source_txt,
    trs, trs_s, district, rate, hp, kwh, regdate, pumprate, pumpdepth,
    decommissiondate, pumpcoldia, ownerid, wellstatusid,
    lastname, longdd, latdd, w_to_e, coef_var
  ) %>%
  data.table()
```

## Multiple wells and multiple energy records in the same trs

```{r}
matched_well_ls <- MW_matched_1st[, wellid] %>% unique()
matched_trs_s_ls <- MW_matched_1st[, trs_s] %>% unique()
wells_2nd <- wells_MW[!(wellid %in% matched_well_ls), ]
e_2nd <- Midwest[!(trs_s %in% matched_trs_s_ls), ]
temp_match_2nd <- e_2nd[N_sub == 1, ] %>%
  left_join(., wells_2nd, by = "trs") %>%
  left_join(., gw, by = c("wellid", "year")) %>%
  mutate(matched = ifelse(!is.na(wellid), 1, 0)) %>%
  filter(matched == 1) %>%
  rename(trs_s = trs_s.x) %>%
  dplyr::select(
    wellid, nrdname, swl, pwl, totaldepth, trs, trs_s, year, volaf, acres, source_txt, source, hp,
    kwh, regdate, pumprate, pumpdepth, decommissiondate, district, rate,
    pumpcoldia, ownerid, wellstatusid, lastname, longdd, latdd, matched
  ) %>%
  mutate(well_trs_s = paste(wellid, trs_s, sep = "_")) %>%
  mutate(w_to_e = volaf * 12 / kwh) %>%
  filter(!is.na(volaf)) %>%
  arrange(well_trs_s, year) %>%
  data.table() %>%
  .[is.infinite(w_to_e), w_to_e := NA] %>%
  .[, coef_var := var(w_to_e, na.rm = TRUE) / mean(w_to_e, na.rm = TRUE), by = .(well_trs_s)]
#--- list of the trs ---#
trs_ls <- temp_match_2nd[, trs] %>% unique()
trs_len <- length(trs_ls)
#++++++++++++++++
# loop over trs to find matches
#++++++++++++++++
matched_store_all <- list()
for (i in 1:trs_len) { # loop over trs
  #--- select well-energy records combinations in the temporary trs ---#
  temp_match <- temp_match_2nd[trs == trs_ls[i] & !is.na(coef_var), .(well_trs_s, wellid, trs_s, coef_var)] %>%
    unique(by = "well_trs_s")
  well_len <- temp_match[, wellid] %>%
    unique() %>%
    length()
  matched_store_i <- list()
  for (j in 1:well_len) { # loop over wells
    if (min(temp_match[, coef_var]) < 7e-4) { # if there is a match
      #--- identify the best matching well-energy combination ---#
      min_index <- which.min(temp_match[, coef_var])
      get_well <- temp_match[min_index, wellid]
      get_trs_s <- temp_match[min_index, trs_s]
      #--- extract the matched data and store in the temporary storage ---#
      matched_store_i[[j]] <- temp_match_2nd %>%
        filter(wellid == get_well & trs_s == get_trs_s) %>%
        data.table()
      #--- exclude the matched wellid and energy records  ---#
      temp_match <- temp_match %>%
        filter(!(wellid == get_well | trs_s == get_trs_s)) %>%
        data.table()
    } else { # if no good enough matches
      break # end the loop
    }
  }
  matched_store_all[[i]] <- rbindlist(matched_store_i)
}

MW_matched_2nd <- rbindlist(matched_store_all) %>%
  dplyr::select(
    wellid, nrdname, swl, pwl, totaldepth, year, acres, volaf, source, source_txt,
    trs, trs_s, district, rate, hp, kwh, regdate, pumprate, pumpdepth,
    decommissiondate, pumpcoldia, ownerid, wellstatusid,
    lastname, longdd, latdd, w_to_e, coef_var
  ) %>%
  data.table()
# ggplot

MW_we <- rbind(MW_matched_1st, MW_matched_2nd) %>%
  .[, hours := kwh / (hp * 0.746)] %>%
  .[, gpm := (volaf * 12 * 27154) / (hours * 60)]
MW_we[, wellid] %>% unique()
matched_all_ls <- MW_we[, wellid] %>% unique()
length(matched_all_ls)
wells_MW
unmatched_all_ls
all_wells_MW
all_wells_MW
#--------------------------
MW_we <- MW_we %>%
  .[, w_to_e := volaf * 12 / kwh] %>%
  .[is.infinite(w_to_e), w_to_e := NA] %>%
  .[, coef_var := var(w_to_e, na.rm = TRUE) / mean(w_to_e, na.rm = TRUE), by = .(wellid)]
well_ls <- MW_we[, wellid] %>% unique()
well_len <- length(well_ls)
#--- find wells within the Midwest PPD ---#
MW_trs_ls <- Midwest[, trs] %>% unique()
wells_MW <- wells %>%
  filter(trs %in% MW_trs_ls) %>%
  data.table()
wells_MW
wells_MW
matched_all_ls <- MW_we[, wellid] %>% unique()
matched_all_ls <- MW_we[, wellid] %>% unique()
u
unmatched_all_ls <- wells_MW[!(wellid %in% matched_all_ls), ]
unmatched_all_ls
matched_all_ls <- MW_we[, wellid] %>% unique()
unmatched_all_ls <- wells_MW[!(wellid %in% matched_all_ls), wellid] %>% unique()
unmatched_all_ls
matched_all_ls
length(unmatched_all_ls)
saveRDS(matched_all_ls, "./Data/Water_Energy/matched_wells_MW.rds")
saveRDS(unmatched_all_ls, "./Data/Water_Energy/unmatched_wells_MW.rds")
saveRDS(MW_trs_ls, "./Data/Water_Energy/MW_trs_ls.rds")
```

```{r}
all_gw
all_gw <- readRDS("~/Dropbox/NebraskaWaterProjectsData/Data/Pumping/Processed/pumping.rds") %>%
  mutate(source_txt = as.character(source)) %>%
  data.table() %>%
  .[source_txt %in% c("Meter", "METER", "metered"), ] %>%
  .[, extended_id := paste(volaf, acres, year, county)] %>%
  .[, count_id := .N, by = extended_id] %>% # get rid of duplicate records
  .[count_id == 1, ]
all_gw
wells <- fread("~/Dropbox/NebraskaWaterProjectsData/Data/WellRegistrationRaw/Reg08_26_2016_Raw/all_rrb_wells.csv") %>%
  setnames(names(.), tolower(names(.))) %>%
  .[useid == "I", ] %>%
  .[, .(
    wellid, twnid, rngid, rngdir, section, subsecmnemonic,
    subsecid, nrdname, swl, pwl, totaldepth, regdate, pumprate, pumpdepth, decommissiondate,
    pumpcoldia, ownerid, wellstatusid, lastname, longdd, latdd
  )] %>%
  setnames(c("twnid", "rngid", "subsecmnemonic"), c("township", "range", "subsec")) %>%
  .[, `:=`(
    trs = paste(township, range, section, sep = "_"),
    subsection = ifelse(str_length(subsec) == 2, subsec, str_sub(subsec, 3, 4)),
    subsubsection = ifelse(str_length(subsec) == 2, NA, str_sub(subsec, 1, 2))
  )] %>%
  .[, trs_s := paste(trs, subsection, sep = "_")] %>%
  .[, trs_ss := paste(trs_s, subsubsection, sep = "_")] %>%
  setorder(township, range, section) %>%
  .[, N_sec := .N, by = .(trs)] %>%
  .[, N_sub := .N, by = .(trs_s)] %>%
  .[, N_subsub := .N, by = .(trs_ss)]
# wells[N_sub>4,]
#
wells <- fread("~/Dropbox/NebraskaWaterProjectsData/Data/WellRegistrationRaw/Reg08_26_2016_Raw/all_rrb_wells.csv") %>%
  setnames(names(.), tolower(names(.))) %>%
  .[useid == "I", ] %>%
  .[, .(
    wellid, twnid, rngid, rngdir, section, subsecmnemonic,
    subsecid, nrdname, swl, pwl, totaldepth, regdate, pumprate, pumpdepth, decommissiondate,
    pumpcoldia, ownerid, wellstatusid, lastname, longdd, latdd
  )] %>%
  setnames(c("twnid", "rngid", "subsecmnemonic"), c("township", "range", "subsec")) %>%
  .[, `:=`(
    trs = paste(township, range, section, sep = "_"),
    subsection = ifelse(str_length(subsec) == 2, subsec, str_sub(subsec, 3, 4)),
    subsubsection = ifelse(str_length(subsec) == 2, NA, str_sub(subsec, 1, 2))
  )]
all_gw <- readRDS("~/Dropbox/NebraskaWaterProjectsData/Data/Pumping/Processed/pumping.rds") %>%
  mutate(source_txt = as.character(source)) %>%
  data.table() %>%
  .[source_txt %in% c("Meter", "METER", "metered"), ] %>%
  .[, count_id := .N, by = extended_id] %>% # get rid of duplicate records
  .[count_id == 1, ] %>%
  wells[., on = "wellid"]
all_gw <- readRDS("~/Dropbox/NebraskaWaterProjectsData/Data/Pumping/Processed/pumping.rds") %>%
  mutate(source_txt = as.character(source)) %>%
  data.table() %>%
  .[source_txt %in% c("Meter", "METER", "metered"), ] %>%
  .[, extended_id := paste(volaf, acres, year, county)] %>%
  .[, count_id := .N, by = extended_id] %>% # get rid of duplicate records
  .[count_id == 1, ] %>%
  wells[., on = "wellid"]
all_gw <- readRDS("~/Dropbox/NebraskaWaterProjectsData/Data/Pumping/Processed/pumping.rds") %>%
  mutate(source_txt = as.character(source)) %>%
  data.table() %>%
  .[source_txt %in% c("Meter", "METER", "metered"), ] %>%
  wells[., on = "wellid"]
all_gw
MW_wells <- readRDS("~/Dropbox/NebraskaWaterProjectsData/Data/Pumping/Processed/pumping.rds") %>%
  mutate(source_txt = as.character(source)) %>%
  data.table() %>%
  .[source_txt %in% c("Meter", "METER", "metered"), ] %>%
  wells[., on = "wellid"] %>%
  .[trs %in% MW_trs_ls, ]
MW_wells
wells <- fread("~/Dropbox/NebraskaWaterProjectsData/Data/WellRegistrationRaw/Reg08_26_2016_Raw/all_rrb_wells.csv") %>%
  setnames(names(.), tolower(names(.))) %>%
  .[useid == "I", ] %>%
  .[, .(
    wellid, twnid, rngid, rngdir, section, subsecmnemonic,
    subsecid, nrdname, swl, pwl, totaldepth, regdate, pumprate, pumpdepth, decommissiondate,
    pumpcoldia, ownerid, wellstatusid, lastname, longdd, latdd
  )] %>%
  setnames(c("twnid", "rngid", "subsecmnemonic"), c("township", "range", "subsec")) %>%
  .[, `:=`(
    trs = paste(township, range, section, sep = "_"),
    subsection = ifelse(str_length(subsec) == 2, subsec, str_sub(subsec, 3, 4)),
    subsubsection = ifelse(str_length(subsec) == 2, NA, str_sub(subsec, 1, 2))
  )]
matched_all_ls <- readRDS("./Data/Water_Energy/matched_wells_MW.rds")
unmatched_all_ls <- readRDS("./Data/Water_Energy/unmatched_wells_MW.rds")
MW_wells <- readRDS("~/Dropbox/NebraskaWaterProjectsData/Data/Pumping/Processed/pumping.rds") %>%
  mutate(source_txt = as.character(source)) %>%
  data.table() %>%
  .[source_txt %in% c("Meter", "METER", "metered"), ] %>%
  wells[., on = "wellid"] %>%
  .[, matched := NA] %>%
  .[wellid %in% matched_all_ls, matched := TRUE] %>%
  .[wellid %in% unmatched_all_ls, matched := FALSE] %>%
  .[!is.na(matched), ]
MW_wells
MW_wells[, .(volaf, acres), by = .(matched, year)]
MW_wells[, .(volaf = mean(volaf), acres = mean(acres)), by = .(matched, year)]
MW_wells[, .(volaf = mean(volaf), acres = mean(acres)), by = .(matched)]
MW_wells[, .(volaf = mean(volaf, na.rm = TRUE), acres = mean(acres, na.rm = TRUE)), by = .(matched, year)]
MW_wells[, .(volaf = mean(volaf, na.rm = TRUE), acres = mean(acres, na.rm = TRUE)), by = .(matched)]
```

### 2024-08-08 Codes/predict_from_energy.rmd
Initial commit. Branching out from the original repository of Energy Regulation Welfare Loss.

# Predict water use from energy use data

# Preparation
```{r}
# data <-
#   fread("Data/water_energy_MW.csv") %>%
#   .[, mean_w_to_e := mean(w_to_e, na.rm = TRUE), by = nrdname] %>%
#   .[, water_est := kwh * mean_w_to_e / 12]

# saveRDS(data, "Data/water_energy_MW.rds")

data <- readRDS("Data/water_energy_MW.rds")
```

# Naive water use prediction

```{r}
ggplot(data = data[nrdname != "Twin Platte", ]) +
  geom_point(aes(y = volaf, x = water_est), size = 0.1) +
  facet_grid(year ~ nrdname) +
  geom_abline(intercept = 0, slopw = 1) +
  xlab("Water Use Estimates Based on Energy Use (acre-feet)") +
  ylab("Observed Water Use (acre-feet)") +
  theme(
    legend.position = "bottom"
  )
ggsave("./Graphs/how_good_energy.pdf", height = 10, width = 6)

ggplot(data = data[!is.na(w_to_e) & nrdname != "Twin Platte", ]) +
  geom_boxplot(aes(y = w_to_e, x = factor(year)), alpha = 0.3) +
  facet_grid(nrdname ~ .) +
  ylab("Water (acre-feet)/Energy (kwh)") +
  xlab("Year")

ggsave("./Graphs/water_to_energy.pdf")

ggplot(data = data[!is.na(w_to_e) & nrdname != "Twin Platte", ]) +
  geom_density(aes(x = w_to_e, fill = factor(year)), alpha = 0.3) +
  facet_grid(nrdname ~ .) +
  ylab("Water (acre-feet)/Energy (kwh)") +
  xlab("Year")

ggsave("./Graphs/water_to_energy.pdf")
```

### 2024-08-08 Codes/production_function.rmd
Initial commit. Branching out from the original repository of Energy Regulation Welfare Loss.

# Data Preparation

```{r}
# Read in matlab data
yield_water <- readMat("Data/ProductionFunction_October2017.mat")

# Acess the data within the array
yiedl_water_array <- yield_water$ProductionFunction.October2017
```

# Extract and transform data by variable

Extracting crop yield and irrigation data from an array and compute expected value given an irrigation strategy

```{r}
#--------------------------
# Yield
#--------------------------
yield_data <- yiedl_water_array[[1]] %>%
  t() %>%
  data.table() %>%
  .[, smt := 1:nrow(.)] %>%
  melt(id.var = "smt") %>%
  setnames(c("variable", "value"), c("year", "yield")) %>%
  .[, yield := yield / 0.06] %>%
  .[, year := as.numeric(gsub("V", "", year))] %>%
  setkey(smt, year)

#--- Expected crop yield ---#
e_yield <- yield_data[, .(e_yield = mean(yield)), by = smt] %>%
  setkey(smt)

#--------------------------
# Irrigation
#--------------------------
irr_data <- yiedl_water_array[[2]] %>%
  t() %>%
  data.table() %>%
  .[, smt := 1:nrow(.)] %>%
  melt(id.var = "smt") %>%
  setnames(c("variable", "value"), c("year", "ir")) %>%
  .[, year := as.numeric(gsub("V", "", year))] %>%
  .[, ir := ir * 0.0393701] %>%
  setkey(smt, year)

#--- expected irrigation ---#
e_ir <- irr_data[, .(e_ir = mean(ir)), by = smt] %>%
  setkey(smt)

#--------------------------
# Combine and save
#--------------------------
#--- raw data ---#
raw_data <- yield_data[irr_data]
```

# Find the maximum yield by irrigation bin for each year

```{r}
year_ls <- raw_data[, year] %>% unique()
prod_store <- list()

for (y in year_ls) {
  temp_data <- 
    copy(raw_data[year == y, ]) %>%
    .[, ir_bin := cut(ir, c(quantile(ir, prob = seq(0, 1, by = 0.05))) %>% unique())] %>%
    .[, ir_bin := as.character(ir_bin)] %>%
    .[is.na(ir_bin), ir_bin := "0"] %>%
    .[, .(yield = max(yield), ir = mean(ir)), by = ir_bin] %>%
    .[, ir_bin := NULL] %>%
    #--- get rid of observations that saw a decline in yield  ---#
    setorder(ir) %>%
    .[, yield_prev := shift(yield, n = 1, type = "lag")] %>%
    .[, dif := yield - yield_prev] %>%
    .[dif > 0 | is.na(dif), ] %>%
    .[, .(yield, ir)]

  if (y == 11) { # special treatment for year 12
    temp_data[ir == 0, yield := 194]
  }
  # g_reg <- ggplot(data=reg_data) +
  # 	geom_point(aes(y=yield,x=ir))
  # ggsave(g_reg,file=paste('./Figures/reg_data_y_',y,'.pdf',sep=''))

  #--- augment data for a better fitting ---#
  max_yield <- temp_data[, max(yield)]
  max_ir <- temp_data[, max(ir)]
  min_ir_data <- temp_data[ir == min(ir), ][rep(1, 5), ]
  max_ir_data <- data.table(
    yield = rep(max_yield, 15),
    ir = max_ir + seq(0, max_ir * 0.2, length = 15)
  )
  reg_data <- rbind(min_ir_data, temp_data, max_ir_data)
  prod_store[[as.character(y)]] <- scam(yield ~ s(ir, k = 7, bs = "micv"), data = reg_data)
}

saveRDS(prod_store, "Results/prod_fcn.rds")
```

# Visualize the production functions

```{r}
for (y in year_ls) {
  temp_prod <- prod_store[[paste(y)]]
  g_temp <- data.table(ir = seq(
    floor(min(temp_prod$model$ir) * 100) / 100,
    floor(max(temp_prod$model$ir) * 100) / 100,
    by = 0.05
  )) %>%
    .[, y_hat := predict(temp_prod, newdata = .)] %>%
    ggplot(data = .) +
    geom_line(aes(y = y_hat, x = ir))
  ggsave(g_temp, file = paste("Figures/production_function/prod_y_", y, ".pdf", sep = ""))
}
```

### 2024-08-08 Codes/welfare_analysis.Rmd
Initial commit. Branching out from the original repository of Energy Regulation Welfare Loss.

--- 
title: "Regulating water by energy: welfare implications of energy use efficiency heterogeneity"
author: ""
date: "`r Sys.Date()`"
output:
  html_document:
    number_sections: yes
    theme: flatly
    toc_float: yes
    toc: yes
    toc_depth: 3
---

```{r }
#--- production function by year ---#
prod_store <- readRDS("Results/prod_fcn.rds")
```

```{r }
# ===================================
# Data preparation
# ===================================
data <-
  readRDS("Data/water_energy_MW.rds") %>%
  #--- focus only on URNRD ---#
  .[nrdname == "Upper Republican", ] %>%
  #--- energy use efficiency (amount of energy needed to apply an acre-inch of water) ---#
  .[, e_ef := kwh / (volaf * 12)] %>%
  #--- average energy use efficiency ---#
  .[, median_e_ef := median(e_ef, na.rm = TRUE)] %>%
  #--- (unbiased) estimated water use ---#
  .[, water_est := kwh / median_e_ef / 12] %>%
  #--- loser and winner ---#
  .[, type := ifelse(water_est > volaf, "Loser", "Winner")]
```
# Theory

Suppose the profit function is quadratic locally (within the range that is relevant) as follows 
$$
\begin{aligned}
\pi=\beta_0+\beta_1 \cdot w-\beta_2\cdot w^2
\end{aligned}
$$
where $\beta_0>0$, $\beta_1>0$ and $\beta_2>0$. Profit is a quadratic function of water, and the marginal profit of water is linear. Further, suppose the water use limit is $\bar{w}$. Let $e$ denote the water use limit error induced by the heterogeneity of energy use efficiency. The distribution of the error is represented by $f(e)$, which satisfies $E[e]=0$ (average error is zero). Finally, suppose $\bar{w}+e<w^*$ where $w^*$ is the optimal water use if it were not for the de facto water use limits (all the producers are constrained).

Then, the profit under the energy use limit scheme is as follows:
$$
\begin{aligned}
E[\pi] & = \int_{-a}^a \Big[ \beta_0+\beta_1 \cdot (w+e)-\beta_2\cdot (w+e)^2 \Big] f(e) de \\
	& = \phi\int_{-a}^a \Big[ (\beta_0+\beta_1 \cdot w-\beta_2\cdot w^2) + (\beta_1 -2\beta_2 \cdot w)\cdot e-\beta_2\cdot e^2 \Big] f(e) de \\
	& = (\beta_0+\beta_1 \cdot w-\beta_2\cdot w^2)+(\beta_1 -2\beta_2 \cdot w)\cdot E[e] -\beta_2\cdot Var(e) \\
	& = (\beta_0+\beta_1 \cdot w-\beta_2\cdot w^2)-\beta_2\cdot Var(e) 
\end{aligned}
$$
Since the expected profit under the water use limit is $(\beta_0+\beta_1 \cdot w-\beta_2\cdot w^2)$, the expected economic loss is $\beta_2\cdot Var(e)$, which is linear in the variance of the error.

<!-- ## General case: Jensen's inequality
$$
\begin{aligned}
E[\pi] & = \int_{-a}^a g(e) f(e) de \\
	& = \phi\int_{-a}^a \Big[ \bar{w}^2+2\cdot\bar{w}\cdot e + \cdot e^2 \Big] f(e) de \\
	& = \phi\bar{w}^2+2\phi\cdot\bar{w}\cdot E[e] + \phi V(e) \\
	& = \phi\bar{w}^2+\phi V(e)
\end{aligned}
$$ -->

# Water Use Estimation Method

1. find the energy use efficiency (the amount of energy needed to apply an acre-inch of water) by dividing energy use (kwh) by water use (acre-feet) for each well
2. calculate the median energy use efficiency, which provides the unbiased energy use efficiency (unbiased in the sense that losers and winners are 50-50)
3. multiply energy use by the average energy use efficiency to obtain water use estimate

# Basic data visualization

## Degrees of Error by Year
```{r, fig.width=10,fig.height=10,out.height='1000px',out.width='1000px'}
ggplot(data = data) +
  geom_point(aes(x = volaf, y = water_est, color = type), size = 0.1) +
  facet_wrap(year ~ ., strip.position = "top") +
  geom_abline(intercept = 0, slope = 1) +
  ylab("Water Use Estimates Based on Energy Use (acre-feet)") +
  xlab("Observed Water Use (acre-feet)") +
  theme(
    legend.position = "bottom"
  )
```

# Welfare loss analysis: set up

## Production functions

There are 35 years of production function estimated for URNRD using AquaCrop available. Unfortunately, I do not know which year each AquaCrop production year corresponds to. So, for now, I apply the energy use efficiency numbers observed in 2013 for the wet and medium years and 2012 for dry years. Here are the production functions I will use.

### wet year
```{r }
temp_prod <- prod_store[[paste(12)]]
data.table(ir = seq(
  floor(min(temp_prod$model$ir) * 100) / 100,
  floor(max(temp_prod$model$ir) * 100) / 100,
  by = 0.05
)) %>%
  .[, y_hat := predict(temp_prod, newdata = .)] %>%
  ggplot(data = .) +
  geom_line(aes(y = y_hat, x = ir)) +
  ylab("Yield (bu/acre)") +
  xlab("Water Use (inches/acre)")
```

### medium year
```{r }
temp_prod <- prod_store[[paste(8)]]
data.table(ir = seq(
  floor(min(temp_prod$model$ir) * 100) / 100,
  floor(max(temp_prod$model$ir) * 100) / 100,
  by = 0.05
)) %>%
  .[, y_hat := predict(temp_prod, newdata = .)] %>%
  ggplot(data = .) +
  geom_line(aes(y = y_hat, x = ir)) +
  ylab("Yield (bu/acre)") +
  xlab("Water Use (inches/acre)")
```

### dry year
```{r }
temp_prod <- prod_store[[paste(19)]]
data.table(ir = seq(
  floor(min(temp_prod$model$ir) * 100) / 100,
  floor(max(temp_prod$model$ir) * 100) / 100,
  by = 0.05
)) %>%
  .[, y_hat := predict(temp_prod, newdata = .)] %>%
  ggplot(data = .) +
  geom_line(aes(y = y_hat, x = ir)) +
  ylab("Yield (bu/acre)") +
  xlab("Water Use (inches/acre)")
```

## Water and energy use limits scheme

Energy use per acre that achieves 13 inches/acre limit is `r round(data[,unique(median_e_ef)*13],digits=2)` kwh.

```{r }
w_lim <- 13
data[, e_lim := median_e_ef * 13] %>%
  #--- water use limit ---#
  .[, w_max := e_lim / e_ef]
```

De facto water use limit distribution is presented below:

```{r }
ggplot(data = data[year == 2013, ]) +
  geom_histogram(aes(x = w_max, fill = type), alpha = 0.8, color = "black") +
  xlab("De facto water use limit (inches/acre)") +
  scale_fill_discrete(name = "")
```

## Other parameters

+ corn price: $3.5/bu
+ energy cost: $0.1/kwh

```{r }
p_corn <- 3.5
p_e <- 0.1
```

# Welfare loss comparison: results

```{r}
prod_year_len <- length(prod_store)

sim_results <-
  data.table(prod_year = seq_len(prod_year_len)) %>%
  rowwise() %>%
  dplyr::mutate(sim_data = list(
    sim_ir_welfare(data, prod_year)
  )) %>%
  dplyr::mutate(g_ir_uc = list(
    ggplot(data = sim_data) +
      geom_histogram(aes(x = ir_u), fill = "blue", color = "black", alpha = 0.5) +
      xlab("Optimal Water Use (unconstrained)") +
      ylab("")
  )) %>%
  dplyr::mutate(g_welfare_loss = list(
    sim_data %>%
      .[, .(pi_loss_elim, pi_loss_wlim)] %>%
      .[, id := 1:.N] %>%
      melt(id.vars = "id") %>%
      .[, type := ifelse(variable == "pi_loss_wlim", "Water Use Limits", "Energy Use Limits")] %>%
      ggplot(data = .) +
      geom_histogram(aes(value)) +
      facet_grid(type ~ .) +
      xlab("Economic Loss Relative to the Unconstrained Case ($/acre)")
  ))
```

```{r}
sim_ir_welfare <- function(data, prod_year, w_seq_len = 1000) {
  #++++++++++++++++++++++++++++++++++++
  #+ Debug
  #++++++++++++++++++++++++++++++++++++
  # prod_year <- 19

  #++++++++++++++++++++++++++++++++++++
  #+ Main
  #++++++++++++++++++++++++++++++++++++
  #--- extract production function ---#
  temp_prod <- prod_store[[paste(prod_year)]]

  #--- number of wells ---#
  well_len <- data[year == 2013, wellid] %>% length()

  opt_ir_uc <-
    data[year == 2013, ] %>%
    .[, .(wellid, e_ef, w_max)] %>%
    .[rep(1:nrow(.), each = w_len), ] %>%
    .[, ir := rep(seq(min(temp_prod$model$ir), max(temp_prod$model$ir), length = w_seq_len), well_len)] %>%
    .[, e_use := ir * e_ef] %>%
    .[, y_hat := predict(temp_prod, newdata = .)] %>%
    .[, pi_hat := p_corn * y_hat - p_e * e_use] %>%
    .[, .SD[which.max(pi_hat), ], by = wellid] %>%
    #--- unconstrained optimal water use ---#
    .[, ir_u := ir] %>%
    #--------------------------
    # Energy use limit
    #--------------------------
    #--- constrained water use ---#
    .[, ir := pmin(ir_u, w_max)] %>%
    .[, y_hat_elim := predict(temp_prod, newdata = .)] %>%
    setnames("ir", "ir_elim") %>%
    #--- constrained profit ---#
    .[, e_use_elim := ir_elim * e_ef] %>%
    .[, pi_hat_elim := p_corn * y_hat_elim - p_e * e_use_elim] %>%
    .[, pi_loss_elim := pi_hat - pi_hat_elim] %>%
    #--------------------------
    # Water use limit
    #--------------------------
    #--- constrained water use ---#
    .[, ir := pmin(ir_u, w_lim)] %>%
    .[, y_hat_wlim := predict(temp_prod, newdata = .)] %>%
    setnames("ir", "ir_wlim") %>%
    #--- constrained profit ---#
    .[, e_use_wlim := ir_wlim * e_ef] %>%
    .[, pi_hat_wlim := p_corn * y_hat_wlim - p_e * e_use_wlim] %>%
    .[, pi_loss_wlim := pi_hat - pi_hat_wlim]
}
```

## wet year

```{r}
prod_year <- 12
```

Here is the distribution of unconstrained optimal water use:

```{r }
sim_results$g_ir_uc[[prod_year]]
```

Profit loss (compared to the unconstrained profit) distribution:

```{r }
sim_results$g_welfare_loss[[prod_year]]
```

No wells are constrained in both energy and water use limits scheme. But, it is possible in a little bit more dry year that some wells are constrained under the energy use limit scheme while no wells are constrained under the water use limit scheme.

## Medium year

```{r}
prod_year <- 8
```

Profit loss (compared to the unconstrained profit) distribution:

```{r }
sim_results$g_welfare_loss[[prod_year]]
```

Now, you see the difference. Energy use limits are more damaging.

## Dry year

```{r}
prod_year <- 19
```

Profit loss (compared to the unconstrained profit) distribution:

```{r }
sim_results$g_welfare_loss[[prod_year]]
```

As we expected, under the energy use limit scheme, some benefited significantly, but others suffered quite a bit more compared to the water use limit scheme. The average economic loss under the energy and water use limits scheme are `r round(opt_ir_uc[,mean(pi_loss_elim)],digits=2)` and `r round(opt_ir_uc[,mean(pi_loss_wlim)],digits=2)`, respectively.

```{r }
sim_data <- sim_results$sim_data[[prod_year]]
sim_data %>%
  .[, .(ir_elim, ir_wlim)] %>%
  .[, id := 1:.N] %>%
  melt(id.vars = "id") %>%
  .[, type := ifelse(variable == "ir_wlim", "Water Use Limits", "Energy Use Limits")] %>%
  ggplot(data = .) +
  geom_histogram(aes(value)) +
  facet_wrap(type ~ .) +
  xlab("Water Use (inches)")
```

The average water use under the energy and water use limits scheme are `r round(sim_data[,mean(ir_elim)],digits=2)` and `r round(sim_data[,mean(ir_wlim)],digits=2)`, respectively. As you can see, the average water use is higher under the energy limit scheme than the water limit scheme. This is because producers are more energy use efficient in dry years. Remember that the average energy use efficiency was calculated using all the years of data. Consequently, there are more winners than losers in 2012, which makes the energy use limit loser than the water use limit, which helped farmer in profitability, but increased water use.

## Dry year II (50-50)

Now, I will use energy use efficiency so that the average water use under the energy limit scheme is the same as 13 inches (try and error).

```{r dry_II_calck}
#--- prod fcn ---#
temp_prod <- prod_store[[paste(19)]]

#--- unconstrained optimal water use ---#
w_len <- 1000
opt_ir_uc <- data[year == 2012, ] %>%
  .[, e_lim_2012 := w_lim * 47.5] %>%
  .[, w_max := e_lim_2012 / e_ef] %>%
  .[, .(wellid, e_ef, w_max)] %>%
  .[rep(1:nrow(.), each = w_len), ] %>%
  .[, ir := seq(min(temp_prod$model$ir), max(temp_prod$model$ir), length = w_len)] %>%
  .[, e_use := ir * e_ef] %>%
  .[, y_hat := predict(temp_prod, newdata = .)] %>%
  .[, pi_hat := p_corn * y_hat - p_e * e_use] %>%
  .[, .SD[which.max(pi_hat), ], by = wellid] %>%
  #--- unconstrained optimal water use ---#
  .[, ir_u := ir] %>%
  #--------------------------
  # Energy use limit
  #--------------------------
  #--- constrained water use ---#
  .[, ir := pmin(ir_u, w_max)] %>%
  .[, y_hat_elim := predict(temp_prod, newdata = .)] %>%
  setnames("ir", "ir_elim") %>%
  #--- constrained profit ---#
  .[, e_use_elim := ir_elim * e_ef] %>%
  .[, pi_hat_elim := p_corn * y_hat_elim - p_e * e_use_elim] %>%
  .[, pi_loss_elim := pi_hat - pi_hat_elim] %>%
  #--------------------------
  # Water use limit
  #--------------------------
  #--- constrained water use ---#
  .[, ir := pmin(ir_u, w_lim)] %>%
  .[, y_hat_wlim := predict(temp_prod, newdata = .)] %>%
  setnames("ir", "ir_wlim") %>%
  #--- constrained profit ---#
  .[, e_use_wlim := ir_wlim * e_ef] %>%
  .[, pi_hat_wlim := p_corn * y_hat_wlim - p_e * e_use_wlim] %>%
  .[, pi_loss_wlim := pi_hat - pi_hat_wlim]
```

Here is the distribution of unconstrained optimal water use:

```{r dry_II_ir_u}
ggplot(data = opt_ir_uc) +
  geom_histogram(aes(x = ir_u), fill = "blue", color = "black", alpha = 0.5) +
  xlab("Optimal Water Use (unconstrained)") +
  ylab("")
```

Profit loss (compared to the unconstrained profit) distribution:

```{r dry_II_pi_loss}
opt_ir_uc %>%
  .[, .(pi_loss_elim, pi_loss_wlim)] %>%
  melt() %>%
  .[, type := ifelse(variable == "pi_loss_wlim", "Water Use Limits", "Energy Use Limits")] %>%
  ggplot(data = .) +
  geom_histogram(aes(value)) +
  facet_wrap(type ~ .) +
  xlab("Economic Loss Relative to the Unconstrained Case ($/acre)")
```

The average economic loss under the energy and water use limits scheme are `r round(opt_ir_uc[,mean(pi_loss_elim)],digits=2)` and `r round(opt_ir_uc[,mean(pi_loss_wlim)],digits=2)`, respectively. Note that the dry-year production function I used is very much linear around 13 inches. So, the energy use limit is not hurting much. But, the more concave the production function, the greater the economic loss of the use of energy use limit schemes.

```{r dry_II_ir_we}
opt_ir_uc %>%
  .[, .(ir_elim, ir_wlim)] %>%
  melt() %>%
  .[, type := ifelse(variable == "ir_wlim", "Water Use Limits", "Energy Use Limits")] %>%
  ggplot(data = .) +
  geom_histogram(aes(value)) +
  facet_wrap(type ~ .) +
  xlab("Water Use (inches)")
```

The average water use under the energy and water use limits scheme are `r round(opt_ir_uc[,mean(ir_elim)],digits=2)` and `r round(opt_ir_uc[,mean(ir_wlim)],digits=2)`, respectively. As you can see, the average water use is almost the same.

### 2024-08-08 Writing/A1_proof_proxy_quota.qmd
Initial commit. Branching out from the original repository of Energy Regulation Welfare Loss.

# Proof 1:

Suppose measurement error is unbiased and independent. Further assume that the expected value of the sum of allocated proxy quota is the same as that of water quota, then expected value of total profit and water use are always higher under the uniform water quota.

+ variability in quota is not good in general due to asymmetric risk (going low hurts more than going high)

## Production function:

**Definitions:**

$$
y_i = f_i(w)
$$

+ $y$: crop yield
+ $f(\cdot)$: production function
+ $w$: water

**Conditions:**

$$
\frac{\partial f_i}{\partial w} \geq 0 \;\; ^{\forall} i = 1, \dots, N
$$

$$
\frac{\partial^2 f_i}{\partial w^2} \leq 0 \;\; ^{\forall} i = 1, \dots, N
$$

## Profit function

$$
\pi_i = P_c \cdot f_i(w) - P_w \cdot w
$$

$$
\frac{\partial \pi_i}{\partial w} \geq 0 \;\; ^{\forall} i = 1, \dots, N
$$

$$
\frac{\partial^2 \pi_i}{\partial w^2} \leq 0 \;\; ^{\forall} i = 1, \dots, N
$$

## Measurement error:

**Definitions**

$$
p_i = w_i + \mu_i 
$$

+ $p_i$: proxy 
+ $w_i$: water 
+ $\mu_i$: measurement error

**Conditions**

+ Proxy is unbiased.

$E[\mu_i] = 0$

+ Measurement error is uncorrelated with $w_i$.

$Cov(w_i, \mu_i) = 0$

+ Variance is finite.

$V(\mu_i) < \infty$

# Theorem 1

## Theorem

Suppose target average water use is $\alpha >0$. Under the uniform water quota, $\alpha$ is allocated to all the individual farmers. Under the proxy quota, proxy is allocated such that $\sum_{i=1}^N E[p_i] = \sum_{i=1}^N E[w_i] = \alpha$.  Then,

+ (1) average water use will be always less than equal to $\alpha$ for both quota systems on average
+ (2) average water use under proxy quota is lower than under water quota on average
+ (3) average profit under proxy quota is lower than under water quota on average

**Point 1**

Let $w^*_i$ denote the amount of water farmer $i$ would have used without any quota. Then, water use under water quota (denoted as $\bar{w}$) is simply $min(w^*_i, \bar{w})$. Since $min(w^*_i, \bar{w}) < \bar{w}$, average water use is always less than equal to water quota $\bar{w}$. This simply states that there are farmers who do not need as much as water quota allocated to them and do not end up using all the allocated quota.

**Point 2**

Let $ws_i$ denote water use slack defined as $\bar{w}_i - w^*_i$. Then, for a given value of optimal water use for farmer $i$ ($w^*_i$), the expected value of water slack is written as follows.

$$
E[ws_i] = \int_{-\infty}^\infty max[0, \bar{w}_i - w^*_i]g(\bar{w}_i)d\bar{w}_i
$$

Now, consider two distribution of $\bar{w}_i$, $g^A(w_i)$ and $g^B(w_i)$ where $g^B(w_i)$ is a mean preserving spread of $g^A(w_i)$. Since $max[0, \bar{w}_i - w^*_i]$ is a convex function with respect to $\bar{w}$, $E^A[ws_i] < E^B[ws_i]$. That is, water use slack is greater under $g^B(w_i)$, meaning lower water use under $g^B(w_i)$.

```{r}
#| eval: false
#| echo: false

#--- distribution of w^* ---#
data_wbar_dist <- 
  data.table(
    x = seq(-10, 30, length = 1000)
  ) %>%
  #--- density ---#
  .[, d_1 := dnorm(x, mean = 10, sd = 1)] %>%
  .[, d_2 := dnorm(x, mean = 10, sd = 2)]

ggplot(data_wbar_dist) +
  geom_line(aes(y = d_1, x = x)) +
  geom_line(aes(y = d_2, x = x)) +
  xlab("Water Quota")
```

```{r}
#| eval: false
#| echo: false

#--- list of allocation limit ---#
wstar_ls <- seq(0, 10, length = 1000)

slack_data <- 
  lapply(
   wstar_ls,
   \(wstar) {
    data_wbar_dist[wstar < x, .(es_1 = sum(d_1 * (x-wstar)) * 0.04, es_2 = sum(d_2 * (x-wstar)) * 0.04)] %>%
    .[, w_unconstrained := wstar]
   } 
  ) %>%
  rbindlist()

slack_data[es_1 > es_2, ]
```

**Point 3**

$$
E[\pi_i] = \int_{-\infty}^\infty \pi(\bar{w_i})g(\bar{w}_i)d\bar{w}_i
$$

Since $\pi(\bar{w_i})$ is a concave function with respect to $\bar{w}$, $E^A[\pi_i] > E^B[\pi_i]$. That is, profit is greater under $g^A(w_i)$ than under $g^B(w_i)$.

# Theorem 2

## Theorem
Conditional on the same expected value of water use, uniform water quota results in a higher expected value of total profit compared to proxy quota with measurement errors.

## Proof

Consider two sets water use by individual farmers

$W^A = \{w^A_1, \dots, w^A_N\}$

$W^B = \{w^B_1, \dots, w^B_N\}$

Suppose the expected total water use are the same ($E[w^A_i] = E[w^B_i]$) and the variance of water use is smaller under A ($Var(w^A_i)$ > $Var(w^B_i)$) $^\forall i = 1, \dots, N$. Therefore, the distribution of $w^A_i$ second-order stochastically dominates $w^B_i$. Since $\frac{\partial \pi_i}{\partial w} \geq 0$ and $\frac{\partial^2 \pi_i}{\partial w^2} \leq 0$,

$$
E[\pi^A_i] = \int \pi(w^A_i)dF(w^A_i) > \int \pi(w^B_i)dG(w^B_i) = E[\pi^B_i]\;\; ^{\forall} i = 1, \dots, N
$$

Since measurement errors are independent across farmers,
$$
E[\sum_{i=1}^N \pi_i] = \sum_{i=1}^N E[\pi_i]
$$

Therefore,

$$
E[\sum_{i=1}^N \pi^A_i] = \sum_{i=1}^N E[\pi^A_i] >  \sum_{i=1}^N E[\pi^B_i] = E[\sum_{i=1}^N \pi^B_i] 
$$

When proxy quota is designed so that total water use is the same as uniform water quota, $E[w^A_i] = E[w^B_i]$ and thus $E[\sum_{i=1}^N w^A_i] = E[\sum_{i=1}^N w^B_i]$. Moreover, $Var(w^A_i)$ > $Var(w^B_i)$ is satisfied. Therefore, uniform water quota always results in a higher total profit than proxy quota with measurement errors.

# Theorem 3

## Theorem

Proxy quota trading always results in lower profit than water quota trading.

## Proof

Conditional on a total water quota allocated to the farmers, the first order conditions of maximizing total profit state that marginal profit of water is equated across farmers:

$$
\frac{\partial \pi_i}{\partial w_i} = \dots = \frac{\partial \pi_N}{\partial w_N}
$$

Under a water permit trading, this condition is satisfied at the equilibrium through water permit trading.

When proxy quota is traded instead of water, then at the permit market equilibrium, marginal profit of quota is equated across farmers.

$$
\frac{\partial \pi_i}{\partial p_i} = \dots = \frac{\partial \pi_N}{\partial p_N}
$$

Since $\frac{\partial \pi_i}{\partial p_i} \ne \frac{\partial \pi_i}{\partial w_i}$ in general, proxy quota trading leads to a lower profit than water quota trading for a given level of target water use.

### 2024-08-08 Writing/manuscript.Rmd
Initial commit. Branching out from the original repository of Energy Regulation Welfare Loss.

---
title: Implications of Measurement Errors in Water Use Estimates for Water Management
author:
  - Taro Mieno^[Department of Agricultural Economics, University of Nebraska Lincoln, tmieno2@unl.edu]
  - Timothy Foster^[Department of WWW, University of Manchester, timothy.foster@manchester.ac.uk]
  - Nicholas Brozovic^[Department of Agricultural Economics, University of Nebraska Lincoln, nbrozovic@nebraska.edu]
abstract: |
  abstract here
acknowledgments: |
  Funding for the research in this manuscript was provided by 
bibliography: DRA.bib
output:
  bookdown::pdf_document2:
    extra_dependencies: ["float"]
    citation_package: natbib
    keep_tex: true
    toc: false
    includes:
      in_header: "preamble.tex"
---

```{r packages}
#| include: false
#| cache: false

#--- packages ---#
library(data.table)
library(tidyverse)
library(stringr)
library(sf)
library(here)
library(tmap)
library(modelsummary)
library(patchwork)
library(kableExtra)

source("../Codes/functions/functions.R")
```

```{r setup-main}
#| include: false
#| cache: false

library(knitr)

opts_chunk$set(
  fig.align = "center",
  fig.retina = 5,
  fig.width = 6,
  fig.height = 4.5,
  fig.pos = "H",
  out.extra = "",
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  cache = FALSE
)

options(knitr.duplicate.label = "allow")
```

```{r read_results}
#--- prices ---#
corn_price <- 6 # (bu/acre)
e_price <- 0.15 # ($/kwh)
w_price <- e_price * 500 / 12 # ($/inch)
other_cost <- 800 # ($/acre)
```

# Main

## Background

+ intensity estimation accuracy
+ (estimated) intensity-based vs (estimated) area-based (Southern Europe History)
+ (estimated) intensity-based vs (true) intensity-based [We work on this]

key objective:

  + start a discussion about the implications of the use of mis-measured water use for water use regulation.

  + shed lights on unintentional consequences of using estiamtes rather than actual measurements

Two policies: 
  + water quota (examples of existing quota systems)
  + water permit trading

Lack of measurement. Emergence of Open ET as a substitute.

No clear policy design suggestions on how to use water use estiamtes with measurement errors.

# Results

## Profit under water and proxy quota

```{r}
sum_res <-
  rbind(
    readRDS(here::here("Results/proxy_results_summary.rds")),
    readRDS(here::here("Results/water_results_summary.rds"))
  ) %>%
  .[, dir_cor_txt := paste0("Correlation: ", dir_cor)] %>%
  .[, dir_cor_txt := factor(dir_cor_txt, levels = paste0("Correlation: ", c("-", "0", "+")))] %>%
  .[, prod_het := str_to_title(prod_het)] %>%
  .[, prod_het := factor(prod_het, c("Zero", "Medium", "High"))]
```

Figure \@ref(fig:profit-quota-water-het) below compares profit from agricultural production as a function of actual water use between water and proxy quota across three different production heterogeneity levels. When there is no heterogeneity in farmers' production function, water quota is the most cost effective way to achieve a water use reduction goal (highest profit achievable for a given level of actual water use). Under this circumstance, proxy quota with unbiased measurement errors achieves worse than water quota due to asymmetry in downside and upside risk of water use.

```{r profit-quota-water-het, fig.cap = "Comparison of profit from agricultural production between the water and quota systems"}
(
  g_profit_quota_w_vs_p <-
    sum_res %>%
    .[instrument_type == "Quota", ] %>%
    .[(dir_cor == "0" & u_dev == 0.3 & measure_type == "Proxy") | measure_type == "Water", ] %>%
    ggplot(data = .) +
    geom_line(aes(y = profit, x = w, color = measure_type)) +
    facet_grid(. ~ prod_het) +
    ylab("Target Water Use (inches)") +
    xlab("Realized Water Use (inches)") +
    scale_color_discrete(name = "Measurement Type") +
    theme_bw() +
    theme(
      legend.position = "bottom"
    )
)
```

```{r}
#| echo: false

system_data <- readRDS(here::here("Results/quota_results_comp_stat.rds"))

farm_data <-
  data.table(system_data)[prod_het == "medium", farmer_data][[1]] %>%
  #--- use farmer 1 ---#
  .[farmer == 1, ] %>%
  .[, farmer := NULL] %>%
  expand_grid_df(., data.table(w = seq(0, 15, by = 0.1))) %>%
  .[, yield := ymax * (1 - alpha * exp(-beta * w))] %>%
  .[, w_cost := w_price * w] %>%
  .[, profit := corn_price * yield - w_cost - other_cost] %>%
  .[, marginal_cost_w := w_price] %>%
  .[, marginal_prod_w := ymax * alpha * beta * exp(-beta * w)] %>%
  .[, marginal_profit_w := marginal_prod_w * corn_price - marginal_cost_w]

opt_w <- unique(farm_data$opt_w)

quota_data <-
  data.table(
    farmer = c(1, 2, 1, 2),
    measure_type = c("Water", "Water", "Proxy", "Proxy"),
    quota = c(7, 7, 4, 10)
  ) %>%
  .[, w := quota] %>%
  .[quota > opt_w, w := opt_w] %>%
  farm_data[., on = .(w), roll = "nearest"]

pi_dif_2 <- quota_data[farmer == 2 & measure_type == "Proxy", profit] - quota_data[farmer == 2 & measure_type == "Water", profit]
pi_dif_1 <- quota_data[farmer == 1 & measure_type == "Proxy", profit] - quota_data[farmer == 1 & measure_type == "Water", profit]
```

Figure \@ref(fig:illust-homegeneous) presents an illustration to build the intuition behind the profit loss due to the use of proxy quota in place of water quota. The red dotted lines indicate the effective water use quota. Under the water quota system, both farmers receive 7 inches of water quota. Since the unconstrained profit maximizing water use is `r round(opt_w, digits = 2)` inches, both farmers use up all the allocated quota and use 10 inches of water. Under the proxy quota system, they are allocated the same amount of proxy quota. However, measurement error in proxy quota resulted in effective water quota of 4 and 10 inches for farmer A and B, respectively. Both farmers use their allocated amout of water. Under both proxy and water quota systems, the total water use is 14 inches. Farmer B makes `r pi_dif_2` less under the water quota system compared to the proxy quota system. However, Farmer A makes `r -pi_dif_1` more under the water quota system compared to the proxy quota system. This comes from an important nature of crop production with respsect to water: declining marginal impact of water on crop yield. As can be seen in the profit-water relationship, removing an inch of water from 6 inches has much larger negative impact compared to revmoing an inch of water from 10 inches.

```{r illust-homegeneous, fig.cap = "Illustration of profit loss due to the use of proxy for quota-based regulation: a case of homegeneous producers"}
#| warning: false
knitr::include_graphics("figures/g_illustration_homogeneous.pdf")
```

However, as the heterogeneity of farmers increases, comparative advantage of water quota over proxy quota diminishes. While the performance of both systems declines as the level of heterogeneity increases, water quota is affected more so than the proxy quota system. This is because uniform quota now acts like heterogeneous quota under homogeneous production function because the same quota is given to farmers with heterogeneous water demand. This is illustrated in Figure \@ref(fig:illust-heterogeneous). In this example,  farmer A needs less water than farmer B. Water and proxy quota allocated to the farmers are exactly the same as the previous case. In this example, errors in proxy happened to realize so that more effective water quota is given to farmer B than farmer A. Consequently, proxy quota produces a higher total profit than water quota. Of course, if error happened to go the opposite way, then the performance of proxy quota relative to water quota is even worse compared to the homogeneous case. This is a big contrast to the homogeneous case because water quota is always better than proxy quota in that case. Consequently, proxy quota performs relatively better under heterogeneous cases. On average, the positive and negative effects of measurement errors tend to even out. However, proxy quota is never better than water quota **on average** (see Appendix ... for mathematical proof).

```{r illust-heterogeneous, fig.cap = "Illustration of profit loss due to the use of proxy for quota-based regulation: a case of heterogeneous producers"}
#| warning: false

knitr::include_graphics("figures/g_illustration_het.pdf")
```

When measurement error is independent and production function is concave, water quota always outperforms proxy quota (show proof in appendix).

## The effect of increasing the size of measurement error

\textbf{Convert $u\_dev$ to $R^2$.}

```{r increase-me-degree, fig.cap = "The impacts of an increase in the degree of measurement error on profit"}
q_udev <- sum_res[(dir_cor == "0" & measure_type == "Proxy"), ]
w_udev <-
  sum_res[measure_type == "Water", ] %>%
  .[, u_dev := NULL] %>%
  expand_grid_df(., data.table(u_dev = c(0.1, 0.3, 0.5)))

quota_plot_data_comp_stat <-
  rbind(q_udev, w_udev) %>%
  .[instrument_type == "Quota", ]

(
  g_profit_quota_comp_stat <-
    ggplot(data = quota_plot_data_comp_stat) +
    geom_line(aes(y = profit, x = w, color = measure_type)) +
    facet_grid(u_dev ~ prod_het) +
    ylab("Profit ($/acre)") +
    xlab("Realized Water Use (inches)") +
    scale_color_discrete(name = "Measurement Type") +
    theme_bw() +
    theme(legend.position = "bottom")
)
```

## The effect of allowing trading quota

Allowing quota to be traded among farmers can dramatically change the relative performance of the water- and quota-based regulation. Figure \@ref(fig:trading-profit) presents profit for water-based quota, proxy-based quota, water-based quota trading, and proxy-based quota trading regulation systems. As shown in the figure, the disadvantage of using proxy almost disappears when trading of quota is allowed. This is because the inefficiencies in quota allocations are resolved through trading of quota whether it is water or proxy quota. (before trading and after trading?)

```{r trading-profit, fig.cap = "Comparison of profit from agricultural production between the water and quota systems when quota trading is allowed"}
#| echo: false
knitr::include_graphics("figures/g_trade_effect_profit.pdf")
```

Figure \@ref(fig:trading-profit-illustration) illustrates

```{r trading-profit-illustration, fig.cap = "Illustration of the benefits of trading quota"}

```

While water-quota and proxy-quota trading perform about the same, water-quota always leads to a higher total profit for a given level of realized water use. In other words, to achieve a certain water use goal, water-quota trading is always to more cost-effective than proxy-quota trading. Under water-quota trading, the margial profit of water is equalized across the farmers, which is a necessary condition to achieve the highest profit for a given level of total water use. Under proxy-quota trading, the marginal profit of proxy is equalized across the farmers, not the margial profit of water (See Appendix ... for a mathematical proof). However, it is worth emphasizing that the inefficiency caused by the use of proxy is likely to be minimal as shown in Figure \@ref(fig:trading-profit).

## Use of proxy can damage distributional equity

Figure below presents the ratio of profit under quota-based relative to water-based system for quota (red) and permit trading (blue). Ratio of less than 1 indicates making less profit under the quota-based system compared to the water-based system.

```{r distributional-equity, fig.cap = "Distribution of profit under various regulation systems"}
knitr::include_graphics("figures/g_profit_ratio.pdf")
```

# Discussion

# Methods

##

Assumptions: 
  + farmers: has learned the degree of under- or over-estimation of water use compared to actual over the years and has learned how to irrigate up to the water use quota

## Data and Code Availability

The datasets created in this article are all computer-generated using R codes. All the datasets and codes are available at .

\clearpage

# (APPENDIX) Appendix {-}

## Distribution of optimal water use under no water use constraints

```{r, fig.height = 5}
system_data %>%
  dplyr::select(prod_het, farmer_data) %>%
  unnest(cols = c(farmer_data)) %>%
  data.table() %>%
  .[, type_txt := case_when(
    prod_het == "zero" ~ "Heterogeneity: Zero",
    prod_het == "medium" ~ "Heterogeneity: Medium",
    prod_het == "high" ~ "Heterogeneity: High"
  )] %>%
  .[, type_txt := factor(
    type_txt,
    levels = c("Heterogeneity: Zero", "Heterogeneity: Medium", "Heterogeneity: High")
  )] %>%
  .[opt_w_true < 30, ] %>%
  ggplot(data = .) +
  geom_histogram(
    aes(
      x = opt_w_true,
      y = ifelse(after_stat(count) > 0, after_stat(count), NA)
    ),
    color = "blue",
    fill = NA
  ) +
  facet_grid(type_txt ~ .) +
  xlab("Optimal Water Use (inches)") +
  ylab("Count") +
  scale_x_continuous(breaks = seq(0, 30, by = 2)) +
  theme_bw()
```

### 2024-08-08 Writing/manuscript.tex
Initial commit. Branching out from the original repository of Energy Regulation Welfare Loss.

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\usepackage{lineno}
% \linenumbers
\usepackage{float}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{plainnat}
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Implications of Measurement Errors in Water Use Estimates for Water Management},
  pdfauthor={Taro Mieno; Timothy Foster; Nicholas Brozovic; Richael Young},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Implications of Measurement Errors in Water Use Estimates for Water Management}
\author{Taro Mieno\footnote{Department of Agricultural Economics, University of Nebraska Lincoln, \href{mailto:tmieno2@unl.edu}{\nolinkurl{tmieno2@unl.edu}}} \and Timothy Foster\footnote{Department of WWW, University of Manchester, \href{mailto:timothy.foster@manchester.ac.uk}{\nolinkurl{timothy.foster@manchester.ac.uk}}} \and Nicholas Brozovic\footnote{Department of Agricultural Economics, University of Nebraska Lincoln, \href{mailto:nbrozovic@nebraska.edu}{\nolinkurl{nbrozovic@nebraska.edu}}} \and Richael Young}
\date{}

\begin{document}
\maketitle
\begin{abstract}
abstract here
\end{abstract}

\section{Main}\label{main}

\subsection{Background}\label{background}

\begin{itemize}
\tightlist
\item
  intensity estimation accuracy
\item
  (estimated) intensity-based vs (estimated) area-based (Southern Europe History)
\item
  (estimated) intensity-based vs (true) intensity-based {[}We work on this{]}
\end{itemize}

key objective:

\begin{itemize}
\item
  start a discussion about the implications of the use of mis-measured water use for water use regulation.
\item
  shed lights on unintentional consequences of using estiamtes rather than actual measurements
\end{itemize}

Two policies:
+ water quota (examples of existing quota systems)
+ water permit trading

Lack of measurement. Emergence of Open ET as a substitute.

No clear policy design suggestions on how to use water use estiamtes with measurement errors.

\section{Results}\label{results}

\subsection{Profit under water and proxy quota}\label{profit-under-water-and-proxy-quota}

Figure \ref{fig:profit-quota-water-het} below compares profit from agricultural production as a function of actual water use between water and proxy quota across three different production heterogeneity levels. When there is no heterogeneity in farmers' production function, water quota is the most cost effective way to achieve a water use reduction goal (highest profit achievable for a given level of actual water use). Under this circumstance, proxy quota with unbiased measurement errors achieves worse than water quota due to asymmetry in downside and upside risk of water use.

\begin{figure}[H]

{\centering \includegraphics[width=432px,]{manuscript_files/figure-latex/profit-quota-water-het-1}

}

\caption{Comparison of profit from agricultural production between the water and quota systems}\label{fig:profit-quota-water-het}
\end{figure}

Figure \ref{fig:illust-homegeneous} presents an illustration to build the intuition behind the profit loss due to the use of proxy quota in place of water quota. The red dotted lines indicate the effective water use quota. Under the water quota system, both farmers receive 7 inches of water quota. Since the unconstrained profit maximizing water use is 10.94 inches, both farmers use up all the allocated quota and use 10 inches of water. Under the proxy quota system, they are allocated the same amount of proxy quota. However, measurement error in proxy quota resulted in effective water quota of 4 and 10 inches for farmer A and B, respectively. Both farmers use their allocated amout of water. Under both proxy and water quota systems, the total water use is 14 inches. Farmer B makes 29.8913345 less under the water quota system compared to the proxy quota system. However, Farmer A makes 128.8452417 more under the water quota system compared to the proxy quota system. This comes from an important nature of crop production with respsect to water: declining marginal impact of water on crop yield. As can be seen in the profit-water relationship, removing an inch of water from 6 inches has much larger negative impact compared to revmoing an inch of water from 10 inches.

\begin{figure}[H]

{\centering \includegraphics{figures/g_illustration_homogeneous}

}

\caption{Illustration of profit loss due to the use of proxy for quota-based regulation: a case of homegeneous producers}\label{fig:illust-homegeneous}
\end{figure}

However, as the heterogeneity of farmers increases, comparative advantage of water quota over proxy quota diminishes. While the performance of both systems declines as the level of heterogeneity increases, water quota is affected more so than the proxy quota system. This is because uniform quota now acts like heterogeneous quota under homogeneous production function because the same quota is given to farmers with heterogeneous water demand. This is illustrated in Figure \ref{fig:illust-heterogeneous}. In this example, farmer A needs less water than farmer B. Water and proxy quota allocated to the farmers are exactly the same as the previous case. In this example, errors in proxy happened to realize so that more effective water quota is given to farmer B than farmer A. Consequently, proxy quota produces a higher total profit than water quota. Of course, if error happened to go the opposite way, then the performance of proxy quota relative to water quota is even worse compared to the homogeneous case. This is a big contrast to the homogeneous case because water quota is always better than proxy quota in that case. Consequently, proxy quota performs relatively better under heterogeneous cases. On average, the positive and negative effects of measurement errors tend to even out. However, proxy quota is never better than water quota \textbf{on average} (see Appendix \ldots{} for mathematical proof).

\begin{figure}[H]

{\centering \includegraphics{figures/g_illustration_het}

}

\caption{Illustration of profit loss due to the use of proxy for quota-based regulation: a case of heterogeneous producers}\label{fig:illust-heterogeneous}
\end{figure}

When measurement error is independent and production function is concave, water quota always outperforms proxy quota (show proof in appendix).

\subsection{The effect of increasing the size of measurement error}\label{the-effect-of-increasing-the-size-of-measurement-error}

\textbf{Convert $u\_dev$ to $R^2$.}

\begin{figure}[H]

{\centering \includegraphics[width=432px,]{manuscript_files/figure-latex/increase-me-degree-1}

}

\caption{The impacts of an increase in the degree of measurement error on profit}\label{fig:increase-me-degree}
\end{figure}

\subsection{The effect of allowing trading quota}\label{the-effect-of-allowing-trading-quota}

Allowing quota to be traded among farmers can dramatically change the relative performance of the water- and quota-based regulation.

\begin{itemize}
\tightlist
\item
  Using proxy under the quota system instead of water can hurt welfare severely
\item
  The disadvantage of using proxy almost disappears when trading of quota is allowed
\item
  Proxy trading will never be as profitable as water trading (provide mathematical proof), but the economic loss seems to be very small
\end{itemize}

\begin{figure}[H]

{\centering \includegraphics{figures/g_trade_effect_profit}

}

\caption{Comparison of profit from agricultural production between the water and quota systems when quota trading is allowed}\label{fig:trading-profit}
\end{figure}

\subsection{Unfairness}\label{unfairness}

Figure below presents the ratio of profit under quota-based relative to water-based system for quota (red) and permit trading (blue). Ratio of less than 1 indicates making less profit under the quota-based system compared to the water-based system.

\begin{center}\includegraphics{figures/g_profit_ratio} \end{center}

\section{Discussion}\label{discussion}

\section{Methods}\label{methods}

\subsection{}\label{section}

Assumptions:
+ farmers: has learned the degree of under- or over-estimation of water use compared to actual over the years and has learned how to irrigate up to the water use quota

\subsection{Data and Code Availability}\label{data-and-code-availability}

The datasets created in this article are all computer-generated using R codes. All the datasets and codes are available at .

\clearpage

\appendix

\subsection{Distribution of optimal water use under no water use constraints}\label{distribution-of-optimal-water-use-under-no-water-use-constraints}

\begin{center}\includegraphics[width=432px,]{manuscript_files/figure-latex/unnamed-chunk-4-1} \end{center}

  \bibliography{DRA.bib}

\end{document}

### 2024-08-08 Writing/paper_structure.rmd
Initial commit. Branching out from the original repository of Energy Regulation Welfare Loss.

# Main

# Results

## ME in water use estiamtes based on energy

## Quota

Energy quota relative to water quota

+ uniform allocation for both energy and water

Things to look at:

+ Economic loss (gain) using 
+ Water use slack

Comparative statics wrt

+ the variance of the measurement error
+ heterogeneity of production function

## Trading

+ Trading reduces profit loss
+ Reduces uncertainty in water use

Measurement error is absorbed.

## Incentive to improve energy use efficiency

+ Energy use looks the same! Trouble for the administrator.
+ But, water use has gone up

## Fairness

# Method

## Data

## Simulation

+ Heterogeneous farmers

# Supplementary Appendix

## More general results (other cases)

### 2024-08-08 Codes/KB.R

@@ -1,0 +1,3 @@
+setwd('~/Box Sync/ResearchProjects/EnergyRegulationWelfareLoss')
+library(rmarkdown)
+render('./Codes/welfare_analysis.Rmd')

### 2024-08-08 Codes/functions/functions.R

@@ -1,0 +1,276 @@
+# !===========================================================
+# ! Quota analysis with heterogeneous random allocation
+# !===========================================================
+
+#++++++++++++++++++++++++++++++++++++
+#+ Generate farmer parameter data
+#++++++++++++++++++++++++++++++++++++
+# ! beta is backed out based on the other parameters
+gen_farmer_data <- function(par_set, num_farmers) {
+  farmer_data <-
+    data.table(
+      opt_w = par_set$opt_w,
+      farmer = 1:num_farmers,
+      #--- maximum yield ---#
+      ymax = runif(num_farmers, min = par_set$ymax_min, max = par_set$ymax_max),
+      alpha = runif(num_farmers, min = par_set$alpha_min, max = par_set$alpha_max)
+    ) %>%
+    #--- find beta that matches with the optimal water use ---#
+    expand_grid_df(., data.table(beta = seq(0, 1, by = 0.001))) %>%
+    .[, opt_w_true := -log(w_price / (corn_price * ymax * alpha * beta)) / beta] %>%
+    .[, .SD[which.min(abs(opt_w_true - opt_w)), ], by = farmer]
+
+  return(farmer_data)
+}
+
+#++++++++++++++++++++++++++++++++++++
+#+ Generate production data
+#++++++++++++++++++++++++++++++++++++
+# For each farmer, yield is generated for a sequence of values of water use. Based on these numbers, marginal profit wrt water and energy, optimal water and energy uses are also calculated.
+
+gen_prod_data <- function(farmer_data, w_resolution = 0.01) {
+
+  #! create water use sequence for each farmer (up to their unconstrained optimal water uses)
+  w_seq_data <-
+    rowwise(farmer_data) %>%
+    dplyr::mutate(w = list(
+      seq(0, max(opt_w) * 1.1, by = w_resolution)
+    )) %>%
+    dplyr::select(farmer, w) %>%
+    unnest(cols = c(w)) %>%
+    data.table()
+
+  #! calcualte yield, profit, and others at each level of water uses for each farmer. Marginal profit of water will be used for trading analysis.
+  prod_data <-
+    farmer_data[w_seq_data, on = "farmer"] %>%
+    .[, yield := ymax * (1 - alpha * exp(-beta * w))] %>%
+    .[, w_cost := w_price * w] %>%
+    .[, profit := corn_price * yield - w_cost - other_cost] %>%
+    .[, marginal_cost_w := w_price] %>%
[…]

### 2024-08-08 Codes/functions/retired/functions.R

@@ -1,0 +1,213 @@
+# !===========================================================
+# ! Quota analysis
+# !===========================================================
+
+#++++++++++++++++++++++++++++++++++++
+#+ Generate farmer data
+#++++++++++++++++++++++++++++++++++++
+# Create a dataset of farmers where their yield production function and energy efficiency are determined
+gen_farmer_data <- function(num_farmers, parameters) {
+  farmer_data <-
+    data.table(
+      farmer = 1:num_farmers,
+      #--- energy use efficiency ---#
+      # factor converting water use to energy use (kwh/acre-inch)
+      eta = runif(num_farmers, min = parameters$eta_min, max = parameters$eta_max), # kwh/inch
+      #--- maximum yield ---#
+      ymax = runif(num_farmers, min = parameters$ymax_min, max = parameters$ymax_max),
+      alpha = runif(num_farmers, min = parameters$alpha_min, max = parameters$alpha_max),
+      beta = runif(num_farmers, min = parameters$beta_min, max = parameters$beta_max)
+    ) %>%
+    #--- find the optimal w and e ---#
+    .[, opt_w := -log((w_price + e_price * eta / 12) / (corn_price * ymax * alpha * beta)) / beta] %>%
+    .[, opt_e := measurements::conv_unit(opt_w, "inch", "ft") * eta]
+
+  return(farmer_data)
+}
+
+#++++++++++++++++++++++++++++++++++++
+#+ Generate production data
+#++++++++++++++++++++++++++++++++++++
+# For each farmer, yield is generated for a sequence of values of water use. Based on these numbers, marginal profit wrt water and energy, optimal water and energy uses are also calculated.
+
+gen_prod_data <- function(farmer_data, w_resolution = 0.01) {
+  prod_data <-
+    expand_grid_df(
+      farmer_data,
+      data.table(w = seq(0, max(farmer_data$opt_w) * 1.2, by = w_resolution))
+    ) %>%
+    .[, yield := ymax * (1 - alpha * exp(-beta * w))] %>%
+    .[, e := measurements::conv_unit(w, "inch", "ft") * eta] %>%
+    .[, e_only_cost := e_price * e] %>%
[…]

### 2024-08-08 Codes/predict_from_energy.R

@@ -1,0 +1,53 @@
+######################################
+# Predict water use from energy use data
+######################################
+# written by Taro Mieno on 06/14/2017
+
+#===================================
+# Preparation 
+#===================================
+#--- import data ---#
+data <- readRDS('~/Box Sync/NebraskaWaterProjectsData/Data/Water_Energy/MW_energy_water.rds')
+
+#===================================
+# Naive water use prediction
+#===================================
+# data[,w_to_e] %>% hist()
+
+data <- data %>% 
+	.[,mean_w_to_e:=mean(w_to_e,na.rm=TRUE),by=nrdname] %>% 
+	.[,water_est:=kwh*mean_w_to_e/12]
+
+saveRDS('./Data/water_energy_MW.rds')
+fwrite(data,'./Data/water_energy_MW.csv')
+
+ggplot(data=data[nrdname!='Twin Platte',]) +
+	geom_point(aes(y=volaf,x=water_est),size=0.1) +
+	facet_grid(year~nrdname) +
+	geom_abline(intercept=0,slopw=1) +
+	xlab('Water Use Estimates Based on Energy Use (acre-feet)') +
+	ylab('Observed Water Use (acre-feet)') +
+	theme(
+		legend.position='bottom'
+		)
+ggsave('./Graphs/how_good_energy.pdf',height=10,width=6)
+
+ggplot(data=data[!is.na(w_to_e) & nrdname!='Twin Platte',]) +
+	geom_boxplot(aes(y=w_to_e,x=factor(year)),alpha=0.3) +
+	facet_grid(nrdname~.) +
+	ylab('Water (acre-feet)/Energy (kwh)') +
+	xlab('Year')
+
+ggsave('./Graphs/water_to_energy.pdf')
+
+ggplot(data=data[!is.na(w_to_e) & nrdname!='Twin Platte',]) +
+	geom_density(aes(x=w_to_e,fill=factor(year)),alpha=0.3) +
+	facet_grid(nrdname~.) +
+	ylab('Water (acre-feet)/Energy (kwh)') +
+	xlab('Year')
+
+ggsave('./Graphs/water_to_energy.pdf')
+
+
+
+

### 2024-08-12 Codes/1_analysis.qmd
manuscript writing started

@@
 ## Prices and costs
+
 ```{r}
@@
 other_cost <- 800 # ($/acre)
+
+save(corn_price, e_price, w_price, other_cost)
 ```
@@
 #| eval: false
+
+set.seed(812614)
+
 system_data <-
@@
 saveRDS(system_data, here::here("Results/quota_results_comp_stat.rds"))
+```
+
+```{r}
+g_opt_w_dist <-
+  system_data %>%
+  dplyr::select(prod_het, farmer_data) %>%
+  unnest(cols = c(farmer_data)) %>%
+  data.table() %>%
+  .[, type_txt := case_when(
+    prod_het == "zero" ~ "Heterogeneity: Zero",
+    prod_het == "medium" ~ "Heterogeneity: Medium",
+    prod_het == "high" ~ "Heterogeneity: High"
+  )] %>%
+  .[, type_txt := factor(
+    type_txt,
+    levels = c("Heterogeneity: Zero", "Heterogeneity: Medium", "Heterogeneity: High")
+  )] %>%
+  .[opt_w_true < 30, ] %>%
+  ggplot(data = .) +
+  geom_histogram(
+    aes(
+      x = opt_w_true,
+      y = ifelse(after_stat(count) > 0, after_stat(count), NA)
+    ),
+    color = "blue",
+    fill = NA
+  ) +
+  facet_grid(type_txt ~ .) +
+  xlab("Optimal Water Use (inches)") +
+  ylab("Count") +
+  scale_x_continuous(breaks = seq(0, 30, by = 2)) +
+  theme_bw()
+
+ggsave("Writing/figures/g_opt_w_dist.pdf", g_opt_w_dist, height = 5, width = 6)
 ```
@@
 
-# Results Presentation
+# Results
 
@@
 ```{r, eval = FALSE}
+#| eval: false
 #--- proxy ---#
@@
 
-farm_data <-
+w_A <- 7
+w_B <- 7
+p_A <- 4
+p_B <- 10
+
+farm_data_1 <-
   data.table(system_data)[prod_het == "medium", farmer_data][[1]] %>%
@@
 
-opt_w <- unique(farm_data$opt_w)
+opt_w <- unique(farm_data_1$opt_w)
 
@@
   data.table(
-    farmer = c(1, 2, 1, 2),
+    farmer = c("A", "B", "A", "B"),
     measure_type = c("Water", "Water", "Proxy", "Proxy"),
-    quota = c(7, 7, 4, 10)
+    quota = c(w_A, w_B, p_A, p_B)
   ) %>%
@@
   .[quota > opt_w, w := opt_w] %>%
-  farm_data[., on = .(w), roll = "nearest"]
+  farm_data_1[., on = .(w), roll = "nearest"]
 
-pi_dif_2 <- quota_data[farmer == 2 & measure_type == "Proxy", profit] - quota_data[farmer == 2 & measure_type == "Water", profit]
-pi_dif_1 <- quota_data[farmer == 1 & measure_type == "Proxy", profit] - quota_data[farmer == 1 & measure_type == "Water", profit]
+pi_dif_B <- quota_data[farmer == "B" & measure_type == "Proxy", profit] - quota_data[farmer == "B" & measure_type == "Water", profit]
+pi_dif_A <- quota_data[farmer == "A" & measure_type == "Proxy", profit] - quota_data[farmer == "A" & measure_type == "Water", profit]
 ```
@@
 Under both proxy and water quota systems, the total water use is 14 inches.
-Farmer B makes `r pi_dif_2` less under the water quota system compared to the proxy quota system.
-However, Farmer A makes `r -pi_dif_1` more under the water quota system compared to the proxy quota system.
+Farmer B makes `r pi_dif_B` less under the water quota system compared to the proxy quota system.
+However, Farmer A makes `r -pi_dif_A` more under the water quota system compared to the proxy quota system.
 This comes from an important nature of crop production with respsect to water: declining marginal impact of water on crop yield.
@@
     geom_line(
-      data = farm_data,
+      data = farm_data_1,
       aes(y = profit, x = w)
@@
 
+w_A <- 7
+w_B <- 7
+p_A <- 4
+p_B <- 10
+
 farm_data <-
@@
   .[, farmer_txt := "A"] %>%
-  .[opt_w == max(opt_w), farmer_txt := "B"]
+  .[opt_w == max(opt_w), farmer_txt := "B"] %>%
+  .[, marginal_profit_p := ifelse(farmer_txt == "A", marginal_profit_w / w_A * p_A, marginal_profit_w / w_B * p_B)]
 
@@
     measure_type = c("Water", "Water", "Proxy", "Proxy"),
-    quota = c(7, 7, 4, 10)
+    quota = c(w_A, w_B, p_A, p_B)
   ) %>%
@@
     ylab("Profit ($/acre)") +
-    xlab("Realized Water Use (inches)")
+    xlab("Realized Water Use (inches)") +
+    scale_color_discrete(name = "Measurement Type") +
+    theme_bw() +
+    theme(legend.position = "bottom")
 )
+
+ggsave("Writing/figures/g_profit_quota_comp_stat.pdf", g_profit_quota_comp_stat, height = 4.5, width = 6)
 ```
@@
 ```
+
+# Quota Trading
 
@@
 
-### Trading reduces welfare loss associated with the use of proxy
+## Trading reduces welfare loss associated with the use of proxy
 
@@
     scale_color_discrete(name = "Measurement Type") +
+    guides(color = guide_legend(nrow = 2, byrow = TRUE)) +
     theme_bw() +
@@
 
-ggsave("Writing/figures/g_trade_effect_profit.pdf", g_trade_effect_profit, height = 3.5, width = 6)
+ggsave("Writing/figures/g_trade_effect_profit.pdf", g_trade_effect_profit, height = 4.5, width = 6)
 ```
 
-### Trading reduces uncertainty in water use slack
+## Trading reduces uncertainty in water use slack
 
@@
 
-## Profit Distribution
+## Trading illustration
+
+Illustrate the effect of allowing proxy trading. Water trading does not happen as it is always optimal.
+
+```{r}
+farm_data_A <-
+  copy(farm_data_1) %>%
+  .[, farmer := "A"] %>%
+  .[, marginal_profit_p := marginal_profit_w / w_A * p_A]
+
+farm_data_B <-
+  copy(farm_data_1) %>%
+  .[, farmer := "B"] %>%
+  .[, marginal_profit_p := marginal_profit_w / w_B * p_B]
+
+mpp_w_A <- gam(w ~ s(marginal_profit_p), data = farm_data_A)
+mpp_w_B <- gam(w ~ s(marginal_profit_p), data = farm_data_B)
+
+w_data <-
+  data.table(
+    marginal_profit_p = seq(0, min(farm_data_A[, max(marginal_profit_p)], farm_data_B[, max(marginal_profit_p)]), length = 1001)
+  ) %>%
+  .[, w_A := predict(mpp_w_A, newdata = .)] %>%
+  .[, w_B := predict(mpp_w_B, newdata = .)] %>%
+  .[, tot_w := w_A + w_B] %>%
+  .[, dev := abs(tot_w - 14)] %>%
+  .[dev == min(dev), ]
+
+pi_w_A <- gam(profit ~ s(w), data = farm_data_A)
+pi_w_B <- gam(profit ~ s(w), data = farm_data_B)
+
+proxy_trade_data_A <-
+  data.table(w = w_data$w_A) %>%
+  .[, profit := predict(pi_w_A, newdata = .)] %>%
+  .[, farmer := "A"]
+
+proxy_trade_data_B <-
+  data.table(w = w_data$w_B) %>%
+  .[, profit := predict(pi_w_B, newdata = .)] %>%
+  .[, farmer := "B"]
+
+proxy_trade_data <-
+  rbind(proxy_trade_data_A, proxy_trade_data_B) %>%
+  .[, measure_type := "Proxy"]
+
+g_illustration_homogeneous +
+  geom_point(data = proxy_trade_data, aes(x = w, y = profit)) 
+```
+
+# Profit Distribution
 
@@
 
-#! Nearest matching based on water use (not target water use).
+# ! Nearest matching based on water use (not target water use).
 
@@
   .[dir_cor == "0" & ratio > 0 & ratio < 3, ] %>%
-  .[, dev_w := abs(w-8), by = .(prod_het, u_dev)] %>%
+  .[, dev_w := abs(w - 8), by = .(prod_het, u_dev)] %>%
   .[, .SD[dev_w == min(dev_w)], by = .(prod_het, u_dev)] %>%
@@
 
-ggsave("Writing/figures/g_profit_ratio.pdf", g_profit_ratio, height = 3.5, width = 6)
+ggsave("Writing/figures/g_profit_ratio.pdf", g_profit_ratio, height = 5, width = 6)
 ```

### 2024-08-12 Codes/2_make_figures.qmd
manuscript writing started

---
title: Create figures for the article
---

# Preparation

## Load datasets

```{r}
system_data <- readRDS(here::here("Results/quota_results_comp_stat.rds"))

sum_res <-
  rbind(
    readRDS(here::here("Results/proxy_results_summary.rds")),
    readRDS(here::here("Results/water_results_summary.rds"))
  ) %>%
  .[, dir_cor_txt := paste0("Correlation: ", dir_cor)] %>%
  .[, dir_cor_txt := factor(dir_cor_txt, levels = paste0("Correlation: ", c("-", "0", "+")))] %>%
  .[, prod_het := str_to_title(prod_het)] %>%
  .[, prod_het := factor(prod_het, c("Zero", "Medium", "High"))]
```

Load prices and costs:

```{r}
load(here::here("Results/prices_costs.RData"))
```

# Visualize: Summary of Production Data

## Distribution of unconstrained optimal water use by heterogeneity degree

```{r}
(
  g_opt_w_dist <-
    system_data %>%
    dplyr::select(prod_het, farmer_data) %>%
    unnest(cols = c(farmer_data)) %>%
    data.table() %>%
    .[, type_txt := case_when(
      prod_het == "zero" ~ "Heterogeneity: Zero",
      prod_het == "medium" ~ "Heterogeneity: Medium",
      prod_het == "high" ~ "Heterogeneity: High"
    )] %>%
    .[, type_txt := factor(
      type_txt,
      levels = c("Heterogeneity: Zero", "Heterogeneity: Medium", "Heterogeneity: High")
    )] %>%
    .[opt_w_true < 30, ] %>%
    ggplot(data = .) +
    geom_histogram(
      aes(
        x = opt_w_true,
        y = ifelse(after_stat(count) > 0, after_stat(count), NA)
      ),
      color = "blue",
      fill = NA
    ) +
    facet_grid(type_txt ~ .) +
    xlab("Optimal Water Use (inches)") +
    ylab("Count") +
    scale_x_continuous(breaks = seq(0, 30, by = 2)) +
    theme_bw()
)

ggsave(here::here("Writing/figures/g_opt_w_dist.pdf"), g_opt_w_dist, height = 5, width = 6)
```

# Visualize: Results

# Visualize: Illustration

Here, illustrative figures to gain insights into the underlying economic intuitions of the results are created.

## Homogeneous farmers under quota

Use the first farmer under the category of `prod_het == "medium"`. It is duplicated to be farmers A and B.

Under the water quota system, both farmers A and B will be given water quota of 7.

```{r}
#| echo: false

w_A <- 7 # water quota for farmer A
w_B <- 7 # water quota for farmer B
```

Under the proxy quota system, both farmers A and B will be given proxy quota of 7. However, the effective water quota for them are different and defined down below.

```{r}
eW_A <- 4 # effective water quota for farmer A
eW_B <- 10 # effective water for farmer B
```

Farmer A is unfairly treated with its water use over-estimated. Specifically, 1 proxy quota is equivalent to `eW_A/w_A` (`r eW_A/w_A`). On the other hand, farmer B is lucky with its water use under-estimated. Specifically, 1 proxy quota is equivalent to `eW_B/w_B` (`r eW_B/w_B`).

$$
P_A = \frac{7 \cdot W_A}{4}
P_B = \frac{7 \cdot W_B}{10}
$$

Create farmer production data.

```{r}
farm_data_1 <-
  data.table(system_data)[prod_het == "medium", farmer_data][[1]] %>%
  #--- use farmer 1 ---#
  .[farmer == 1, ] %>%
  .[, farmer := NULL] %>%
  expand_grid_df(., data.table(w = seq(0, 15, by = 0.1))) %>%
  .[, yield := ymax * (1 - alpha * exp(-beta * w))] %>%
  .[, w_cost := w_price * w] %>%
  .[, profit := corn_price * yield - w_cost - other_cost] %>%
  .[, marginal_cost_w := w_price] %>%
  .[, marginal_prod_w := ymax * alpha * beta * exp(-beta * w)] %>%
  .[, marginal_profit_w := marginal_prod_w * corn_price - marginal_cost_w]
```

Make production data at the quota level.

```{r}
opt_w <- unique(farm_data_1$opt_w)

production_at_quota <-
  data.table(
    farmer = c("A", "B", "A", "B"),
    measure_type = c("Water", "Water", "Proxy", "Proxy"),
    quota = c(w_A, w_B, eW_A, eW_B)
  ) %>%
  .[, w := quota] %>%
  .[quota > opt_w, w := opt_w] %>%
  farm_data_1[., on = .(w), roll = "nearest"]
```

Visualize the production data.

```{r}
#| warning: false
(
  g_illustration_homogeneous <-
    ggplot() +
    geom_line(
      data = farm_data_1,
      aes(y = profit, x = w)
    ) +
    geom_vline(
      data = production_at_quota,
      aes(xintercept = quota),
      linetype = 2,
      color = "red"
    ) +
    geom_point(
      data = production_at_quota,
      aes(y = profit, x = w),
      color = "blue",
      size = 2
    ) +
    facet_grid(measure_type ~ farmer) +
    ylim(0, NA) +
    xlab("Water Use (inches)") +
    ylab("Profit ($/acre)") +
    theme_bw()
)

ggsave("Writing/figures/g_illustration_homogeneous.pdf", g_illustration_homogeneous, height = 4, width = 6)
```

## Homogeneous farmers under quota trading

Illustrate the effect of allowing proxy trading. Water trading does not happen as it is always optimal.

Create production data for two homogeneous farmers. They differ in water/proxy ratio.

For farmer A,

$$
P_A = \frac{7 \cdot W_A}{4}
$$

$$
\frac{\partial \pi}{\partial p} =  \frac{\partial \pi}{\partial w} \cdot \frac{\partial w}{\partial p} = \frac{\partial \pi}{\partial w} \cdot \frac{4}{7}
$$

```{r}
farm_data_A <-
  copy(farm_data_1) %>%
  .[, farmer := "A"] %>%
  .[, marginal_profit_p := marginal_profit_w / w_A * p_A]

farm_data_B <-
  copy(farm_data_1) %>%
  .[, farmer := "B"] %>%
  .[, marginal_profit_p := marginal_profit_w / w_B * p_B]
```

Find the results of proxy quota trading, at which the marginal profit of proxy is equalized between the farmers.

```{r}
#--- link water use and marginal profit of proxy  ---#
mpp_w_A <- gam(w ~ s(marginal_profit_p), data = farm_data_A)
mpp_w_B <- gam(w ~ s(marginal_profit_p), data = farm_data_B)

#--- proxy quota trading results ---#
w_data <-
  data.table(
    marginal_profit_p = seq(0, min(farm_data_A[, max(marginal_profit_p)], farm_data_B[, max(marginal_profit_p)]), length = 1001)
  ) %>%
  .[, w_A := predict(mpp_w_A, newdata = .)] %>%
  .[, w_B := predict(mpp_w_B, newdata = .)] %>%
  .[, tot_w := w_A + w_B] %>%
  .[, dev := abs(tot_w - 14)] %>%
  .[dev == min(dev), ]
```

Associate profit to the water use levels observed under the proxy quota trading.

```{r}
pi_w_A <- gam(profit ~ s(w), data = farm_data_A)
pi_w_B <- gam(profit ~ s(w), data = farm_data_B)

proxy_trade_data_A <-
  data.table(w = w_data$w_A) %>%
  .[, profit := predict(pi_w_A, newdata = .)] %>%
  .[, farmer := "A"]

proxy_trade_data_B <-
  data.table(w = w_data$w_B) %>%
  .[, profit := predict(pi_w_B, newdata = .)] %>%
  .[, farmer := "B"]

proxy_trade_data <-
  rbind(proxy_trade_data_A, proxy_trade_data_B) %>%
  .[, measure_type := "Proxy"] %>%
  .[, instrument_type := "Trading"]
```

Visualize the trading results.

```{r}
(
  g_illustration_homogeneous <-
    ggplot() +
    geom_line(
      data = farm_data_1,
      aes(y = profit, x = w)
    ) +
    geom_vline(
      data = production_at_quota,
      aes(xintercept = quota),
      linetype = 2,
      color = "red"
    ) +
    geom_point(
      data = production_at_quota,
      aes(y = profit, x = w),
      color = "blue",
      size = 2
    ) +
    geom_point(
      data = proxy_trade_data, 
      aes(x = w, y = profit)
    ) +
    facet_grid(measure_type ~ farmer) +
    ylim(0, NA) +
    xlab("Water Use (inches)") +
    ylab("Profit ($/acre)") +
    theme_bw()

)
```

## Heterogeneous farmers under quota

```{r}
farm_data_het <-
  data.table(system_data)[prod_het == "medium", farmer_data][[1]] %>%
  #--- pick the farmers whose optimal water use is 7 and 13 ---#
  .[, dev_from_7 := abs(opt_w - 7)] %>%
  .[, dev_from_13 := abs(opt_w - 13)] %>%
  .[(dev_from_7 == min(dev_from_7) | dev_from_13 == min(dev_from_13)), ] %>%
  expand_grid_df(., data.table(w = seq(0, 15, by = 0.1))) %>%
  #--- production data ---#
  .[, yield := ymax * (1 - alpha * exp(-beta * w))] %>%
  .[, w_cost := w_price * w] %>%
  .[, profit := corn_price * yield - w_cost - other_cost] %>%
  .[, marginal_cost_w := w_price] %>%
  .[, marginal_prod_w := ymax * alpha * beta * exp(-beta * w)] %>%
  .[, marginal_profit_w := marginal_prod_w * corn_price - marginal_cost_w] %>%
  .[, farmer_txt := "A"] %>%
  .[opt_w == max(opt_w), farmer_txt := "B"]
```

Production data at the quota levels.

```{r}
opt_w <- farm_data_het[, .(opt_w = unique(opt_w)), by = farmer_txt]

quota_data_het <-
  data.table(
    farmer_txt = c("A", "B", "A", "B"),
    measure_type = c("Water", "Water", "Proxy", "Proxy"),
    quota = c(w_A, w_B, p_A, p_B)
  ) %>%
  opt_w[., on = .(farmer_txt)] %>%
  .[, w := quota] %>%
  .[quota > opt_w, w := opt_w] %>%
  setnames("farmer_txt", "farmer_id") %>%
  nest_by(farmer_id) %>%
  dplyr::mutate(merged = list(
    farm_data_het[farmer_txt == farmer_id, ][data.table(data), on = .(w), roll = "nearest"]
  )) %>%
  dplyr::select(farmer_id, merged) %>%
  unnest(cols = c(merged)) %>%
  data.table() %>%
  .[, .(farmer, farmer_txt, w, opt_w, profit, measure_type, quota)]
```

Visualize the production data.

```{r}
#| warning: false
(
  g_illustration_het <-
    ggplot() +
    geom_line(
      data = farm_data_het,
      aes(y = profit, x = w)
    ) +
    geom_vline(
      data = quota_data_het,
      aes(xintercept = quota),
      linetype = 2,
      color = "red"
    ) +
    geom_point(
      data = quota_data_het,
      aes(y = profit, x = w),
      color = "blue",
      size = 2
    ) +
    facet_grid(measure_type ~ farmer_txt) +
    ylim(0, NA) +
    xlab("Water Use (inches)") +
    ylab("Profit ($/acre)") +
    theme_bw()
)

ggsave("Writing/figures/g_illustration_het.pdf", g_illustration_het, height = 4, width = 6)
```

### 2024-08-12 Writing/manuscript.Rmd
manuscript writing started

@@
 ```{r profit-quota-water-het, fig.cap = "Comparison of profit from agricultural production between the water and quota systems"}
-(
-  g_profit_quota_w_vs_p <-
-    sum_res %>%
-    .[instrument_type == "Quota", ] %>%
-    .[(dir_cor == "0" & u_dev == 0.3 & measure_type == "Proxy") | measure_type == "Water", ] %>%
-    ggplot(data = .) +
-    geom_line(aes(y = profit, x = w, color = measure_type)) +
-    facet_grid(. ~ prod_het) +
-    ylab("Target Water Use (inches)") +
-    xlab("Realized Water Use (inches)") +
-    scale_color_discrete(name = "Measurement Type") +
-    theme_bw() +
-    theme(
-      legend.position = "bottom"
-    )
-)
+knitr::include_graphics("figures/g_profit_quota_w_vs_p.pdf")
 ```
@@
 ```{r increase-me-degree, fig.cap = "The impacts of an increase in the degree of measurement error on profit"}
-q_udev <- sum_res[(dir_cor == "0" & measure_type == "Proxy"), ]
-w_udev <-
-  sum_res[measure_type == "Water", ] %>%
-  .[, u_dev := NULL] %>%
-  expand_grid_df(., data.table(u_dev = c(0.1, 0.3, 0.5)))
 
-quota_plot_data_comp_stat <-
-  rbind(q_udev, w_udev) %>%
-  .[instrument_type == "Quota", ]
-
-(
-  g_profit_quota_comp_stat <-
-    ggplot(data = quota_plot_data_comp_stat) +
-    geom_line(aes(y = profit, x = w, color = measure_type)) +
-    facet_grid(u_dev ~ prod_het) +
-    ylab("Profit ($/acre)") +
-    xlab("Realized Water Use (inches)") +
-    scale_color_discrete(name = "Measurement Type") +
-    theme_bw() +
-    theme(legend.position = "bottom")
-)
+knitr::include_graphics("figures/g_profit_quota_comp_stat.pdf")
 ```
@@
 
-Figure below presents the ratio of profit under quota-based relative to water-based system for quota (red) and permit trading (blue).
+Figure \@ref(fig:distributional-equity) presents the cumulative probability of the ratio of profit under quota-based relative to water-based system for quota (red) and permit trading (blue).
 Ratio of less than 1 indicates making less profit under the quota-based system compared to the water-based system.
+If farmers make just as much profir under proxy-based regulation compared to water-based regulation, then the cumulative probability line would be a vertical line at 1.
+For example, under the high degree of measurement error and medium heterogenenity scenario, some farmers would make about the half of what they would make under the water quota system.
+At the lower end of the distribution are farmers who would be constrained severely by water use quota, but whose water use estiamtes are much higher than their actual water use.
+At the higher end of the distribution are farmers who would be constrained by water use quota, but whose water use estiamtes are much lower than their actual water use.
+Famres who suffer significantly under the quota system can develop strong dissatisfaction of the quota-based regulation system, which in turn may lead to installing water meter themselves.
+If they discover the over-estimation of their water use, they may appeal to legal actions against the administrator for their unfair treatment.
+Allowind quota trading greatly diminishes the distributional inequality, though not completely.
+This is because unfortunate farmers who suffered from over-estimation of their water use can now at least purchase proxy quota to increase their production level.
 
@@
 # Discussion
+
+## Limitations
+
+Assumptions.
+Temporal
 
@@
 
-```{r, fig.height = 5}
-system_data %>%
-  dplyr::select(prod_het, farmer_data) %>%
-  unnest(cols = c(farmer_data)) %>%
-  data.table() %>%
-  .[, type_txt := case_when(
-    prod_het == "zero" ~ "Heterogeneity: Zero",
-    prod_het == "medium" ~ "Heterogeneity: Medium",
-    prod_het == "high" ~ "Heterogeneity: High"
-  )] %>%
-  .[, type_txt := factor(
-    type_txt,
-    levels = c("Heterogeneity: Zero", "Heterogeneity: Medium", "Heterogeneity: High")
-  )] %>%
-  .[opt_w_true < 30, ] %>%
-  ggplot(data = .) +
-  geom_histogram(
-    aes(
-      x = opt_w_true,
-      y = ifelse(after_stat(count) > 0, after_stat(count), NA)
-    ),
-    color = "blue",
-    fill = NA
-  ) +
-  facet_grid(type_txt ~ .) +
-  xlab("Optimal Water Use (inches)") +
-  ylab("Count") +
-  scale_x_continuous(breaks = seq(0, 30, by = 2)) +
-  theme_bw()
+```{r dist-opt-w, fig.cap = "Distribution of optimal water use under no water use constraints", fig.height = 5}
+knitr::include_graphics("figures/g_opt_w_dist.pdf")
 ```

### 2024-08-12 Writing/manuscript.tex
manuscript writing started

@@
 \usepackage{amsmath,amssymb}
+\usepackage{lmodern}
 \usepackage{iftex}
@@
 \else % if luatex or xetex
-  \usepackage{unicode-math} % this also loads fontspec
+  \usepackage{unicode-math}
   \defaultfontfeatures{Scale=MatchLowercase}
   \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
-\fi
-\usepackage{lmodern}
-\ifPDFTeX\else
-  % xetex/luatex font selection
 \fi
@@
 \IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same}
+\urlstyle{same} % disable monospaced font for URLs
 \hypersetup{
   pdftitle={Implications of Measurement Errors in Water Use Estimates for Water Management},
-  pdfauthor={Taro Mieno; Timothy Foster; Nicholas Brozovic; Richael Young},
+  pdfauthor={Taro Mieno; Timothy Foster; Nicholas Brozovic},
   hidelinks,
@@
 \title{Implications of Measurement Errors in Water Use Estimates for Water Management}
-\author{Taro Mieno\footnote{Department of Agricultural Economics, University of Nebraska Lincoln, \href{mailto:tmieno2@unl.edu}{\nolinkurl{tmieno2@unl.edu}}} \and Timothy Foster\footnote{Department of WWW, University of Manchester, \href{mailto:timothy.foster@manchester.ac.uk}{\nolinkurl{timothy.foster@manchester.ac.uk}}} \and Nicholas Brozovic\footnote{Department of Agricultural Economics, University of Nebraska Lincoln, \href{mailto:nbrozovic@nebraska.edu}{\nolinkurl{nbrozovic@nebraska.edu}}} \and Richael Young}
+\author{Taro Mieno\footnote{Department of Agricultural Economics, University of Nebraska Lincoln, \href{mailto:tmieno2@unl.edu}{\nolinkurl{tmieno2@unl.edu}}} \and Timothy Foster\footnote{Department of WWW, University of Manchester, \href{mailto:timothy.foster@manchester.ac.uk}{\nolinkurl{timothy.foster@manchester.ac.uk}}} \and Nicholas Brozovic\footnote{Department of Agricultural Economics, University of Nebraska Lincoln, \href{mailto:nbrozovic@nebraska.edu}{\nolinkurl{nbrozovic@nebraska.edu}}}}
 \date{}
@@
 
-\section{Main}\label{main}
+\hypertarget{main}{%
+\section{Main}\label{main}}
 
-\subsection{Background}\label{background}
+\hypertarget{background}{%
+\subsection{Background}\label{background}}
 
@@
 
-\section{Results}\label{results}
+\hypertarget{results}{%
+\section{Results}\label{results}}
 
-\subsection{Profit under water and proxy quota}\label{profit-under-water-and-proxy-quota}
+\hypertarget{profit-under-water-and-proxy-quota}{%
+\subsection{Profit under water and proxy quota}\label{profit-under-water-and-proxy-quota}}
 
@@
 
-{\centering \includegraphics[width=432px,]{manuscript_files/figure-latex/profit-quota-water-het-1}
+{\centering \includegraphics{figures/g_profit_quota_w_vs_p}
 
@@
 Under both proxy and water quota systems, the total water use is 14 inches.
-Farmer B makes 29.8913345 less under the water quota system compared to the proxy quota system.
-However, Farmer A makes 128.8452417 more under the water quota system compared to the proxy quota system.
+Farmer B makes 30.6035744 less under the water quota system compared to the proxy quota system.
+However, Farmer A makes 133.2697115 more under the water quota system compared to the proxy quota system.
 This comes from an important nature of crop production with respsect to water: declining marginal impact of water on crop yield.
@@
 
-\subsection{The effect of increasing the size of measurement error}\label{the-effect-of-increasing-the-size-of-measurement-error}
+\hypertarget{the-effect-of-increasing-the-size-of-measurement-error}{%
+\subsection{The effect of increasing the size of measurement error}\label{the-effect-of-increasing-the-size-of-measurement-error}}
 
@@
 
-{\centering \includegraphics[width=432px,]{manuscript_files/figure-latex/increase-me-degree-1}
+{\centering \includegraphics{figures/g_profit_quota_comp_stat}
 
@@
 
-\subsection{The effect of allowing trading quota}\label{the-effect-of-allowing-trading-quota}
+\hypertarget{the-effect-of-allowing-trading-quota}{%
+\subsection{The effect of allowing trading quota}\label{the-effect-of-allowing-trading-quota}}
 
 Allowing quota to be traded among farmers can dramatically change the relative performance of the water- and quota-based regulation.
-
-\begin{itemize}
-\tightlist
-\item
-  Using proxy under the quota system instead of water can hurt welfare severely
-\item
-  The disadvantage of using proxy almost disappears when trading of quota is allowed
-\item
-  Proxy trading will never be as profitable as water trading (provide mathematical proof), but the economic loss seems to be very small
-\end{itemize}
+Figure \ref{fig:trading-profit} presents profit for water-based quota, proxy-based quota, water-based quota trading, and proxy-based quota trading regulation systems.
+As shown in the figure, the disadvantage of using proxy almost disappears when trading of quota is allowed.
+This is because the inefficiencies in quota allocations are resolved through trading of quota whether it is water or proxy quota.
+(before trading and after trading?)
 
@@
 
-\subsection{Unfairness}\label{unfairness}
+Figure \ref{fig:trading-profit-illustration} illustrates
 
-Figure below presents the ratio of profit under quota-based relative to water-based system for quota (red) and permit trading (blue).
+While water-quota and proxy-quota trading perform about the same, water-quota always leads to a higher total profit for a given level of realized water use.
+In other words, to achieve a certain water use goal, water-quota trading is always to more cost-effective than proxy-quota trading.
+Under water-quota trading, the margial profit of water is equalized across the farmers, which is a necessary condition to achieve the highest profit for a given level of total water use.
+Under proxy-quota trading, the marginal profit of proxy is equalized across the farmers, not the margial profit of water (See Appendix \ldots{} for a mathematical proof).
+However, it is worth emphasizing that the inefficiency caused by the use of proxy is likely to be minimal as shown in Figure \ref{fig:trading-profit}.
+
+\hypertarget{use-of-proxy-can-damage-distributional-equity}{%
+\subsection{Use of proxy can damage distributional equity}\label{use-of-proxy-can-damage-distributional-equity}}
+
+Figure \ref{fig:distributional-equity} presents the cumulative probability of the ratio of profit under quota-based relative to water-based system for quota (red) and permit trading (blue).
 Ratio of less than 1 indicates making less profit under the quota-based system compared to the water-based system.
+If farmers make just as much profir under proxy-based regulation compared to water-based regulation, then the cumulative probability line would be a vertical line at 1.
+For example, under the high degree of measurement error and medium heterogenenity scenario, some farmers would make about the half of what they would make under the water quota system.
+At the lower end of the distribution are farmers who would be constrained severely by water use quota, but whose water use estiamtes are much higher than their actual water use.
+At the higher end of the distribution are farmers who would be constrained by water use quota, but whose water use estiamtes are much lower than their actual water use.
+Famres who suffer significantly under the quota system can develop strong dissatisfaction of the quota-based regulation system, which in turn may lead to installing water meter themselves.
+If they discover the over-estimation of their water use, they may appeal to legal actions against the administrator for their unfair treatment.
+Allowind quota trading greatly diminishes the distributional inequality, though not completely.
+This is because unfortunate farmers who suffered from over-estimation of their water use can now at least purchase proxy quota to increase their production level.
 
-\begin{center}\includegraphics{figures/g_profit_ratio} \end{center}
+\begin{figure}[H]
 
-\section{Discussion}\label{discussion}
+{\centering \includegraphics{figures/g_profit_ratio}
 
-\section{Methods}\label{methods}
+}
 
-\subsection{}\label{section}
+\caption{Distribution of profit under various regulation systems}\label{fig:distributional-equity}
+\end{figure}
+
+\hypertarget{discussion}{%
+\section{Discussion}\label{discussion}}
+
+\hypertarget{limitations}{%
+\subsection{Limitations}\label{limitations}}
+
+Assumptions.
+Temporal
+
+\hypertarget{methods}{%
+\section{Methods}\label{methods}}
+
+\hypertarget{section}{%
+\subsection{}\label{section}}
 
@@
 
-\subsection{Data and Code Availability}\label{data-and-code-availability}
+\hypertarget{data-and-code-availability}{%
+\subsection{Data and Code Availability}\label{data-and-code-availability}}
 
@@
 
-\appendix
+\hypertarget{appendix-appendix}{%
+\appendix}
 
-\subsection{Distribution of optimal water use under no water use constraints}\label{distribution-of-optimal-water-use-under-no-water-use-constraints}
+\hypertarget{distribution-of-optimal-water-use-under-no-water-use-constraints}{%
+\subsection{Distribution of optimal water use under no water use constraints}\label{distribution-of-optimal-water-use-under-no-water-use-constraints}}
 
-\begin{center}\includegraphics[width=432px,]{manuscript_files/figure-latex/unnamed-chunk-4-1} \end{center}
+\begin{figure}[H]
+
+{\centering \includegraphics{figures/g_opt_w_dist}
+
+}
+
+\caption{Distribution of optimal water use under no water use constraints}\label{fig:dist-opt-w}
+\end{figure}
 

### 2024-08-14 Codes/2_make_figures.qmd
manuscript modified
1. method updated

@@
 
+## Profitability: Water vs Proxy Quota (with comparative statistics wrt heterogeneity of farmers)
+
+```{r}
+w_p_plot_data <-
+  sum_res %>%
+  .[instrument_type == "Quota", ] %>%
+  .[(dir_cor == "0" & u_dev == 0.3 & measure_type == "Proxy") | measure_type == "Water", ]
+
+y_lims <- w_p_plot_data[, c(floor(min(profit / 10)), ceiling(max(profit / 10)))] * 10
+
+(
+  g_profit_quota_w_vs_p <-
+    ggplot(data = w_p_plot_data) +
+    geom_line(aes(y = profit, x = w, color = measure_type)) +
+    facet_grid(. ~ prod_het) +
+    ylab("Target Water Use (inches)") +
+    xlab("Realized Water Use (inches)") +
+    scale_color_discrete(name = "Measurement Type") +
+    scale_y_continuous(
+      breaks = seq(y_lims[1], y_lims[2], by = 10)
+    ) +
+    theme_bw() +
+    theme(
+      legend.position = "bottom"
+    )
+)
+
+ggsave("Writing/figures/g_profit_quota_w_vs_p.pdf", g_profit_quota_w_vs_p, height = 3.5, width = 6)
+```
+
+## The effect of increasing the size of measurement error
+
+```{r}
+q_udev <- sum_res[(dir_cor == "0" & measure_type == "Proxy"), ]
+w_udev <-
+  sum_res[measure_type == "Water", ] %>%
+  .[, u_dev := NULL] %>%
+  expand_grid_df(., data.table(u_dev = c(0.1, 0.3, 0.5)))
+
+quota_plot_data_comp_stat <-
+  rbind(q_udev, w_udev) %>%
+  .[instrument_type == "Quota", ]
+
+y_lims <- quota_plot_data_comp_stat[, c(floor(min(profit / 10)), ceiling(max(profit / 10)))] * 10
+
+(
+  g_profit_quota_comp_stat <-
+    ggplot(data = quota_plot_data_comp_stat) +
+    geom_line(aes(y = profit, x = w, color = measure_type)) +
+    facet_grid(u_dev ~ prod_het) +
+    ylab("Profit ($/acre)") +
+    xlab("Realized Water Use (inches)") +
+    scale_color_discrete(name = "Measurement Type") +
+    scale_y_continuous(
+      breaks = seq(y_lims[1], y_lims[2], by = 10)
+    ) +
+    scale_x_continuous(breaks = 7:12) +
+    theme_bw() +
+    theme(
+      legend.position = "bottom",
+      panel.grid.minor = element_blank(),
+      panel.spacing.y = unit(1, "lines")
+    )
+)
+
+ggsave("Writing/figures/g_profit_quota_comp_stat.pdf", g_profit_quota_comp_stat, height = 6, width = 6)
+```
+
+## The effect of allowing trading quota
+
+```{r}
+#| echo: false
+q_temp <- sum_res[(dir_cor == "0" & u_dev != 0 & measure_type == "Proxy"), ]
+w_temp <-
+  sum_res[measure_type == "Water", ] %>%
+  .[, u_dev := NULL] %>%
+  expand_grid_df(., data.table(u_dev = c(0.1, 0.3, 0.5)))
+
+trading_plot_data <-
+  rbind(w_temp, q_temp) %>%
+  .[, type := paste0(measure_type, "-", instrument_type)]
+
+y_lims <- trading_plot_data[, c(floor(min(profit / 10)), ceiling(max(profit / 10)))] * 10
+
+(
+  g_trade_effect_profit <-
+    ggplot(data = trading_plot_data) +
+    geom_line(aes(y = profit, x = w, color = type)) +
+    facet_grid(u_dev ~ prod_het) +
+    scale_color_brewer(palette = "Set1") +
+    ylab("Profit ($/acre)") +
+    xlab("Realized Water Use (inches)") +
+    scale_color_discrete(name = "Measurement Type") +
+    guides(color = guide_legend(nrow = 2, byrow = TRUE)) +
+    theme_bw() +
+    scale_y_continuous(
+      breaks = seq(y_lims[1], y_lims[2], by = 10)
+    ) +
+    scale_x_continuous(breaks = 7:12) +
+    theme_bw() +
+    theme(
+      legend.position = "bottom",
+      panel.grid.minor = element_blank(),
+      panel.spacing.y = unit(1, "lines")
+    )
+)
+
+ggsave("Writing/figures/g_trade_effect_profit.pdf", g_trade_effect_profit, height = 6, width = 6)
+```
+
+## Profit Ratio (distributional inequality)
+
+```{r}
+profit_ratio <- readRDS(here::here("Results/profit_ratio.rds"))
+
+x_breaks <- seq(0.2, ceiling(profit_ratio[, max(ratio)]), by = 0.4)
+
+(
+  g_profit_ratio <-
+    ggplot(profit_ratio) +
+    geom_line(aes(x = ratio, y = prob, color = instrument_type)) +
+    facet_grid(u_dev ~ prod_het) +
+    xlab("Ratio of Profit under Proxy-based to Water-based systems") +
+    ylab("Cumulative Probability") +
+    scale_color_discrete(name = "Insturment Type") +
+    theme_bw() +
+    scale_x_continuous(breaks = x_breaks) +
+    scale_y_continuous(breaks = seq(0, 1, by = 0.25)) +
+    theme(
+      legend.position = "bottom",
+      panel.grid.minor = element_blank(),
+      panel.spacing.y = unit(0.5, "lines"),
+      panel.spacing.x = unit(0.6, "lines")
+    )
+)
+ggsave("Writing/figures/g_profit_ratio.pdf", g_profit_ratio, height = 6, width = 6)
+```
+
 # Visualize: Illustration
@@
   .[quota > opt_w, w := opt_w] %>%
-  farm_data_1[., on = .(w), roll = "nearest"]
+  farm_data_1[., on = .(w), roll = "nearest"] %>%
+  .[, instrument_type := "Quota"]
 ```
@@
     ylab("Profit ($/acre)") +
-    theme_bw()
+    theme_bw() +
+    scale_x_continuous(breaks = 0:15) +
+    scale_y_continuous(
+      breaks = (0:10) * 50,
+      limits = c(0, NA)
+    ) +
+    theme(
+      legend.position = "bottom",
+      panel.grid.minor = element_blank()
+    )
 )
 
-ggsave("Writing/figures/g_illustration_homogeneous.pdf", g_illustration_homogeneous, height = 4, width = 6)
+ggsave("Writing/figures/g_illustration_homogeneous.pdf", g_illustration_homogeneous, height = 4.5, width = 6.5)
 ```
@@
   .[, farmer := "A"] %>%
-  .[, marginal_profit_p := marginal_profit_w / w_A * p_A]
+  .[, marginal_profit_p := marginal_profit_w / w_A * eW_A]
 
@@
   .[, farmer := "B"] %>%
-  .[, marginal_profit_p := marginal_profit_w / w_B * p_B]
+  .[, marginal_profit_p := marginal_profit_w / w_B * eW_B]
 ```
@@
 (
-  g_illustration_homogeneous <-
+  g_illustration_homogeneous_with_trade <-
     ggplot() +
@@
       linetype = 2,
-      color = "red"
+      color = "blue",
+      linewidth = 0.4
+    ) +
+    geom_vline(
+      data = proxy_trade_data,
+      aes(xintercept = w),
+      linetype = 2,
+      color = "blue",
+      linewidth = 0.4
     ) +
@@
       data = production_at_quota,
-      aes(y = profit, x = w),
-      color = "blue",
-      size = 2
+      aes(y = profit, x = w, color = instrument_type),
+      size = 3
     ) +
@@
       data = proxy_trade_data,
-      aes(x = w, y = profit)
+      aes(x = w, y = profit, color = instrument_type),
+      size = 3
+    ) +
+    geom_segment(
+      data = data.table(
+        x = production_at_quota[measure_type == "Proxy", w],
+        y = c(200, 200),
+        xend = proxy_trade_data[measure_type == "Proxy", w],
+        yend = c(200, 200),
+        measure_type = c("Proxy", "Proxy"),
+        farmer = c("A", "B")
+      ),
+      aes(x = x, y = y, xend = xend, yend = yend),
+      arrow = arrow(length = unit(0.3, "cm"))
     ) +
     facet_grid(measure_type ~ farmer) +
-    ylim(0, NA) +
     xlab("Water Use (inches)") +
     ylab("Profit ($/acre)") +
-    theme_bw()
+    theme_bw() +
+    scale_color_discrete(name = "Instrument Type") +
+    scale_x_continuous(breaks = 0:15) +
+    scale_y_continuous(
+      breaks = (0:10) * 50,
+      limits = c(0, NA)
+    ) +
+    theme(
+      legend.position = "bottom",
+      panel.grid.minor = element_blank()
+    )
 
 )
+
+ggsave("Writing/figures/g_illustration_homogeneous_with_trade.pdf", g_illustration_homogeneous_with_trade, height = 5, width = 6.5)
 ```
@@
     measure_type = c("Water", "Water", "Proxy", "Proxy"),
-    quota = c(w_A, w_B, p_A, p_B)
+    quota = c(w_A, w_B, eW_A, eW_B)
   ) %>%
@@
     ylab("Profit ($/acre)") +
-    theme_bw()
+    theme_bw() +
+    scale_x_continuous(breaks = 0:15) +
+    scale_y_continuous(
+      breaks = (0:10) * 50,
+      limits = c(0, NA)
+    ) +
+    theme(
+      legend.position = "bottom",
+      panel.grid.minor = element_blank()
+    )
 )
 
-ggsave("Writing/figures/g_illustration_het.pdf", g_illustration_het, height = 4, width = 6)
+ggsave("Writing/figures/g_illustration_het.pdf", g_illustration_het, height = 4.5, width = 6.5)
 ```
+
+## Save all the illustration datasets
+
+```{r}
+save(production_at_quota, proxy_trade_data, farm_data_het, quota_data_het, farm_data_1, file = "Results/illustration_data.RData")
+```

### 2024-08-14 Writing/manuscript.Rmd
manuscript modified
1. method updated

@@
 other_cost <- 800 # ($/acre)
-```
 
-# Main
+#--- illustration dataset ---#
+load(here::here("Results/illustration_data.RData"))
 
-## Background
-
-+ intensity estimation accuracy
-+ (estimated) intensity-based vs (estimated) area-based (Southern Europe History)
-+ (estimated) intensity-based vs (true) intensity-based [We work on this]
-
-key objective:
-
-  + start a discussion about the implications of the use of mis-measured water use for water use regulation.
-
-  + shed lights on unintentional consequences of using estiamtes rather than actual measurements
-
-Two policies: 
-  + water quota (examples of existing quota systems)
-  + water permit trading
-
-Lack of measurement. Emergence of Open ET as a substitute.
-
-No clear policy design suggestions on how to use water use estiamtes with measurement errors.
-
-# Results
-
-## Profit under water and proxy quota
-
-```{r}
 sum_res <-
@@
 
-Figure \@ref(fig:profit-quota-water-het) below compares profit from agricultural production as a function of actual water use between water and proxy quota across three different production heterogeneity levels.
+\newpage
+
+# Main
+
+## Background
+
++ intensity estimation accuracy
++ (estimated) intensity-based vs (estimated) area-based (Southern Europe History)
++ (estimated) intensity-based vs (true) intensity-based [We work on this]
+
++ Lack of measurement. Use of water use estimates for water management (current and future). Emergence of Open ET as a substitute.
+
+key objective:
+
+  + start a discussion about the implications of the use of mis-measured water use for water use regulation.
+
+  + shed lights on unintentional consequences of using estiamtes rather than actual measurements
+
+Two policies:
+
+  + water quota (examples of existing quota systems)
+  + water permit trading
+
+No clear policy design suggestions on how to use water use estiamtes with measurement errors.
+
+# Results
+
+## Profit under water and proxy quota
+
+Figure \@ref(fig:profit-quota-water-het) below compares profit from agricultural production as a function of actual water use between water and proxy quota across three different production heterogeneity levels and the size of the measurement errors.
 When there is no heterogeneity in farmers' production function, water quota is the most cost effective way to achieve a water use reduction goal (highest profit achievable for a given level of actual water use).
 Under this circumstance, proxy quota with unbiased measurement errors achieves worse than water quota due to asymmetry in downside and upside risk of water use.
+However, as production heterogeneity increases, water quota loses its comparative advantage over proxy quota.
+It can be shown that water quota always outperforms proxy quota on average irrespective of the degere of production heterogeneity when measurement error is independent and production function is concave (show proof in appendix).
+Not surprisingly, profit losses of using proxy quota increase as measurement error size increases.
+Profit loss of using proxy-based quota tends to become greater as the toal realized water use becomes smaller.
 
-```{r profit-quota-water-het, fig.cap = "Comparison of profit from agricultural production between the water and quota systems"}
-knitr::include_graphics("figures/g_profit_quota_w_vs_p.pdf")
+```{r profit-quota-water-het, fig.cap = "The impacts of an increase in the degree of measurement error on profit"}
+knitr::include_graphics("figures/g_profit_quota_comp_stat.pdf")
 ```
@@
 
-pi_dif_2 <- quota_data[farmer == 2 & measure_type == "Proxy", profit] - quota_data[farmer == 2 & measure_type == "Water", profit]
-pi_dif_1 <- quota_data[farmer == 1 & measure_type == "Proxy", profit] - quota_data[farmer == 1 & measure_type == "Water", profit]
+pi_dif_2 <-
+  (quota_data[farmer == 2 & measure_type == "Proxy", profit] - quota_data[farmer == 2 & measure_type == "Water", profit]) %>%
+  round(digits = 1)
+
+pi_dif_1 <-
+  (quota_data[farmer == 1 & measure_type == "Proxy", profit] - quota_data[farmer == 1 & measure_type == "Water", profit]) %>%
+  round(digits = 1)
 ```
 
-Figure \@ref(fig:illust-homegeneous) presents an illustration to build the intuition behind the profit loss due to the use of proxy quota in place of water quota.
-The red dotted lines indicate the effective water use quota.
+We now look at simple two-farm examles to build intuition behind the profit loss due to the use of proxy quota in place of water quota.
+Figure \@ref(fig:illust-homegeneous) presents a case with two homegeneous farmers under water and proxy quota.
+The red dotted lines indicate the effective water quota.
 Under the water quota system, both farmers receive 7 inches of water quota.
@@
 
-When measurement error is independent and production function is concave, water quota always outperforms proxy quota (show proof in appendix).
-
-## The effect of increasing the size of measurement error
-
 \textbf{Convert $u\_dev$ to $R^2$.}
-
-```{r increase-me-degree, fig.cap = "The impacts of an increase in the degree of measurement error on profit"}
-
-knitr::include_graphics("figures/g_profit_quota_comp_stat.pdf")
-```
 
@@
 This is because the inefficiencies in quota allocations are resolved through trading of quota whether it is water or proxy quota.
-(before trading and after trading?)
 
@@
 
-Figure \@ref(fig:trading-profit-illustration) illustrates
+```{r}
+#| echo: false
+
+farmer_A_purchase <-
+  round(proxy_trade_data[farmer == "A", w] - 4, digits = 2)
+
+profit_before_trade_quota <- round(production_at_quota[measure_type == "Proxy", sum(profit)], digits = 2)
+
+profit_after_trade_proxy <- round(proxy_trade_data[, sum(profit)], digits = 2)
+
+profit_after_trade_water <- round(production_at_quota[measure_type == "Water", sum(profit)], digits = 2)
+```
+
+Figure \@ref(fig:trading-profit-illustration) illustrates the impact of allowing for trading proxy quota using the case of two homogeneous farmers illustrated in Figure \@ref(fig:illust-homegeneous).
+In this illustration, the same water quota of 7 is allocated for both farmers under the water-based systems.
+No water quota trading would happen as the marginal profit of water is already equated at water use of 7.
+Under the proxy-base quota system, proxy quota of 7 is allocated for both farmers, but the effective water quota for farmers A and B are 4 and 7, respectively.
+Once trading of proxy quota is alllowed, farmer A would buy `r farmer_A_purchase` proxy quota from farmer B.
+At these production levels, the marginal profit of quota (not water) are equated acros the farmers and no further transfer between them would happen.
+Trading of proxy quota improves the overall profit to `r profit_after_trade_proxy` $/acre from `r profit_before_trade_quota` $/acre.
 
 ```{r trading-profit-illustration, fig.cap = "Illustration of the benefits of trading quota"}
-
+#| echo: false
+knitr::include_graphics("figures/g_illustration_homogeneous_with_trade.pdf")
 ```
@@
 However, it is worth emphasizing that the inefficiency caused by the use of proxy is likely to be minimal as shown in Figure \@ref(fig:trading-profit).
+This point is well-illustrated in Figure \@ref(fig:trading-profit-illustration), where total profit per acre is `r profit_after_trade_water` and `r profit_after_trade_proxy` under the water-quota and proxy-quota trading system, respsectively.
 
-## Use of proxy can damage distributional equity
+Figure \@ref(fig:trading-profit) presents the simualtion results of proxy-quota and water-quota trading systems added to Figure \@ref(fig:profit-quota-water-het).
+As you can see at all levels of production heterogeneity levels and the degres of measurement errors, proxy-quota and water-quota trading systems perform almost identical at all levels of realized water use (water-quota trading is always slightly better than proxy-quota trading as explained earlier).
+Not surprisingly, the benefit of allowing for trading is greater when the degree of measurement errors is larger.
+
+## Use of proxy can exercebate distributional inequity
 
@@
 For example, under the high degree of measurement error and medium heterogenenity scenario, some farmers would make about the half of what they would make under the water quota system.
-At the lower end of the distribution are farmers who would be constrained severely by water use quota, but whose water use estiamtes are much higher than their actual water use.
-At the higher end of the distribution are farmers who would be constrained by water use quota, but whose water use estiamtes are much lower than their actual water use.
+At the lower end of the distribution are farmers who would be constrained severely by water quota, but whose water use estiamtes are much higher than their actual water use.
+At the higher end of the distribution are farmers who would be constrained by water quota, but whose water use estiamtes are much lower than their actual water use.
 Famres who suffer significantly under the quota system can develop strong dissatisfaction of the quota-based regulation system, which in turn may lead to installing water meter themselves.
@@
 
-## Limitations
-
-Assumptions.
-Temporal
++ Unbiased proxy 
+  + can hurt profit  
+  + elements that matter
+    + the heterogeneity of production function
+    + the degree of measurement error
++ Allowing quota trading can be particularly beneficial when proxy is used.
+  + Trade-off of implementing quota trading (this is not anything new)
+    + gain in profit from agricultural production
+    + administrative cost
++ Use of proxy exercebates distributional inequality
+  + trading quota can help here again 
+  + greater chance of litigations from farmers against the administrator
++ Limitations
+  + Assumptions (farmers have linked their practice and water use estimates, but not water)
+    + uncertainty in water use estimates lead to under-use of water, harming profit even more
+  + Temporal
+    + one-year decision
+    + other quota designs (multiple year)
 
@@
 
-##
+This section describes the details of the simulation analysis conducted in this article.
+Our simulation imagines a region with 1000 (denoted as $N$, hereafter) farmers, where a single water governing body possesses a right to devise groundwater policies.
+Our simulation considers nine scenarios in total: three different levels of production heterogeneity times three different degrees of measurement errors.
+Under each scenario, 1000 rounds of individual simulations are run.
+In each simulation round, average water use and profit are calculated at different levels of water or proxy quota levels for four different policies: water-quota, proxy-quota, water-quota trading, proxy-quota trading.
+The key components of the simluation analysis are presented below.
+
+## Crop-water production function
+
+For all $i \in 1,\dots, N$, the crop-water production function follows the Michelich-Baule functional form presented below(citations).
+
+```{=tex}
+\begin{equation}
+y_i = f_i(w) = \phi_i (1 - \alpha_i \cdot e^{-\beta_i\cdot w})
+\end{equation}
+```
+
+Given the price of corn ($P_c$) and water ($P_w$), farmer $i$ is assumed to maximize profit by solving the following maximization problem when no water quota is placed:
+
+```{=tex}
+\begin{equation}
+w^* = argmax_{w} \;\; P_c \cdot f_i(w) - P_w \cdot w
+\end{equation}
+```
+
+Three different sets of the collections of crop-water production functions are generated that vary in the degree of heterogeneity in unconstrained optimal water use ($w^*$).
+Under no-heterogeneity set, farmers share exactly the same profuction function (the same value of $\phi_i$, $\alpha_i$, and $\beta_i$).
+Unde the medium-heterogeneity set, model parameters vary and so does $w^*$.
+Under the high-heterogeneity set, the variance of $w^*$ becomes even greater.
+The distribution of $w^*$ for each of the sets is presented in Figure \@ref(fig:dist-opt-w).
+
+## Measurement error in water use
+
+When water use values are not measured and observed, the administrator estimates water use.
+The estimated value of water use is named "proxy" and denoted as $p$.
+Proxy and water are assumed to follow the relationship below for all the farmers ($i \in 1,\dots, N$):
+
+```{=tex}
+\begin{equation}
+p = \eta_i \cdot w
+\end{equation}
+```
+
+where $\eta_i$ is a scalar greater than 0. Measurement error (denoted as $\mu$) can be written as follows:
+
+```{=tex}
+\begin{equation}
+\mu_i = p - w = (\eta_i - 1)\cdot w
+\end{equation}
+```
+
+While farmers with $\eta_i > 1$ are unfortunate and their water uses are over-estimated, farmers with $\eta_i < 1$ are fortunate and their water uses are under-estimated.
+
+Three different sets of the distribution of $\eta$ are considered that vary in the degree of heterogeneity in $\eta$: low, medium, and high.
+For all the sets, $E[\eta] = 1$ (or equivalently $E[\mu] = 0$), meaning that water use estimation is ubiased.
+
+For a given scenario, the 1000 individual simulation rounds differ only in the realization of randomly drawn values of $\eta$.
+A sample of the empirical (realized) distribution of $\eta$ for each of the sets is presented in Figure \@ref(fig:dist-eta).
+
+## Water use under a quota system
+
+Under both water and proxy quota systems, the same amount of quota is allocated to all the farmers.
+(this is realistic with insufficient information available to the administrator).
+For a given water quota of $\overline{w}$, farmer $i$'s water use would be $min\{w^*, \overline{w}\}$.
+Under the proxy quota system, the same amount of proxy quota ($\overline{p}$) is allocated to all the farmers.
+However, the effective limit on water use varies by farmer.
+Given the proxy quota of $\overline{p}$, the effective water use limit for farmer $i$ is $\overline{p} / \eta_i$, and uses $min\{w^*, \overline{p} / \eta_i\}$.
 
 Assumptions: 
-  + farmers: has learned the degree of under- or over-estimation of water use compared to actual over the years and has learned how to irrigate up to the water use quota
+  + farmers: has learned the degree of under- or over-estimation of water use compared to actual over the years and has learned how to irrigate up to the water quota
+
+## Water use under a trading system
+
+Under a water trading system, the same amount of water quota is first allocated to all the farmers just like water quota system.
+However, farmers are now allowed to sell or buy water quota under a water trading system.
+Assuming no transaction cost of trading, water quota will be traded until the marginal profit of water at their respective level of water uses is equated across the farmers.
+Let $\pi_i(w)$ denote farmer $i$'s profit: $P_c \cdot f_i(w) - P_w \cdot w$.
+Conditional on water quota of $\overline{w}$, individual water uses for the farmers can be identified by finding a series of water use values ($w_1, w_2, \dots, w_N$) that satisfy the following conditions:
+
+```{=tex}
+\begin{align}
+& \frac{\partial \pi_1(w)}{\partial w}\Big\rvert_{w = w_1} = \frac{\partial \pi_2(w)}{\partial w}\Big\rvert_{w = w_2} = \dots = \frac{\partial \pi_N(w)}{\partial w}\Big\rvert_{w = w_N} \\
+& \sum_{i=1}^N w_i = N \cdot \overline{w}
+\end{align}
+```
+
+Under a proxy trading system, proxy quota will be traded until the marginal profit of proxy (not water) at their respective level of effective water (or equivalently proxy) uses is equated across the farmers.
+Conditional on proxy quota of $\overline{p}$, individual proxy use for the farmers can be identified by finding a series of proxy use values ($p_1, p_2, \dots, p_N$) that satisfy the following conditions:
+
+```{=tex}
+\begin{align}
+& \frac{\partial \pi_1(w)}{\partial p}\Big\rvert_{p = p_1} = \frac{\partial \pi_2(w)}{\partial p}\Big\rvert_{p = p_2} = \dots = \frac{\partial \pi_N(w)}{\partial p}\Big\rvert_{p = p_N} \\
+& \sum_{i=1}^N p_i = N \cdot \overline{p}
+\end{align}
+```
 
@@
 ```
+
+## Distribution of water-proxy conversion factor
+
+```{r dist-eta, fig.cap = "Distribution of water-proxy conversion factor", fig.height = 5}
+# knitr::include_graphics("figures/g_eta_dist.pdf")
+```
+
+\clearpage

### 2024-08-14 Writing/manuscript.tex
manuscript modified
1. method updated

@@
 \usepackage{amsmath,amssymb}
-\usepackage{lmodern}
 \usepackage{iftex}
@@
 \else % if luatex or xetex
-  \usepackage{unicode-math}
+  \usepackage{unicode-math} % this also loads fontspec
   \defaultfontfeatures{Scale=MatchLowercase}
   \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+\fi
+\usepackage{lmodern}
+\ifPDFTeX\else
+  % xetex/luatex font selection
 \fi
@@
 \makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
-\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
-\makeatother
-% Scale images if necessary, so that they will not overflow the page
-% margins by default, and it is still possible to overwrite the defaults
-% using explicit options in \includegraphics[width, height, ...]{}
-\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+\newsavebox\pandoc@box
+\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
+  \sbox\pandoc@box{#1}%
+  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
+  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
+  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
+  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
+  \else\usebox{\pandoc@box}%
+  \fi%
+}
 % Set default figure placement to htbp
-\makeatletter
 \def\fps@figure{htbp}
@@
 \usepackage{float}
-\ifLuaTeX
-  \usepackage{selnolig}  % disable illegal ligatures
-\fi
 \usepackage[]{natbib}
 \bibliographystyle{plainnat}
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\usepackage{bookmark}
 \IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same} % disable monospaced font for URLs
+\urlstyle{same}
 \hypersetup{
@@
 
-\hypertarget{main}{%
-\section{Main}\label{main}}
+\newpage
 
-\hypertarget{background}{%
-\subsection{Background}\label{background}}
+\section{Main}\label{main}
+
+\subsection{Background}\label{background}
 
 \begin{itemize}
-\tightlist
 \item
@@
   (estimated) intensity-based vs (true) intensity-based {[}We work on this{]}
+\item
+  Lack of measurement. Use of water use estimates for water management (current and future). Emergence of Open ET as a substitute.
 \end{itemize}
@@
 Two policies:
-+ water quota (examples of existing quota systems)
-+ water permit trading
 
-Lack of measurement. Emergence of Open ET as a substitute.
+\begin{itemize}
+\tightlist
+\item
+  water quota (examples of existing quota systems)
+\item
+  water permit trading
+\end{itemize}
 
@@
 
-\hypertarget{results}{%
-\section{Results}\label{results}}
+\section{Results}\label{results}
 
-\hypertarget{profit-under-water-and-proxy-quota}{%
-\subsection{Profit under water and proxy quota}\label{profit-under-water-and-proxy-quota}}
+\subsection{Profit under water and proxy quota}\label{profit-under-water-and-proxy-quota}
 
-Figure \ref{fig:profit-quota-water-het} below compares profit from agricultural production as a function of actual water use between water and proxy quota across three different production heterogeneity levels.
+Figure \ref{fig:profit-quota-water-het} below compares profit from agricultural production as a function of actual water use between water and proxy quota across three different production heterogeneity levels and the size of the measurement errors.
 When there is no heterogeneity in farmers' production function, water quota is the most cost effective way to achieve a water use reduction goal (highest profit achievable for a given level of actual water use).
 Under this circumstance, proxy quota with unbiased measurement errors achieves worse than water quota due to asymmetry in downside and upside risk of water use.
+However, as production heterogeneity increases, water quota loses its comparative advantage over proxy quota.
+It can be shown that water quota always outperforms proxy quota on average irrespective of the degere of production heterogeneity when measurement error is independent and production function is concave (show proof in appendix).
+Not surprisingly, profit losses of using proxy quota increase as measurement error size increases.
+Profit loss of using proxy-based quota tends to become greater as the toal realized water use becomes smaller.
 
@@
 
-{\centering \includegraphics{figures/g_profit_quota_w_vs_p}
+{\centering \includegraphics{figures/g_profit_quota_comp_stat}
 
@@
 
-\caption{Comparison of profit from agricultural production between the water and quota systems}\label{fig:profit-quota-water-het}
+\caption{The impacts of an increase in the degree of measurement error on profit}\label{fig:profit-quota-water-het}
 \end{figure}
 
-Figure \ref{fig:illust-homegeneous} presents an illustration to build the intuition behind the profit loss due to the use of proxy quota in place of water quota.
-The red dotted lines indicate the effective water use quota.
+We now look at simple two-farm examles to build intuition behind the profit loss due to the use of proxy quota in place of water quota.
+Figure \ref{fig:illust-homegeneous} presents a case with two homegeneous farmers under water and proxy quota.
+The red dotted lines indicate the effective water quota.
 Under the water quota system, both farmers receive 7 inches of water quota.
@@
 Under both proxy and water quota systems, the total water use is 14 inches.
-Farmer B makes 30.6035744 less under the water quota system compared to the proxy quota system.
-However, Farmer A makes 133.2697115 more under the water quota system compared to the proxy quota system.
+Farmer B makes 29.9 less under the water quota system compared to the proxy quota system.
+However, Farmer A makes 128.9 more under the water quota system compared to the proxy quota system.
 This comes from an important nature of crop production with respsect to water: declining marginal impact of water on crop yield.
@@
 
-When measurement error is independent and production function is concave, water quota always outperforms proxy quota (show proof in appendix).
-
-\hypertarget{the-effect-of-increasing-the-size-of-measurement-error}{%
-\subsection{The effect of increasing the size of measurement error}\label{the-effect-of-increasing-the-size-of-measurement-error}}
-
 \textbf{Convert $u\_dev$ to $R^2$.}
 
-\begin{figure}[H]
-
-{\centering \includegraphics{figures/g_profit_quota_comp_stat}
-
-}
-
-\caption{The impacts of an increase in the degree of measurement error on profit}\label{fig:increase-me-degree}
-\end{figure}
-
-\hypertarget{the-effect-of-allowing-trading-quota}{%
-\subsection{The effect of allowing trading quota}\label{the-effect-of-allowing-trading-quota}}
+\subsection{The effect of allowing trading quota}\label{the-effect-of-allowing-trading-quota}
 
@@
 
-Figure \ref{fig:trading-profit-illustration} illustrates
+Figure \ref{fig:trading-profit-illustration} illustrates the impact of allowing for trading proxy quota using the case of two homogeneous farmers illustrated in Figure \ref{fig:illust-homegeneous}.
+In this illustration, the same water quota of 7 is allocated for both farmers under the water-based systems.
+No water quota trading would happen as the marginal profit of water is already equated at water use of 7.
+Under the proxy-base quota system, proxy quota of 7 is allocated for both farmers, but the effective water quota for farmers A and B are 4 and 7, respectively.
+Once trading of proxy quota is alllowed, farmer A would buy 1.85 proxy quota from farmer B.
+At these production levels, the marginal profit of quota (not water) are equated acros the farmers and no further transfer between them would happen.
+Trading of proxy quota improves the overall profit to 920.08 \$/acre from 831.94 \$/acre.
+
+\begin{figure}[H]
+
+{\centering \includegraphics{figures/g_illustration_homogeneous_with_trade}
+
+}
+
+\caption{Illustration of the benefits of trading quota}\label{fig:trading-profit-illustration}
+\end{figure}
 
@@
 However, it is worth emphasizing that the inefficiency caused by the use of proxy is likely to be minimal as shown in Figure \ref{fig:trading-profit}.
+This point is well-illustrated in Figure \ref{fig:trading-profit-illustration}, where total profit per acre is 930.91 and 920.08 under the water-quota and proxy-quota trading system, respsectively.
 
-\hypertarget{use-of-proxy-can-damage-distributional-equity}{%
-\subsection{Use of proxy can damage distributional equity}\label{use-of-proxy-can-damage-distributional-equity}}
+Figure \ref{fig:trading-profit} presents the simualtion results of proxy-quota and water-quota trading systems added to Figure \ref{fig:profit-quota-water-het}.
+As you can see at all levels of production heterogeneity levels and the degres of measurement errors, proxy-quota and water-quota trading systems perform almost identical at all levels of realized water use (water-quota trading is always slightly better than proxy-quota trading as explained earlier).
+Not surprisingly, the benefit of allowing for trading is greater when the degree of measurement errors is larger.
+
+\subsection{Use of proxy can exercebate distributional inequity}\label{use-of-proxy-can-exercebate-distributional-inequity}
 
@@
 
-\hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
+\section{Discussion}\label{discussion}
 
-\hypertarget{limitations}{%
-\subsection{Limitations}\label{limitations}}
+\begin{itemize}
+\tightlist
+\item
+  Unbiased proxy
 
-Assumptions.
+  \begin{itemize}
+  \tightlist
+  \item
+    can hurt profit\\
+  \item
+    elements that matter
+
+    \begin{itemize}
+    \tightlist
+    \item
+      the heterogeneity of production function
+    \item
+      the degree of measurement error
+    \end{itemize}
+  \end{itemize}
+\item
+  Allowing quota trading can be particularly beneficial when proxy is used.
+
+  \begin{itemize}
+  \tightlist
+  \item
+    Trade-off of implementing quota trading (this is not anything new)
+
+    \begin{itemize}
+    \tightlist
+    \item
+      gain in profit from agricultural production
+    \item
+      administrative cost
+    \end{itemize}
+  \end{itemize}
+\item
+  Use of proxy exercebates distributional inequality
+
+  \begin{itemize}
+  \tightlist
+  \item
+    trading quota can help here again
+  \item
+    greater chance of litigations from farmers against the administrator
+  \end{itemize}
+\item
+  Limitations
+
+  \begin{itemize}
+  \tightlist
+  \item
+    Assumptions (farmers have linked their practice and water use estimates, but not water)
+
+    \begin{itemize}
+    \tightlist
+    \item
+      uncertainty in water use estimates lead to under-use of water, harming profit even more
+    \end{itemize}
+  \item
     Temporal
 
-\hypertarget{methods}{%
-\section{Methods}\label{methods}}
+    \begin{itemize}
+    \tightlist
+    \item
+      one-year decision
+    \item
+      other quota designs (multiple year)
+    \end{itemize}
+  \end{itemize}
+\end{itemize}
 
-\hypertarget{section}{%
-\subsection{}\label{section}}
+\section{Methods}\label{methods}
+
+This section describes the details of the simulation analysis conducted in this article.
+Our simulation imagines a region with 1000 (denoted as \(N\), hereafter) farmers, where a single water governing body possesses a right to devise groundwater policies.
+Our simulation considers nine scenarios in total: three different levels of production heterogeneity times three different degrees of measurement errors.
+Under each scenario, 1000 rounds of individual simulations are run.
+In each simulation round, average water use and profit are calculated at different levels of water or proxy quota levels for four different policies: water-quota, proxy-quota, water-quota trading, proxy-quota trading.
+The key components of the simluation analysis are presented below.
+
+\subsection{Crop-water production function}\label{crop-water-production-function}
+
+For all \(i \in 1,\dots, N\), the crop-water production function follows the Michelich-Baule functional form presented below(citations).
+
+\begin{equation}
+y_i = f_i(w) = \phi_i (1 - \alpha_i \cdot e^{-\beta_i\cdot w})
+\end{equation}
+
+Given the price of corn (\(P_c\)) and water (\(P_w\)), farmer \(i\) is assumed to maximize profit by solving the following maximization problem when no water quota is placed:
+
+\begin{equation}
+w^* = argmax_{w} \;\; P_c \cdot f_i(w) - P_w \cdot w
+\end{equation}
+
+Three different sets of the collections of crop-water production functions are generated that vary in the degree of heterogeneity in unconstrained optimal water use (\(w^*\)).
+Under no-heterogeneity set, farmers share exactly the same profuction function (the same value of \(\phi_i\), \(\alpha_i\), and \(\beta_i\)).
+Unde the medium-heterogeneity set, model parameters vary and so does \(w^*\).
+Under the high-heterogeneity set, the variance of \(w^*\) becomes even greater.
+The distribution of \(w^*\) for each of the sets is presented in Figure \ref{fig:dist-opt-w}.
+
+\subsection{Measurement error in water use}\label{measurement-error-in-water-use}
+
+When water use values are not measured and observed, the administrator estimates water use.
+The estimated value of water use is named ``proxy'' and denoted as \(p\).
+Proxy and water are assumed to follow the relationship below for all the farmers (\(i \in 1,\dots, N\)):
+
+\begin{equation}
+p = \eta_i \cdot w
+\end{equation}
+
+where \(\eta_i\) is a scalar greater than 0. Measurement error (denoted as \(\mu\)) can be written as follows:
+
+\begin{equation}
+\mu_i = p - w = (\eta_i - 1)\cdot w
+\end{equation}
+
+While farmers with \(\eta_i > 1\) are unfortunate and their water uses are over-estimated, farmers with \(\eta_i < 1\) are fortunate and their water uses are under-estimated.
+
+Three different sets of the distribution of \(\eta\) are considered that vary in the degree of heterogeneity in \(\eta\): low, medium, and high.
+For all the sets, \(E[\eta] = 1\) (or equivalently \(E[\mu] = 0\)), meaning that water use estimation is ubiased.
+
+For a given scenario, the 1000 individual simulation rounds differ only in the realization of randomly drawn values of \(\eta\).
+A sample of the empirical (realized) distribution of \(\eta\) for each of the sets is presented in Figure \ref{fig:dist-eta}.
+
+\subsection{Water use under a quota system}\label{water-use-under-a-quota-system}
+
+Under both water and proxy quota systems, the same amount of quota is allocated to all the farmers.
+(this is realistic with insufficient information available to the administrator).
+For a given water quota of \(\overline{w}\), farmer \(i\)'s water use would be \(min\{w^*, \overline{w}\}\).
+Under the proxy quota system, the same amount of proxy quota (\(\overline{p}\)) is allocated to all the farmers.
+However, the effective limit on water use varies by farmer.
+Water and proxy are assumed to follow the following relationship for farmer \(i\),
+
+\begin{equation}
+w = \eta_i \cdot p
+\end{equation}
+
+Given the proxy quota of \(\overline{p}\), the effective water use limit for farmer \(i\) is \(\overline{p} / \eta_i\), and uses \(min\{w^*, \overline{p} / \eta_i\}\).
 
 Assumptions:
-+ farmers: has learned the degree of under- or over-estimation of water use compared to actual over the years and has learned how to irrigate up to the water use quota
++ farmers: has learned the degree of under- or over-estimation of water use compared to actual over the years and has learned how to irrigate up to the water quota
 
-\hypertarget{data-and-code-availability}{%
-\subsection{Data and Code Availability}\label{data-and-code-availability}}
+\subsection{Water use under a trading system}\label{water-use-under-a-trading-system}
+
+Under a water trading system, the same amount of water quota is first allocated to all the farmers just like water quota system.
+However, farmers are now allowed to sell or buy water quota under a water trading system.
+Assuming no transaction cost of trading, water quota will be traded until the marginal profit of water at their respective level of water uses is equated across the farmers.
+Let \(\pi_i(w)\) denote farmer \(i\)'s profit: \(P_c \cdot f_i(w) - P_w \cdot w\).
+Conditional on water quota of \(\overline{w}\), individual water uses for the farmers can be identified by finding a series of water use values (\(w_1, w_2, \dots, w_N\)) that satisfy the following conditions:
+
+\begin{align}
+& \frac{\partial \pi_1(w)}{\partial w}\Big\rvert_{w = w_1} = \frac{\partial \pi_2(w)}{\partial w}\Big\rvert_{w = w_2} = \dots = \frac{\partial \pi_N(w)}{\partial w}\Big\rvert_{w = w_N} \\
+& \sum_{i=1}^N w_i = N \cdot \overline{w}
+\end{align}
+
+Under a proxy trading system, proxy quota will be traded until the marginal profit of proxy (not water) at their respective level of effective water (or equivalently proxy) uses is equated across the farmers.
+Conditional on proxy quota of \(\overline{p}\), individual proxy use for the farmers can be identified by finding a series of proxy use values (\(p_1, p_2, \dots, p_N\)) that satisfy the following conditions:
+
+\begin{align}
+& \frac{\partial \pi_1(w)}{\partial p}\Big\rvert_{p = p_1} = \frac{\partial \pi_2(w)}{\partial p}\Big\rvert_{p = p_2} = \dots = \frac{\partial \pi_N(w)}{\partial p}\Big\rvert_{p = p_N} \\
+& \sum_{i=1}^N p_i = N \cdot \overline{p}
+\end{align}
+
+\subsection{Simulations}\label{simulations}
+
+We have nine sets of scenarios: three levels of heterogeneity in optimal water use
+
+1000 rounds of simulations were run
+
+. In each of the rounds,
+
+\subsection{Data and Code Availability}\label{data-and-code-availability}
 
@@
 
-\hypertarget{appendix-appendix}{%
-\appendix}
+\appendix
 
-\hypertarget{distribution-of-optimal-water-use-under-no-water-use-constraints}{%
-\subsection{Distribution of optimal water use under no water use constraints}\label{distribution-of-optimal-water-use-under-no-water-use-constraints}}
+\subsection{Distribution of optimal water use under no water use constraints}\label{distribution-of-optimal-water-use-under-no-water-use-constraints}
 
@@
 
+\subsection{Distribution of water-proxy conversion factor}\label{distribution-of-water-proxy-conversion-factor}
+
+\clearpage
+
   \bibliography{DRA.bib}

### 2024-08-14 Writing/manuscript.Rmd
readme added

@@
 Under each scenario, 1000 rounds of individual simulations are run.
-In each simulation round, average water use and profit are calculated at different levels of water or proxy quota levels for four different policies: water-quota, proxy-quota, water-quota trading, proxy-quota trading.
+In each simulation round, measurement errors are drawn randomly for the individual farmers, and then average (across the farmers) water use and profit are calculated at different levels of water or proxy quota levels for four different policies: water-quota, proxy-quota, water-quota trading, proxy-quota trading.
+The summary of the 1000 simulation rounds.
 The key components of the simluation analysis are presented below.
@@
 
-For all $i \in 1,\dots, N$, the crop-water production function follows the Michelich-Baule functional form presented below(citations).
+For all faemers $i \in 1,\dots, N$, the crop-water production function follows the Michelich-Baule functional form presented below(citations).
 
@@
 ```
+
+where $y$ is corn yield (kg/ha), $w$ is water use (mm), and $\phi$, $\alpha$, and $\beta$ are model parameters that govern how corn yield responds to water use.
 
@@
 For all the sets, $E[\eta] = 1$ (or equivalently $E[\mu] = 0$), meaning that water use estimation is ubiased.
-
-For a given scenario, the 1000 individual simulation rounds differ only in the realization of randomly drawn values of $\eta$.
 A sample of the empirical (realized) distribution of $\eta$ for each of the sets is presented in Figure \@ref(fig:dist-eta).
 
-## Water use under a quota system
+## Water use under quota and trading systems
 
-Under both water and proxy quota systems, the same amount of quota is allocated to all the farmers.
+Under both water and proxy quota systems without trading, the same amount of quota is allocated to all the farmers.
 (this is realistic with insufficient information available to the administrator).
@@
   + farmers: has learned the degree of under- or over-estimation of water use compared to actual over the years and has learned how to irrigate up to the water quota
-
-## Water use under a trading system
 
@@
 
-The datasets created in this article are all computer-generated using R codes. All the datasets and codes are available at .
+The datasets created in this article are all computer-generated using R (citation).
+All the codes and datasets are available at [this GitHub repository](https://github.com/tmieno2/Measurement-Error-Water-Management).
+Instructions for reproducing all the outputs presented in this article are provided at the bottom of the page.
 

### 2024-08-14 Writing/manuscript.tex
readme added

@@
 
-For all \(i \in 1,\dots, N\), the crop-water production function follows the Michelich-Baule functional form presented below(citations).
+For all faemers \(i \in 1,\dots, N\), the crop-water production function follows the Michelich-Baule functional form presented below(citations).
 
@@
 \end{equation}
+
+where \(y\) is corn yield (kg/ha), \(w\) is water use (mm), and \(\phi\), \(\alpha\), and \(\beta\) are model parameters that govern how corn yield responds to water use.
 
@@
 For all the sets, \(E[\eta] = 1\) (or equivalently \(E[\mu] = 0\)), meaning that water use estimation is ubiased.
-
-For a given scenario, the 1000 individual simulation rounds differ only in the realization of randomly drawn values of \(\eta\).
 A sample of the empirical (realized) distribution of \(\eta\) for each of the sets is presented in Figure \ref{fig:dist-eta}.
 
-\subsection{Water use under a quota system}\label{water-use-under-a-quota-system}
+\subsection{Water use under quota and trading systems}\label{water-use-under-quota-and-trading-systems}
 
-Under both water and proxy quota systems, the same amount of quota is allocated to all the farmers.
+Under both water and proxy quota systems without trading, the same amount of quota is allocated to all the farmers.
 (this is realistic with insufficient information available to the administrator).
@@
 However, the effective limit on water use varies by farmer.
-Water and proxy are assumed to follow the following relationship for farmer \(i\),
-
-\begin{equation}
-w = \eta_i \cdot p
-\end{equation}
-
 Given the proxy quota of \(\overline{p}\), the effective water use limit for farmer \(i\) is \(\overline{p} / \eta_i\), and uses \(min\{w^*, \overline{p} / \eta_i\}\).
@@
 + farmers: has learned the degree of under- or over-estimation of water use compared to actual over the years and has learned how to irrigate up to the water quota
-
-\subsection{Water use under a trading system}\label{water-use-under-a-trading-system}
 
@@
 
-\subsection{Simulations}\label{simulations}
-
-We have nine sets of scenarios: three levels of heterogeneity in optimal water use
-
-1000 rounds of simulations were run
-
-. In each of the rounds,
-
 \subsection{Data and Code Availability}\label{data-and-code-availability}
 
-The datasets created in this article are all computer-generated using R codes. All the datasets and codes are available at .
+The datasets created in this article are all computer-generated using R codes.
+All the datasets and codes are available at the \href{https://github.com/tmieno2/Measurement-Error-Water-Management}{following GitHub repository}.
 

### 2024-08-19 Codes/1_analysis.qmd
typst version added

@@
 
-save(corn_price, e_price, w_price, other_cost)
+# save(corn_price, e_price, w_price, other_cost)
 ```
@@
   )
+
+saveRDS(par_data, "Results/parameter_data.rds")
 ```
@@
   dplyr::mutate(results = list(
-    run_analysis(parameter_sets = par_sets_w, farmer_data, prod_data, num_it = 1)
+    run_analysis(
+      parameter_sets = par_sets_w,
+      farmer_data,
+      prod_data,
+      num_it = 1
+    )
   )) %>%
@@
   dplyr::mutate(results = list(
-    run_analysis(parameter_sets = par_sets_p, farmer_data, prod_data, num_it = 100, num_cores = 8)
+    run_analysis(
+      parameter_sets = par_sets_p, 
+      farmer_data, 
+      prod_data, 
+      num_it = 1000, 
+      num_cores = parallel::detectCores() - 2
+    )
   )) %>%

### 2024-08-19 Codes/2_make_figures.qmd
typst version added

@@
 ggsave(here::here("Writing/figures/g_opt_w_dist.pdf"), g_opt_w_dist, height = 5, width = 6)
+```
+
+## Distribution of water-proxy conversion factor
+
+```{r}
+par_data <-
+  readRDS("Results/parameter_data.rds") %>%
+  .[u_dev != 0, ] %>%
+  .[dir_cor == "0", ] %>%
+  .[target_w == 7, ] %>%
+  .[, ]
+
+eta_data <-
+  lapply(
+    1:nrow(par_data),
+    \(x) {
+      quota_data <-
+        make_quota_data(
+          system_data$farmer_data[[1]],
+          target_w = par_data[x, target_w],
+          u_dev = par_data[x, u_dev],
+          cor = par_data[x, dir_cor],
+          num_it = 1
+        ) %>%
+        .[, u_dev := par_data[x, u_dev]]
+    }
+  ) %>%
+  rbindlist() %>%
+  .[, med_txt := case_when(
+    u_dev == 0.1 ~ "ME: Low",
+    u_dev == 0.3 ~ "ME: Medium",
+    u_dev == 0.5 ~ "ME: High"
+  )] %>%
+  .[, med_txt := factor(med_txt, levels = c("ME: Low", "ME: Medium", "ME: High"))]
+
+ggplot(eta_data) +
+  geom_histogram(
+    aes(
+      x = proxy_to_water,
+      y = ifelse(after_stat(count) > 0, after_stat(count), NA)
+    ),
+    color = "blue",
+    fill = NA
+  ) +
+  facet_grid(med_txt ~ .) +
+  theme_bw() +
+  xlab("Water to proxy conversion factor") +
+  ylab("Count")
+
 ```
@@
 ggsave("Writing/figures/g_profit_quota_comp_stat.pdf", g_profit_quota_comp_stat, height = 6, width = 6)
+
+ggsave("Writing/figures/g_profit_quota_comp_stat.png", g_profit_quota_comp_stat, width = 6, height = 6, dpi = 400)
 ```

### 2024-08-19 Writing/manuscript.tex
typst version added

@@
 \begin{equation}
-p = \eta_i \cdot w
+p = \eta_i\cdot w
 \end{equation}
@@
 
-The datasets created in this article are all computer-generated using R codes.
-All the datasets and codes are available at the \href{https://github.com/tmieno2/Measurement-Error-Water-Management}{following GitHub repository}.
+The datasets created in this article are all computer-generated using R (citation).
+All the codes and datasets are available at \href{https://github.com/tmieno2/Measurement-Error-Water-Management}{this GitHub repository}.
+Instructions for reproducing all the outputs presented in this article are provided at the bottom of the page.
 

### 2024-08-19 Writing/manuscript_typst.qmd
typst version added

--- 2024-08-12 Writing/manuscript.Rmd
@@
 ---
-title: Implications of Measurement Errors in Water Use Estimates for Water Management
+title: "Hello Typst!"
 author:
-  - Taro Mieno^[Department of Agricultural Economics, University of Nebraska Lincoln, tmieno2@unl.edu]
-  - Timothy Foster^[Department of WWW, University of Manchester, timothy.foster@manchester.ac.uk]
-  - Nicholas Brozovic^[Department of Agricultural Economics, University of Nebraska Lincoln, nbrozovic@nebraska.edu]
-abstract: |
-  abstract here
-acknowledgments: |
-  Funding for the research in this manuscript was provided by 
+  - name: "Taro Mieno^[University of Nebraska-Lincoln, Email: tmieno2@unl.edu]"
+    orcid: 0000-0003-1689-0557
+  - name: Timothy Foster^[University of Mancherster]
+    orcid: 0000-0003-1689-0557
+  - name: Nicholas Brozovic^[University of Nebraska-Lincoln]
+    orcid: 0000-0003-1689-0557
+format:
+  typst:
+    toc: false
+    keep-typ: true
+    section-numbering: 1.1.a
+    columns: 1
+    fig-format: png
 bibliography: DRA.bib
-output:
-  bookdown::pdf_document2:
-    extra_dependencies: ["float"]
-    citation_package: natbib
-    keep_tex: true
-    toc: false
-    includes:
-      in_header: "preamble.tex"
+bibliographystyle: apa
 ---
@@
 #--- packages ---#
-library(data.table)
-library(tidyverse)
-library(stringr)
-library(sf)
 library(here)
-library(tmap)
-library(modelsummary)
-library(patchwork)
-library(kableExtra)
+library(dplyr)
 
@@
 
-Figure \@ref(fig:profit-quota-water-het) below compares profit from agricultural production as a function of actual water use between water and proxy quota across three different production heterogeneity levels.
+# Results
+
+## Profit under water and proxy quota
+
+@fig-profit-quota-water-het below compares profit from agricultural production as a function of actual water use between water and proxy quota across three different production heterogeneity levels and the size of the measurement errors.
 When there is no heterogeneity in farmers' production function, water quota is the most cost effective way to achieve a water use reduction goal (highest profit achievable for a given level of actual water use).
 Under this circumstance, proxy quota with unbiased measurement errors achieves worse than water quota due to asymmetry in downside and upside risk of water use.
+However, as production heterogeneity increases, water quota loses its comparative advantage over proxy quota.
+It can be shown that water quota always outperforms proxy quota on average irrespective of the degere of production heterogeneity when measurement error is independent and production function is concave (show proof in appendix).
+Not surprisingly, profit losses of using proxy quota increase as measurement error size increases.
+Profit loss of using proxy-based quota tends to become greater as the toal realized water use becomes smaller.
 
-```{r profit-quota-water-het, fig.cap = "Comparison of profit from agricultural production between the water and quota systems"}
-knitr::include_graphics("figures/g_profit_quota_w_vs_p.pdf")
+```{r}
+#| label: fig-profit-quota-water-het
+#| fig-cap: "The impacts of an increase in the degree of measurement error on profit"
+knitr::include_graphics("figures/g_profit_quota_comp_stat.png")
 ```
 
-```{r}
-#| echo: false
-
-system_data <- readRDS(here::here("Results/quota_results_comp_stat.rds"))
-
-farm_data <-
-  data.table(system_data)[prod_het == "medium", farmer_data][[1]] %>%
-  #--- use farmer 1 ---#
-  .[farmer == 1, ] %>%
-  .[, farmer := NULL] %>%
-  expand_grid_df(., data.table(w = seq(0, 15, by = 0.1))) %>%
-  .[, yield := ymax * (1 - alpha * exp(-beta * w))] %>%
-  .[, w_cost := w_price * w] %>%
-  .[, profit := corn_price * yield - w_cost - other_cost] %>%
-  .[, marginal_cost_w := w_price] %>%
-  .[, marginal_prod_w := ymax * alpha * beta * exp(-beta * w)] %>%
-  .[, marginal_profit_w := marginal_prod_w * corn_price - marginal_cost_w]
-
-opt_w <- unique(farm_data$opt_w)
-
-quota_data <-
-  data.table(
-    farmer = c(1, 2, 1, 2),
-    measure_type = c("Water", "Water", "Proxy", "Proxy"),
-    quota = c(7, 7, 4, 10)
-  ) %>%
-  .[, w := quota] %>%
-  .[quota > opt_w, w := opt_w] %>%
-  farm_data[., on = .(w), roll = "nearest"]
-
-pi_dif_2 <- quota_data[farmer == 2 & measure_type == "Proxy", profit] - quota_data[farmer == 2 & measure_type == "Water", profit]
-pi_dif_1 <- quota_data[farmer == 1 & measure_type == "Proxy", profit] - quota_data[farmer == 1 & measure_type == "Water", profit]
-```
-
-Figure \@ref(fig:illust-homegeneous) presents an illustration to build the intuition behind the profit loss due to the use of proxy quota in place of water quota.
-The red dotted lines indicate the effective water use quota.
-Under the water quota system, both farmers receive 7 inches of water quota.
-Since the unconstrained profit maximizing water use is `r round(opt_w, digits = 2)` inches, both farmers use up all the allocated quota and use 10 inches of water.
-Under the proxy quota system, they are allocated the same amount of proxy quota.
-However, measurement error in proxy quota resulted in effective water quota of 4 and 10 inches for farmer A and B, respectively.
-Both farmers use their allocated amout of water.
-Under both proxy and water quota systems, the total water use is 14 inches.
-Farmer B makes `r pi_dif_2` less under the water quota system compared to the proxy quota system.
-However, Farmer A makes `r -pi_dif_1` more under the water quota system compared to the proxy quota system.
-This comes from an important nature of crop production with respsect to water: declining marginal impact of water on crop yield.
-As can be seen in the profit-water relationship, removing an inch of water from 6 inches has much larger negative impact compared to revmoing an inch of water from 10 inches.
-
-```{r illust-homegeneous, fig.cap = "Illustration of profit loss due to the use of proxy for quota-based regulation: a case of homegeneous producers"}
-#| warning: false
-knitr::include_graphics("figures/g_illustration_homogeneous.pdf")
-```
-
-However, as the heterogeneity of farmers increases, comparative advantage of water quota over proxy quota diminishes.
-While the performance of both systems declines as the level of heterogeneity increases, water quota is affected more so than the proxy quota system.
-This is because uniform quota now acts like heterogeneous quota under homogeneous production function because the same quota is given to farmers with heterogeneous water demand.
-This is illustrated in Figure \@ref(fig:illust-heterogeneous).
-In this example,  farmer A needs less water than farmer B.
-Water and proxy quota allocated to the farmers are exactly the same as the previous case.
-In this example, errors in proxy happened to realize so that more effective water quota is given to farmer B than farmer A.
-Consequently, proxy quota produces a higher total profit than water quota.
-Of course, if error happened to go the opposite way, then the performance of proxy quota relative to water quota is even worse compared to the homogeneous case.
-This is a big contrast to the homogeneous case because water quota is always better than proxy quota in that case.
-Consequently, proxy quota performs relatively better under heterogeneous cases.
-On average, the positive and negative effects of measurement errors tend to even out.
-However, proxy quota is never better than water quota **on average** (see Appendix ...
-for mathematical proof).
-
-```{r illust-heterogeneous, fig.cap = "Illustration of profit loss due to the use of proxy for quota-based regulation: a case of heterogeneous producers"}
-#| warning: false
-
-knitr::include_graphics("figures/g_illustration_het.pdf")
-```
-
-When measurement error is independent and production function is concave, water quota always outperforms proxy quota (show proof in appendix).
-
-## The effect of increasing the size of measurement error
-
-\textbf{Convert $u\_dev$ to $R^2$.}
-
-```{r increase-me-degree, fig.cap = "The impacts of an increase in the degree of measurement error on profit"}
-
-knitr::include_graphics("figures/g_profit_quota_comp_stat.pdf")
-```
-
-## The effect of allowing trading quota
-
-Allowing quota to be traded among farmers can dramatically change the relative performance of the water- and quota-based regulation.
-Figure \@ref(fig:trading-profit) presents profit for water-based quota, proxy-based quota, water-based quota trading, and proxy-based quota trading regulation systems.
-As shown in the figure, the disadvantage of using proxy almost disappears when trading of quota is allowed.
-This is because the inefficiencies in quota allocations are resolved through trading of quota whether it is water or proxy quota.
-(before trading and after trading?)
-
-```{r trading-profit, fig.cap = "Comparison of profit from agricultural production between the water and quota systems when quota trading is allowed"}
-#| echo: false
-knitr::include_graphics("figures/g_trade_effect_profit.pdf")
-```
-
-Figure \@ref(fig:trading-profit-illustration) illustrates
-
-```{r trading-profit-illustration, fig.cap = "Illustration of the benefits of trading quota"}
-
-```
-
-While water-quota and proxy-quota trading perform about the same, water-quota always leads to a higher total profit for a given level of realized water use.
-In other words, to achieve a certain water use goal, water-quota trading is always to more cost-effective than proxy-quota trading.
-Under water-quota trading, the margial profit of water is equalized across the farmers, which is a necessary condition to achieve the highest profit for a given level of total water use.
-Under proxy-quota trading, the marginal profit of proxy is equalized across the farmers, not the margial profit of water (See Appendix ...
-for a mathematical proof).
-However, it is worth emphasizing that the inefficiency caused by the use of proxy is likely to be minimal as shown in Figure \@ref(fig:trading-profit).
-
-## Use of proxy can damage distributional equity
-
-Figure \@ref(fig:distributional-equity) presents the cumulative probability of the ratio of profit under quota-based relative to water-based system for quota (red) and permit trading (blue).
-Ratio of less than 1 indicates making less profit under the quota-based system compared to the water-based system.
-If farmers make just as much profir under proxy-based regulation compared to water-based regulation, then the cumulative probability line would be a vertical line at 1.
-For example, under the high degree of measurement error and medium heterogenenity scenario, some farmers would make about the half of what they would make under the water quota system.
-At the lower end of the distribution are farmers who would be constrained severely by water use quota, but whose water use estiamtes are much higher than their actual water use.
-At the higher end of the distribution are farmers who would be constrained by water use quota, but whose water use estiamtes are much lower than their actual water use.
-Famres who suffer significantly under the quota system can develop strong dissatisfaction of the quota-based regulation system, which in turn may lead to installing water meter themselves.
-If they discover the over-estimation of their water use, they may appeal to legal actions against the administrator for their unfair treatment.
-Allowind quota trading greatly diminishes the distributional inequality, though not completely.
-This is because unfortunate farmers who suffered from over-estimation of their water use can now at least purchase proxy quota to increase their production level.
-
-```{r distributional-equity, fig.cap = "Distribution of profit under various regulation systems"}
-knitr::include_graphics("figures/g_profit_ratio.pdf")
-```
-
-# Discussion
-
-## Limitations
-
-Assumptions.
-Temporal
-
-# Methods
-
-##
-
-Assumptions: 
-  + farmers: has learned the degree of under- or over-estimation of water use compared to actual over the years and has learned how to irrigate up to the water use quota
-
-## Data and Code Availability
-
-The datasets created in this article are all computer-generated using R codes. All the datasets and codes are available at .
-
-\clearpage
-
-# (APPENDIX) Appendix {-}
-
-## Distribution of optimal water use under no water use constraints
-
-```{r dist-opt-w, fig.cap = "Distribution of optimal water use under no water use constraints", fig.height = 5}
-knitr::include_graphics("figures/g_opt_w_dist.pdf")
-```
+@grafton2018paradox

### 2024-08-19 Codes/functions/functions.R

@@ -88,11 +88,6 @@ run_analysis <- function(parameter_sets, farmer_data, prod_data, num_it = 1, num
             num_it = num_it
           )
 
-        # temp <-
-        #   copy(quota_data) %>%
-        #   .[, w := rnorm(.N, 12, sd = 3)] %>%
-        #   .[, est_w := w / proxy_to_water]
-        
         # lm(est_w ~ w, data = temp) %>% summary() %>% .$r.squared
 
         #--- analysis ---#
@@ -129,8 +124,8 @@ run_analysis_by_case <- function(prod_data, quota_data) {
           copy(prod_data) %>%
           quota_data[case == x, ][., on = "farmer"] %>%
           #--- proxy use ---#
-          .[, proxy := w / proxy_to_water] %>%
-          .[, marginal_profit_p := proxy_to_water * marginal_profit_w]
+          .[, proxy := w * water_to_proxy] %>%
+          .[, marginal_profit_p := marginal_profit_w / water_to_proxy]
 
         #---------------------
         #- Quota Analysis
@@ -207,7 +202,7 @@ make_quota_data <- function(farmer_data, target_w, u_dev, cor, num_it = 100) {
           copy(farmer_data)[, .(farmer, opt_w)] %>%
             .[, dev_from_mean := (opt_w - mean(opt_w)) / mean_opt_w * target_w] %>%
             #--- effective water use limit ---#
-            .[, w_lim := (target_w + dev_from_mean) * runif(1, min = 1 - u_dev, max = 1 + u_dev), by = farmer]
+            .[, w_lim := (target_w + dev_from_mean) / runif(1, min = 1 - u_dev, max = 1 + u_dev), by = farmer]
         }
       )
   } else if (cor == "-") {
@@ -218,7 +213,7 @@ make_quota_data <- function(farmer_data, target_w, u_dev, cor, num_it = 100) {
           copy(farmer_data)[, .(farmer, opt_w)] %>%
             .[, dev_from_mean := (opt_w - mean(opt_w)) / mean_opt_w * target_w] %>%
             #--- effective water use limit ---#
-            .[, w_lim := (target_w - dev_from_mean) * runif(1, min = 1 - u_dev, max = 1 + u_dev), by = farmer]
+            .[, w_lim := (target_w - dev_from_mean) / runif(1, min = 1 - u_dev, max = 1 + u_dev), by = farmer]
         }
       )
   } else if (cor == "0") {
[…]

### 2024-11-13 Codes/1_analysis.qmd
tex version added

@@
       prod_data, 
-      num_it = 1000, 
+      num_it = 100, 
       num_cores = parallel::detectCores() - 2
@@
   .[, prod_het := factor(prod_het, c("Zero", "Medium", "High"))]
+
+saveRDS(sum_res, here::here("Results/results_summary.rds"))
 ```

### 2024-11-13 Codes/2_make_figures.qmd
tex version added

@@
 
-ggsave(here::here("Writing/figures/g_opt_w_dist.pdf"), g_opt_w_dist, height = 5, width = 6)
+ggsave(here::here("Writing/figures/g_opt_w_dist.png"), g_opt_w_dist, height = 5, width = 6, dpi = 400)
 ```
@@
 
-ggsave("Writing/figures/g_profit_quota_w_vs_p.pdf", g_profit_quota_w_vs_p, height = 3.5, width = 6)
+ggsave("Writing/figures/g_profit_quota_w_vs_p.png", g_profit_quota_w_vs_p, height = 3.5, width = 6, dpi = 400)
 ```
@@
 
-ggsave("Writing/figures/g_trade_effect_profit.pdf", g_trade_effect_profit, height = 6, width = 6)
+ggsave("Writing/figures/g_trade_effect_profit.png", g_trade_effect_profit, height = 6, width = 6, dpi = 400)
 ```
@@
 )
-ggsave("Writing/figures/g_profit_ratio.pdf", g_profit_ratio, height = 6, width = 6)
+ggsave("Writing/figures/g_profit_ratio.png", g_profit_ratio, height = 6, width = 6, dpi = 400)
 ```
@@
 
-ggsave("Writing/figures/g_illustration_homogeneous.pdf", g_illustration_homogeneous, height = 4.5, width = 6.5)
+ggsave("Writing/figures/g_illustration_homogeneous.png", g_illustration_homogeneous, height = 4.5, width = 6.5, dpi = 400)
 ```
@@
 
-ggsave("Writing/figures/g_illustration_homogeneous_with_trade.pdf", g_illustration_homogeneous_with_trade, height = 5, width = 6.5)
+ggsave("Writing/figures/g_illustration_homogeneous_with_trade.png", g_illustration_homogeneous_with_trade, height = 5, width = 6.5, dpi = 400)
 ```
@@
 
-ggsave("Writing/figures/g_illustration_het.pdf", g_illustration_het, height = 4.5, width = 6.5)
+ggsave("Writing/figures/g_illustration_het.png", g_illustration_het, height = 4.5, width = 6.5, dpi = 400)
 ```

### 2024-11-13 Writing/manuscript_typst.qmd
tex version added

--- 2024-08-14 Writing/manuscript.Rmd
@@
 ---
-title: Implications of Measurement Errors in Water Use Estimates for Water Management
+title: "Implications of Measurement Errors in Water Use Estimates for Water Management"
 author:
-  - Taro Mieno^[Department of Agricultural Economics, University of Nebraska Lincoln, tmieno2@unl.edu]
-  - Timothy Foster^[Department of WWW, University of Manchester, timothy.foster@manchester.ac.uk]
-  - Nicholas Brozovic^[Department of Agricultural Economics, University of Nebraska Lincoln, nbrozovic@nebraska.edu]
-abstract: |
-  abstract here
-acknowledgments: |
-  Funding for the research in this manuscript was provided by 
+  - name: "Taro Mieno^[University of Nebraska-Lincoln, Email: tmieno2@unl.edu]"
+    orcid: 0000-0003-1689-0557
+  - name: Timothy Foster^[University of Manchester]
+    orcid: 0000-0003-1689-0557
+  - name: Nicholas Brozovic^[University of Nebraska-Lincoln]
+    orcid: 0000-0003-1689-0557
+format:
+  pdf:
+    toc: false
+    keep-tex: true
+  html:
+    embed-resources: true
+  typst:
+    toc: false
+    keep-typ: true
+    section-numbering: 1.1.a
+    columns: 1
+    fig-format: png
+  docx:
+    toc: false
 bibliography: DRA.bib
-output:
-  bookdown::pdf_document2:
-    extra_dependencies: ["float"]
-    citation_package: natbib
-    keep_tex: true
-    toc: false
-    includes:
-      in_header: "preamble.tex"
+bibliographystyle: apa
 ---
@@
 #--- packages ---#
+library(here)
 library(data.table)
-library(tidyverse)
+library(dplyr)
 library(stringr)
-library(sf)
-library(here)
-library(tmap)
-library(modelsummary)
-library(patchwork)
-library(kableExtra)
 
@@
 
-\newpage
-
 # Main
@@
 ## Background
+
++ Use of satellite imagery in water management in general
+  + water theft detection in Australia (Nature Water, Adam Loch)
 
@@
 
-  + shed lights on unintentional consequences of using estiamtes rather than actual measurements
+  + shed lights on unintentional consequences of using estimates rather than actual measurements
 
@@
 
-No clear policy design suggestions on how to use water use estiamtes with measurement errors.
+No clear policy design suggestions on how to use water use estimates with measurement errors.
 
@@
 
-Figure \@ref(fig:profit-quota-water-het) below compares profit from agricultural production as a function of actual water use between water and proxy quota across three different production heterogeneity levels and the size of the measurement errors.
-When there is no heterogeneity in farmers' production function, water quota is the most cost effective way to achieve a water use reduction goal (highest profit achievable for a given level of actual water use).
-Under this circumstance, proxy quota with unbiased measurement errors achieves worse than water quota due to asymmetry in downside and upside risk of water use.
-However, as production heterogeneity increases, water quota loses its comparative advantage over proxy quota.
-It can be shown that water quota always outperforms proxy quota on average irrespective of the degere of production heterogeneity when measurement error is independent and production function is concave (show proof in appendix).
-Not surprisingly, profit losses of using proxy quota increase as measurement error size increases.
-Profit loss of using proxy-based quota tends to become greater as the toal realized water use becomes smaller.
+@fig-profit-quota-water-het illustrates the profit from agricultural production as a function of actual water use, comparing water quotas and proxy quotas across three levels of production heterogeneity and varying sizes of measurement errors.
+When there is no production heterogeneity among farmers, the water quota is the most cost-effective mechanism to achieve a targeted reduction in water use (yielding the highest profit for a given level of actual water use).
+In this scenario, the proxy quota with unbiased measurement errors performs worse than the water quota due to the asymmetry in downside and upside risk of water use.
+However, as production heterogeneity increases, the comparative advantage of water quotas over proxy quotas diminishes.
 
-```{r profit-quota-water-het, fig.cap = "The impacts of an increase in the degree of measurement error on profit"}
-knitr::include_graphics("figures/g_profit_quota_comp_stat.pdf")
+It is demonstrated (proof in Appendix) that water quotas consistently outperform proxy quotas on average, regardless of production heterogeneity, when measurement errors are independent and the production function is concave.
+As expected, the profit losses associated with proxy quotas increase as the size of measurement errors grows.
+Furthermore, the profit loss from using proxy-based quotas tends to become more pronounced as total realized water use decreases.
+
+```{r}
+#| label: fig-profit-quota-water-het
+#| fig-cap: "The impacts of an increase in the degree of measurement error on profit"
+knitr::include_graphics("figures/g_profit_quota_comp_stat.png")
 ```
+
+@grafton2018paradox
 
@@
 We now look at simple two-farm examles to build intuition behind the profit loss due to the use of proxy quota in place of water quota.
-Figure \@ref(fig:illust-homegeneous) presents a case with two homegeneous farmers under water and proxy quota.
+@fig-illust-homegeneous presents a case with two homegeneous farmers under water and proxy quota.
 The red dotted lines indicate the effective water quota.
@@
 
-```{r illust-homegeneous, fig.cap = "Illustration of profit loss due to the use of proxy for quota-based regulation: a case of homegeneous producers"}
+```{r}
+#| label: fig-illust-homegeneous
+#| fig-cap: "Illustration of profit loss due to the use of proxy for quota-based regulation: a case of homegeneous producers"
 #| warning: false
-knitr::include_graphics("figures/g_illustration_homogeneous.pdf")
+knitr::include_graphics("figures/g_illustration_homogeneous.png")
 ```
@@
 This is because uniform quota now acts like heterogeneous quota under homogeneous production function because the same quota is given to farmers with heterogeneous water demand.
-This is illustrated in Figure \@ref(fig:illust-heterogeneous).
+This is illustrated in @fig-illust-heterogeneous.
 In this example, farmer A needs less water than farmer B.
@@
 This is a big contrast to the homogeneous case because water quota is always better than proxy quota in that case.
-Consequently, proxy quota performs relatively better under heterogeneous cases.
+Consequently, proxy quota can perform relatively better under heterogeneous cases.
 On average, the positive and negative effects of measurement errors tend to even out.
@@
 
-```{r illust-heterogeneous, fig.cap = "Illustration of profit loss due to the use of proxy for quota-based regulation: a case of heterogeneous producers"}
+```{r}
+#| label: fig-illust-heterogeneous
+#| fig-cap: "Illustration of profit loss due to the use of proxy for quota-based regulation: a case of heterogeneous producers" 
 #| warning: false
 
-knitr::include_graphics("figures/g_illustration_het.pdf")
+knitr::include_graphics("figures/g_illustration_het.png")
 ```
@@
 Allowing quota to be traded among farmers can dramatically change the relative performance of the water- and quota-based regulation.
-Figure \@ref(fig:trading-profit) presents profit for water-based quota, proxy-based quota, water-based quota trading, and proxy-based quota trading regulation systems.
+@fig-trading-profit presents profit for water-based quota, proxy-based quota, water-based quota trading, and proxy-based quota trading regulation systems.
 As shown in the figure, the disadvantage of using proxy almost disappears when trading of quota is allowed.
@@
 
-```{r trading-profit, fig.cap = "Comparison of profit from agricultural production between the water and quota systems when quota trading is allowed"}
+```{r}
+#| label: fig-trading-profit
+#| fig-cap: "Comparison of profit from agricultural production between the water and quota systems when quota trading is allowed"
 #| echo: false
-knitr::include_graphics("figures/g_trade_effect_profit.pdf")
+knitr::include_graphics("figures/g_trade_effect_profit.png")
 ```
@@
 
-Figure \@ref(fig:trading-profit-illustration) illustrates the impact of allowing for trading proxy quota using the case of two homogeneous farmers illustrated in Figure \@ref(fig:illust-homegeneous).
+@fig-trading-profit-illustration illustrates the impact of allowing for trading proxy quota using the case of two homogeneous farmers illustrated in @fig-illust-homegeneous.
 In this illustration, the same water quota of 7 is allocated for both farmers under the water-based systems.
@@
 
-```{r trading-profit-illustration, fig.cap = "Illustration of the benefits of trading quota"}
+```{r}
+#| label: fig-trading-profit-illustration
+#| fig-cap: "Illustration of the benefits of trading quota"
 #| echo: false
-knitr::include_graphics("figures/g_illustration_homogeneous_with_trade.pdf")
+knitr::include_graphics("figures/g_illustration_homogeneous_with_trade.png")
 ```
@@
 for a mathematical proof).
-However, it is worth emphasizing that the inefficiency caused by the use of proxy is likely to be minimal as shown in Figure \@ref(fig:trading-profit).
-This point is well-illustrated in Figure \@ref(fig:trading-profit-illustration), where total profit per acre is `r profit_after_trade_water` and `r profit_after_trade_proxy` under the water-quota and proxy-quota trading system, respsectively.
+However, it is worth emphasizing that the inefficiency caused by the use of proxy is likely to be minimal as shown in @fig-trading-profit.
+This point is well-illustrated in @fig-trading-profit-illustration, where total profit per acre is `r profit_after_trade_water` and `r profit_after_trade_proxy` under the water-quota and proxy-quota trading system, respsectively.
 
-Figure \@ref(fig:trading-profit) presents the simualtion results of proxy-quota and water-quota trading systems added to Figure \@ref(fig:profit-quota-water-het).
+@fig-trading-profit presents the simualtion results of proxy-quota and water-quota trading systems added to @fig-profit-quota-water-het.
 As you can see at all levels of production heterogeneity levels and the degres of measurement errors, proxy-quota and water-quota trading systems perform almost identical at all levels of realized water use (water-quota trading is always slightly better than proxy-quota trading as explained earlier).
@@
 
-Figure \@ref(fig:distributional-equity) presents the cumulative probability of the ratio of profit under quota-based relative to water-based system for quota (red) and permit trading (blue).
-Ratio of less than 1 indicates making less profit under the quota-based system compared to the water-based system.
-If farmers make just as much profir under proxy-based regulation compared to water-based regulation, then the cumulative probability line would be a vertical line at 1.
+@fig-distributional-equity presents the cumulative probability of the ratio of profit under the proxy-based relative to water-based system for quota (red) and permit trading (blue).
+Ratio of less than 1 indicates making less profit under the proxy-based system compared to the water-based system.
+If farmers make just as much profit under proxy-based regulation compared to water-based regulation, then the cumulative probability line would be a vertical line at 1.
 For example, under the high degree of measurement error and medium heterogenenity scenario, some farmers would make about the half of what they would make under the water quota system.
@@
 
-```{r distributional-equity, fig.cap = "Distribution of profit under various regulation systems"}
-knitr::include_graphics("figures/g_profit_ratio.pdf")
+```{r}
+#| label: fig-distributional-equity 
+#| fig-cap: "Distribution of profit under various regulation systems"
+knitr::include_graphics("figures/g_profit_ratio.png")
 ```
@@
 Under the high-heterogeneity set, the variance of $w^*$ becomes even greater.
-The distribution of $w^*$ for each of the sets is presented in Figure \@ref(fig:dist-opt-w).
+The distribution of $w^*$ for each of the sets is presented in @fig-dist-opt-w.
 
@@
 For all the sets, $E[\eta] = 1$ (or equivalently $E[\mu] = 0$), meaning that water use estimation is ubiased.
-A sample of the empirical (realized) distribution of $\eta$ for each of the sets is presented in Figure \@ref(fig:dist-eta).
+A sample of the empirical (realized) distribution of $\eta$ for each of the sets is presented in @fig-dist-eta.
 
@@
 
-\clearpage
-
 # (APPENDIX) Appendix {-}
@@
 
-```{r dist-opt-w, fig.cap = "Distribution of optimal water use under no water use constraints", fig.height = 5}
-knitr::include_graphics("figures/g_opt_w_dist.pdf")
+```{r}
+#| label: fig-dist-opt-w
+#| fig-cap: "Distribution of optimal water use under no water use constraints"
+knitr::include_graphics("figures/g_opt_w_dist.png")
 ```
@@
 
-```{r dist-eta, fig.cap = "Distribution of water-proxy conversion factor", fig.height = 5}
-# knitr::include_graphics("figures/g_eta_dist.pdf")
+```{r}
+#| label: fig-dist-eta
+#| fig-cap: "Distribution of water-proxy conversion factor" 
+# knitr::include_graphics("figures/g_eta_dist.png")
 ```
-
-\clearpage

### 2024-11-13 Writing/manuscript_typst.tex
tex version added

--- 2024-08-19 Writing/manuscript.tex
@@
 \PassOptionsToPackage{hyphens}{url}
+\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
 %
 \documentclass[
-]{article}
+  letterpaper,
+  DIV=11,
+  numbers=noendperiod]{scrartcl}
+
 \usepackage{amsmath,amssymb}
@@
 \else % if luatex or xetex
-  \usepackage{unicode-math} % this also loads fontspec
+  \usepackage{unicode-math}
   \defaultfontfeatures{Scale=MatchLowercase}
@@
 \usepackage{xcolor}
-\usepackage[margin=1in]{geometry}
-\usepackage{longtable,booktabs,array}
+\setlength{\emergencystretch}{3em} % prevent overfull lines
+\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
+% Make \paragraph and \subparagraph free-standing
+\makeatletter
+\ifx\paragraph\undefined\else
+  \let\oldparagraph\paragraph
+  \renewcommand{\paragraph}{
+    \@ifstar
+      \xxxParagraphStar
+      \xxxParagraphNoStar
+  }
+  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
+  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
+\fi
+\ifx\subparagraph\undefined\else
+  \let\oldsubparagraph\subparagraph
+  \renewcommand{\subparagraph}{
+    \@ifstar
+      \xxxSubParagraphStar
+      \xxxSubParagraphNoStar
+  }
+  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
+  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
+\fi
+\makeatother
+
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
 \usepackage{calc} % for calculating minipage widths
@@
 \makeatletter
-\newsavebox\pandoc@box
-\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
-  \sbox\pandoc@box{#1}%
-  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
-  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
-  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
-  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
-  \else\usebox{\pandoc@box}%
-  \fi%
-}
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
+\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
+\makeatother
+% Scale images if necessary, so that they will not overflow the page
+% margins by default, and it is still possible to overwrite the defaults
+% using explicit options in \includegraphics[width, height, ...]{}
+\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
 % Set default figure placement to htbp
+\makeatletter
 \def\fps@figure{htbp}
 \makeatother
-\setlength{\emergencystretch}{3em} % prevent overfull lines
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{5}
-\usepackage{lineno}
-% \linenumbers
-\usepackage{float}
-\usepackage[]{natbib}
-\bibliographystyle{plainnat}
+% definitions for citeproc citations
+\NewDocumentCommand\citeproctext{}{}
+\NewDocumentCommand\citeproc{mm}{%
+  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
+\makeatletter
+ % allow citations to break across lines
+ \let\@cite@ofmt\@firstofone
+ % avoid brackets around text for \cite:
+ \def\@biblabel#1{}
+ \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
+\makeatother
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
+ {\begin{list}{}{%
+  \setlength{\itemindent}{0pt}
+  \setlength{\leftmargin}{0pt}
+  \setlength{\parsep}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1
+   \setlength{\leftmargin}{\cslhangindent}
+   \setlength{\itemindent}{-1\cslhangindent}
+  \fi
+  % set entry spacing
+  \setlength{\itemsep}{#2\baselineskip}}}
+ {\end{list}}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
+
+\KOMAoption{captions}{tableheading}
+\makeatletter
+\@ifpackageloaded{caption}{}{\usepackage{caption}}
+\AtBeginDocument{%
+\ifdefined\contentsname
+  \renewcommand*\contentsname{Table of contents}
+\else
+  \newcommand\contentsname{Table of contents}
+\fi
+\ifdefined\listfigurename
+  \renewcommand*\listfigurename{List of Figures}
+\else
+  \newcommand\listfigurename{List of Figures}
+\fi
+\ifdefined\listtablename
+  \renewcommand*\listtablename{List of Tables}
+\else
+  \newcommand\listtablename{List of Tables}
+\fi
+\ifdefined\figurename
+  \renewcommand*\figurename{Figure}
+\else
+  \newcommand\figurename{Figure}
+\fi
+\ifdefined\tablename
+  \renewcommand*\tablename{Table}
+\else
+  \newcommand\tablename{Table}
+\fi
+}
+\@ifpackageloaded{float}{}{\usepackage{float}}
+\floatstyle{ruled}
+\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
+\floatname{codelisting}{Listing}
+\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
+\makeatother
+\makeatletter
+\makeatother
+\makeatletter
+\@ifpackageloaded{caption}{}{\usepackage{caption}}
+\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
+\makeatother
+
+\ifLuaTeX
+  \usepackage{selnolig}  % disable illegal ligatures
+\fi
 \usepackage{bookmark}
+
 \IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same}
+\urlstyle{same} % disable monospaced font for URLs
 \hypersetup{
@@
   pdfauthor={Taro Mieno; Timothy Foster; Nicholas Brozovic},
-  hidelinks,
+  colorlinks=true,
+  linkcolor={blue},
+  filecolor={Maroon},
+  citecolor={Blue},
+  urlcolor={Blue},
   pdfcreator={LaTeX via pandoc}}
 
-\title{Implications of Measurement Errors in Water Use Estimates for Water Management}
-\author{Taro Mieno\footnote{Department of Agricultural Economics, University of Nebraska Lincoln, \href{mailto:tmieno2@unl.edu}{\nolinkurl{tmieno2@unl.edu}}} \and Timothy Foster\footnote{Department of WWW, University of Manchester, \href{mailto:timothy.foster@manchester.ac.uk}{\nolinkurl{timothy.foster@manchester.ac.uk}}} \and Nicholas Brozovic\footnote{Department of Agricultural Economics, University of Nebraska Lincoln, \href{mailto:nbrozovic@nebraska.edu}{\nolinkurl{nbrozovic@nebraska.edu}}}}
+\title{Implications of Measurement Errors in Water Use Estimates for
+Water Management}
+\author{Taro Mieno\footnote{University of Nebraska-Lincoln, Email:
+  tmieno2@unl.edu} \and Timothy Foster\footnote{University of Manchester} \and Nicholas
+Brozovic\footnote{University of Nebraska-Lincoln}}
 \date{}
@@
 \maketitle
-\begin{abstract}
-abstract here
-\end{abstract}
-
-\newpage
 
@@
 \item
+  Use of satellite imagery in water management in general
+
+  \begin{itemize}
+  \tightlist
+  \item
+    water theft detection in Australia (Nature Water, Adam Loch)
+  \end{itemize}
+\item
   intensity estimation accuracy
 \item
-  (estimated) intensity-based vs (estimated) area-based (Southern Europe History)
+  (estimated) intensity-based vs (estimated) area-based (Southern Europe
+  History)
 \item
-  (estimated) intensity-based vs (true) intensity-based {[}We work on this{]}
+  (estimated) intensity-based vs (true) intensity-based {[}We work on
+  this{]}
 \item
-  Lack of measurement. Use of water use estimates for water management (current and future). Emergence of Open ET as a substitute.
+  Lack of measurement. Use of water use estimates for water management
+  (current and future). Emergence of Open ET as a substitute.
 \end{itemize}
@@
 \item
-  start a discussion about the implications of the use of mis-measured water use for water use regulation.
+  start a discussion about the implications of the use of mis-measured
+  water use for water use regulation.
 \item
-  shed lights on unintentional consequences of using estiamtes rather than actual measurements
+  shed lights on unintentional consequences of using estimates rather
+  than actual measurements
 \end{itemize}
@@
 
-No clear policy design suggestions on how to use water use estiamtes with measurement errors.
+No clear policy design suggestions on how to use water use estimates
+with measurement errors.
 
@@
 
-\subsection{Profit under water and proxy quota}\label{profit-under-water-and-proxy-quota}
+\subsection{Profit under water and proxy
+quota}\label{profit-under-water-and-proxy-quota}
 
-Figure \ref{fig:profit-quota-water-het} below compares profit from agricultural production as a function of actual water use between water and proxy quota across three different production heterogeneity levels and the size of the measurement errors.
-When there is no heterogeneity in farmers' production function, water quota is the most cost effective way to achieve a water use reduction goal (highest profit achievable for a given level of actual water use).
-Under this circumstance, proxy quota with unbiased measurement errors achieves worse than water quota due to asymmetry in downside and upside risk of water use.
-However, as production heterogeneity increases, water quota loses its comparative advantage over proxy quota.
-It can be shown that water quota always outperforms proxy quota on average irrespective of the degere of production heterogeneity when measurement error is independent and production function is concave (show proof in appendix).
-Not surprisingly, profit losses of using proxy quota increase as measurement error size increases.
-Profit loss of using proxy-based quota tends to become greater as the toal realized water use becomes smaller.
+Figure~\ref{fig-profit-quota-water-het} illustrates the profit from
+agricultural production as a function of actual water use, comparing
+water quotas and proxy quotas across three levels of production
+heterogeneity and varying sizes of measurement errors. When there is no
+production heterogeneity among farmers, the water quota is the most
+cost-effective mechanism to achieve a targeted reduction in water use
+(yielding the highest profit for a given level of actual water use). In
+this scenario, the proxy quota with unbiased measurement errors performs
+worse than the water quota due to the asymmetry in downside and upside
+risk of water use. However, as production heterogeneity increases, the
+comparative advantage of water quotas over proxy quotas diminishes.
+
+It is demonstrated (proof in Appendix) that water quotas consistently
+outperform proxy quotas on average, regardless of production
+heterogeneity, when measurement errors are independent and the
+production function is concave. As expected, the profit losses
+associated with proxy quotas increase as the size of measurement errors
+grows. Furthermore, the profit loss from using proxy-based quotas tends
+to become more pronounced as total realized water use decreases.
 
@@
 
-{\centering \includegraphics{figures/g_profit_quota_comp_stat}
+\centering{
+
+\includegraphics[width=1.6in,height=\textheight]{figures/g_profit_quota_comp_stat.png}
 
@@
 
-\caption{The impacts of an increase in the degree of measurement error on profit}\label{fig:profit-quota-water-het}
-\end{figure}
+\caption{\label{fig-profit-quota-water-het}The impacts of an increase in
+the degree of measurement error on profit}
 
-We now look at simple two-farm examles to build intuition behind the profit loss due to the use of proxy quota in place of water quota.
-Figure \ref{fig:illust-homegeneous} presents a case with two homegeneous farmers under water and proxy quota.
-The red dotted lines indicate the effective water quota.
-Under the water quota system, both farmers receive 7 inches of water quota.
-Since the unconstrained profit maximizing water use is 10.94 inches, both farmers use up all the allocated quota and use 10 inches of water.
-Under the proxy quota system, they are allocated the same amount of proxy quota.
-However, measurement error in proxy quota resulted in effective water quota of 4 and 10 inches for farmer A and B, respectively.
-Both farmers use their allocated amout of water.
-Under both proxy and water quota systems, the total water use is 14 inches.
-Farmer B makes 29.9 less under the water quota system compared to the proxy quota system.
-However, Farmer A makes 128.9 more under the water quota system compared to the proxy quota system.
-This comes from an important nature of crop production with respsect to water: declining marginal impact of water on crop yield.
-As can be seen in the profit-water relationship, removing an inch of water from 6 inches has much larger negative impact compared to revmoing an inch of water from 10 inches.
+\end{figure}%
+
+Grafton et al. (2018)
+
+We now look at simple two-farm examles to build intuition behind the
+profit loss due to the use of proxy quota in place of water quota.
+Figure~\ref{fig-illust-homegeneous} presents a case with two homegeneous
+farmers under water and proxy quota. The red dotted lines indicate the
+effective water quota. Under the water quota system, both farmers
+receive 7 inches of water quota. Since the unconstrained profit
+maximizing water use is 10.94 inches, both farmers use up all the
+allocated quota and use 10 inches of water. Under the proxy quota
+system, they are allocated the same amount of proxy quota. However,
+measurement error in proxy quota resulted in effective water quota of 4
+and 10 inches for farmer A and B, respectively. Both farmers use their
+allocated amout of water. Under both proxy and water quota systems, the
+total water use is 14 inches. Farmer B makes 29.9 less under the water
+quota system compared to the proxy quota system. However, Farmer A makes
+128.9 more under the water quota system compared to the proxy quota
+system. This comes from an important nature of crop production with
+respsect to water: declining marginal impact of water on crop yield. As
+can be seen in the profit-water relationship, removing an inch of water
+from 6 inches has much larger negative impact compared to revmoing an
+inch of water from 10 inches.
 
@@
 
-{\centering \includegraphics{figures/g_illustration_homogeneous}
+\centering{
+
+\includegraphics[width=1.73in,height=\textheight]{figures/g_illustration_homogeneous.png}
 
@@
 
-\caption{Illustration of profit loss due to the use of proxy for quota-based regulation: a case of homegeneous producers}\label{fig:illust-homegeneous}
-\end{figure}
+\caption{\label{fig-illust-homegeneous}Illustration of profit loss due
+to the use of proxy for quota-based regulation: a case of homegeneous
+producers}
 
-However, as the heterogeneity of farmers increases, comparative advantage of water quota over proxy quota diminishes.
-While the performance of both systems declines as the level of heterogeneity increases, water quota is affected more so than the proxy quota system.
-This is because uniform quota now acts like heterogeneous quota under homogeneous production function because the same quota is given to farmers with heterogeneous water demand.
-This is illustrated in Figure \ref{fig:illust-heterogeneous}.
-In this example, farmer A needs less water than farmer B.
-Water and proxy quota allocated to the farmers are exactly the same as the previous case.
-In this example, errors in proxy happened to realize so that more effective water quota is given to farmer B than farmer A.
-Consequently, proxy quota produces a higher total profit than water quota.
-Of course, if error happened to go the opposite way, then the performance of proxy quota relative to water quota is even worse compared to the homogeneous case.
-This is a big contrast to the homogeneous case because water quota is always better than proxy quota in that case.
-Consequently, proxy quota performs relatively better under heterogeneous cases.
-On average, the positive and negative effects of measurement errors tend to even out.
-However, proxy quota is never better than water quota \textbf{on average} (see Appendix \ldots{} for mathematical proof).
+\end{figure}%
+
+However, as the heterogeneity of farmers increases, comparative
+advantage of water quota over proxy quota diminishes. While the
+performance of both systems declines as the level of heterogeneity
+increases, water quota is affected more so than the proxy quota system.
+This is because uniform quota now acts like heterogeneous quota under
+homogeneous production function because the same quota is given to
+farmers with heterogeneous water demand. This is illustrated in
+Figure~\ref{fig-illust-heterogeneous}. In this example, farmer A needs
+less water than farmer B. Water and proxy quota allocated to the farmers
+are exactly the same as the previous case. In this example, errors in
+proxy happened to realize so that more effective water quota is given to
+farmer B than farmer A. Consequently, proxy quota produces a higher
+total profit than water quota. Of course, if error happened to go the
+opposite way, then the performance of proxy quota relative to water
+quota is even worse compared to the homogeneous case. This is a big
+contrast to the homogeneous case because water quota is always better
+than proxy quota in that case. Consequently, proxy quota can perform
+relatively better under heterogeneous cases. On average, the positive
+and negative effects of measurement errors tend to even out. However,
+proxy quota is never better than water quota \textbf{on average} (see
+Appendix \ldots{} for mathematical proof).
 
@@
 
-{\centering \includegraphics{figures/g_illustration_het}
+\centering{
+
+\includegraphics[width=1.73in,height=\textheight]{figures/g_illustration_het.png}
 
@@
 
-\caption{Illustration of profit loss due to the use of proxy for quota-based regulation: a case of heterogeneous producers}\label{fig:illust-heterogeneous}
-\end{figure}
+\caption{\label{fig-illust-heterogeneous}Illustration of profit loss due
+to the use of proxy for quota-based regulation: a case of heterogeneous
+producers}
+
+\end{figure}%
 
@@
 
-\subsection{The effect of allowing trading quota}\label{the-effect-of-allowing-trading-quota}
+\subsection{The effect of allowing trading
+quota}\label{the-effect-of-allowing-trading-quota}
 
-Allowing quota to be traded among farmers can dramatically change the relative performance of the water- and quota-based regulation.
-Figure \ref{fig:trading-profit} presents profit for water-based quota, proxy-based quota, water-based quota trading, and proxy-based quota trading regulation systems.
-As shown in the figure, the disadvantage of using proxy almost disappears when trading of quota is allowed.
-This is because the inefficiencies in quota allocations are resolved through trading of quota whether it is water or proxy quota.
+Allowing quota to be traded among farmers can dramatically change the
+relative performance of the water- and quota-based regulation.
+Figure~\ref{fig-trading-profit} presents profit for water-based quota,
+proxy-based quota, water-based quota trading, and proxy-based quota
+trading regulation systems. As shown in the figure, the disadvantage of
+using proxy almost disappears when trading of quota is allowed. This is
+because the inefficiencies in quota allocations are resolved through
+trading of quota whether it is water or proxy quota.
 
@@
 
-{\centering \includegraphics{figures/g_trade_effect_profit}
+\centering{
+
+\includegraphics[width=1.6in,height=\textheight]{figures/g_trade_effect_profit.png}
 
@@
 
-\caption{Comparison of profit from agricultural production between the water and quota systems when quota trading is allowed}\label{fig:trading-profit}
-\end{figure}
+\caption{\label{fig-trading-profit}Comparison of profit from
+agricultural production between the water and quota systems when quota
+trading is allowed}
 
-Figure \ref{fig:trading-profit-illustration} illustrates the impact of allowing for trading proxy quota using the case of two homogeneous farmers illustrated in Figure \ref{fig:illust-homegeneous}.
-In this illustration, the same water quota of 7 is allocated for both farmers under the water-based systems.
-No water quota trading would happen as the marginal profit of water is already equated at water use of 7.
-Under the proxy-base quota system, proxy quota of 7 is allocated for both farmers, but the effective water quota for farmers A and B are 4 and 7, respectively.
-Once trading of proxy quota is alllowed, farmer A would buy 1.85 proxy quota from farmer B.
-At these production levels, the marginal profit of quota (not water) are equated acros the farmers and no further transfer between them would happen.
-Trading of proxy quota improves the overall profit to 920.08 \$/acre from 831.94 \$/acre.
+\end{figure}%
+
+Figure~\ref{fig-trading-profit-illustration} illustrates the impact of
+allowing for trading proxy quota using the case of two homogeneous
+farmers illustrated in Figure~\ref{fig-illust-homegeneous}. In this
+illustration, the same water quota of 7 is allocated for both farmers
+under the water-based systems. No water quota trading would happen as
+the marginal profit of water is already equated at water use of 7. Under
+the proxy-base quota system, proxy quota of 7 is allocated for both
+farmers, but the effective water quota for farmers A and B are 4 and 7,
+respectively. Once trading of proxy quota is alllowed, farmer A would
+buy 1.85 proxy quota from farmer B. At these production levels, the
+marginal profit of quota (not water) are equated acros the farmers and
+no further transfer between them would happen. Trading of proxy quota
+improves the overall profit to 920.08 \$/acre from 831.94 \$/acre.
 
@@
 
-{\centering \includegraphics{figures/g_illustration_homogeneous_with_trade}
+\centering{
+
+\includegraphics[width=1.73in,height=\textheight]{figures/g_illustration_homogeneous_with_trade.png}
 
@@
 
-\caption{Illustration of the benefits of trading quota}\label{fig:trading-profit-illustration}
-\end{figure}
+\caption{\label{fig-trading-profit-illustration}Illustration of the
+benefits of trading quota}
 
-While water-quota and proxy-quota trading perform about the same, water-quota always leads to a higher total profit for a given level of realized water use.
-In other words, to achieve a certain water use goal, water-quota trading is always to more cost-effective than proxy-quota trading.
-Under water-quota trading, the margial profit of water is equalized across the farmers, which is a necessary condition to achieve the highest profit for a given level of total water use.
-Under proxy-quota trading, the marginal profit of proxy is equalized across the farmers, not the margial profit of water (See Appendix \ldots{} for a mathematical proof).
-However, it is worth emphasizing that the inefficiency caused by the use of proxy is likely to be minimal as shown in Figure \ref{fig:trading-profit}.
-This point is well-illustrated in Figure \ref{fig:trading-profit-illustration}, where total profit per acre is 930.91 and 920.08 under the water-quota and proxy-quota trading system, respsectively.
+\end{figure}%
 
-Figure \ref{fig:trading-profit} presents the simualtion results of proxy-quota and water-quota trading systems added to Figure \ref{fig:profit-quota-water-het}.
-As you can see at all levels of production heterogeneity levels and the degres of measurement errors, proxy-quota and water-quota trading systems perform almost identical at all levels of realized water use (water-quota trading is always slightly better than proxy-quota trading as explained earlier).
-Not surprisingly, the benefit of allowing for trading is greater when the degree of measurement errors is larger.
+While water-quota and proxy-quota trading perform about the same,
+water-quota always leads to a higher total profit for a given level of
+realized water use. In other words, to achieve a certain water use goal,
+water-quota trading is always to more cost-effective than proxy-quota
+trading. Under water-quota trading, the margial profit of water is
+equalized across the farmers, which is a necessary condition to achieve
+the highest profit for a given level of total water use. Under
+proxy-quota trading, the marginal profit of proxy is equalized across
+the farmers, not the margial profit of water (See Appendix \ldots{} for
+a mathematical proof). However, it is worth emphasizing that the
+inefficiency caused by the use of proxy is likely to be minimal as shown
+in Figure~\ref{fig-trading-profit}. This point is well-illustrated in
+Figure~\ref{fig-trading-profit-illustration}, where total profit per
+acre is 930.91 and 920.08 under the water-quota and proxy-quota trading
+system, respsectively.
 
-\subsection{Use of proxy can exercebate distributional inequity}\label{use-of-proxy-can-exercebate-distributional-inequity}
+Figure~\ref{fig-trading-profit} presents the simualtion results of
+proxy-quota and water-quota trading systems added to
+Figure~\ref{fig-profit-quota-water-het}. As you can see at all levels of
+production heterogeneity levels and the degres of measurement errors,
+proxy-quota and water-quota trading systems perform almost identical at
+all levels of realized water use (water-quota trading is always slightly
+better than proxy-quota trading as explained earlier). Not surprisingly,
+the benefit of allowing for trading is greater when the degree of
+measurement errors is larger.
 
-Figure \ref{fig:distributional-equity} presents the cumulative probability of the ratio of profit under quota-based relative to water-based system for quota (red) and permit trading (blue).
-Ratio of less than 1 indicates making less profit under the quota-based system compared to the water-based system.
-If farmers make just as much profir under proxy-based regulation compared to water-based regulation, then the cumulative probability line would be a vertical line at 1.
-For example, under the high degree of measurement error and medium heterogenenity scenario, some farmers would make about the half of what they would make under the water quota system.
-At the lower end of the distribution are farmers who would be constrained severely by water quota, but whose water use estiamtes are much higher than their actual water use.
-At the higher end of the distribution are farmers who would be constrained by water quota, but whose water use estiamtes are much lower than their actual water use.
-Famres who suffer significantly under the quota system can develop strong dissatisfaction of the quota-based regulation system, which in turn may lead to installing water meter themselves.
-If they discover the over-estimation of their water use, they may appeal to legal actions against the administrator for their unfair treatment.
-Allowind quota trading greatly diminishes the distributional inequality, though not completely.
-This is because unfortunate farmers who suffered from over-estimation of their water use can now at least purchase proxy quota to increase their production level.
+\subsection{Use of proxy can exercebate distributional
+inequity}\label{use-of-proxy-can-exercebate-distributional-inequity}
+
+Figure~\ref{fig-distributional-equity} presents the cumulative
+probability of the ratio of profit under the proxy-based relative to
+water-based system for quota (red) and permit trading (blue). Ratio of
+less than 1 indicates making less profit under the proxy-based system
+compared to the water-based system. If farmers make just as much profit
+under proxy-based regulation compared to water-based regulation, then
+the cumulative probability line would be a vertical line at 1. For
+example, under the high degree of measurement error and medium
+heterogenenity scenario, some farmers would make about the half of what
+they would make under the water quota system. At the lower end of the
+distribution are farmers who would be constrained severely by water
+quota, but whose water use estiamtes are much higher than their actual
+water use. At the higher end of the distribution are farmers who would
+be constrained by water quota, but whose water use estiamtes are much
+lower than their actual water use. Famres who suffer significantly under
+the quota system can develop strong dissatisfaction of the quota-based
+regulation system, which in turn may lead to installing water meter
+themselves. If they discover the over-estimation of their water use,
+they may appeal to legal actions against the administrator for their
+unfair treatment. Allowind quota trading greatly diminishes the
+distributional inequality, though not completely. This is because
+unfortunate farmers who suffered from over-estimation of their water use
+can now at least purchase proxy quota to increase their production
+level.
 
@@
 
-{\centering \includegraphics{figures/g_profit_ratio}
+\centering{
+
+\includegraphics[width=1.6in,height=\textheight]{figures/g_profit_ratio.png}
 
@@
 
-\caption{Distribution of profit under various regulation systems}\label{fig:distributional-equity}
-\end{figure}
+\caption{\label{fig-distributional-equity}Distribution of profit under
+various regulation systems}
+
+\end{figure}%
 
@@
 \item
-  Allowing quota trading can be particularly beneficial when proxy is used.
+  Allowing quota trading can be particularly beneficial when proxy is
+  used.
 
@@
   \item
-    Assumptions (farmers have linked their practice and water use estimates, but not water)
+    Assumptions (farmers have linked their practice and water use
+    estimates, but not water)
 
@@
     \item
-      uncertainty in water use estimates lead to under-use of water, harming profit even more
+      uncertainty in water use estimates lead to under-use of water,
+      harming profit even more
     \end{itemize}
@@
 
-This section describes the details of the simulation analysis conducted in this article.
-Our simulation imagines a region with 1000 (denoted as \(N\), hereafter) farmers, where a single water governing body possesses a right to devise groundwater policies.
-Our simulation considers nine scenarios in total: three different levels of production heterogeneity times three different degrees of measurement errors.
-Under each scenario, 1000 rounds of individual simulations are run.
-In each simulation round, measurement errors are drawn randomly for the individual farmers, and then average (across the farmers) water use and profit are calculated at different levels of water or proxy quota levels for four different policies: water-quota, proxy-quota, water-quota trading, proxy-quota trading.
-The summary of the 1000 simulation rounds.
+This section describes the details of the simulation analysis conducted
+in this article. Our simulation imagines a region with 1000 (denoted as
+\(N\), hereafter) farmers, where a single water governing body possesses
+a right to devise groundwater policies. Our simulation considers nine
+scenarios in total: three different levels of production heterogeneity
+times three different degrees of measurement errors. Under each
+scenario, 1000 rounds of individual simulations are run. In each
+simulation round, measurement errors are drawn randomly for the
+individual farmers, and then average (across the farmers) water use and
+profit are calculated at different levels of water or proxy quota levels
+for four different policies: water-quota, proxy-quota, water-quota
+trading, proxy-quota trading. The summary of the 1000 simulation rounds.
 The key components of the simluation analysis are presented below.
 
-\subsection{Crop-water production function}\label{crop-water-production-function}
+\subsection{Crop-water production
+function}\label{crop-water-production-function}
 
-For all faemers \(i \in 1,\dots, N\), the crop-water production function follows the Michelich-Baule functional form presented below(citations).
+For all faemers \(i \in 1,\dots, N\), the crop-water production function
+follows the Michelich-Baule functional form presented below(citations).
 
@@
 
-where \(y\) is corn yield (kg/ha), \(w\) is water use (mm), and \(\phi\), \(\alpha\), and \(\beta\) are model parameters that govern how corn yield responds to water use.
+where \(y\) is corn yield (kg/ha), \(w\) is water use (mm), and
+\(\phi\), \(\alpha\), and \(\beta\) are model parameters that govern how
+corn yield responds to water use.
 
-Given the price of corn (\(P_c\)) and water (\(P_w\)), farmer \(i\) is assumed to maximize profit by solving the following maximization problem when no water quota is placed:
+Given the price of corn (\(P_c\)) and water (\(P_w\)), farmer \(i\) is
+assumed to maximize profit by solving the following maximization problem
+when no water quota is placed:
 
@@
 
-Three different sets of the collections of crop-water production functions are generated that vary in the degree of heterogeneity in unconstrained optimal water use (\(w^*\)).
-Under no-heterogeneity set, farmers share exactly the same profuction function (the same value of \(\phi_i\), \(\alpha_i\), and \(\beta_i\)).
-Unde the medium-heterogeneity set, model parameters vary and so does \(w^*\).
-Under the high-heterogeneity set, the variance of \(w^*\) becomes even greater.
-The distribution of \(w^*\) for each of the sets is presented in Figure \ref{fig:dist-opt-w}.
+Three different sets of the collections of crop-water production
+functions are generated that vary in the degree of heterogeneity in
+unconstrained optimal water use (\(w^*\)). Under no-heterogeneity set,
+farmers share exactly the same profuction function (the same value of
+\(\phi_i\), \(\alpha_i\), and \(\beta_i\)). Unde the
+medium-heterogeneity set, model parameters vary and so does \(w^*\).
+Under the high-heterogeneity set, the variance of \(w^*\) becomes even
+greater. The distribution of \(w^*\) for each of the sets is presented
+in Figure~\ref{fig-dist-opt-w}.
 
-\subsection{Measurement error in water use}\label{measurement-error-in-water-use}
+\subsection{Measurement error in water
+use}\label{measurement-error-in-water-use}
 
-When water use values are not measured and observed, the administrator estimates water use.
-The estimated value of water use is named ``proxy'' and denoted as \(p\).
-Proxy and water are assumed to follow the relationship below for all the farmers (\(i \in 1,\dots, N\)):
+When water use values are not measured and observed, the administrator
+estimates water use. The estimated value of water use is named ``proxy''
+and denoted as \(p\). Proxy and water are assumed to follow the
+relationship below for all the farmers (\(i \in 1,\dots, N\)):
 
@@
 
-where \(\eta_i\) is a scalar greater than 0. Measurement error (denoted as \(\mu\)) can be written as follows:
+where \(\eta_i\) is a scalar greater than 0. Measurement error (denoted
+as \(\mu\)) can be written as follows:
 
@@
 
-While farmers with \(\eta_i > 1\) are unfortunate and their water uses are over-estimated, farmers with \(\eta_i < 1\) are fortunate and their water uses are under-estimated.
+While farmers with \(\eta_i > 1\) are unfortunate and their water uses
+are over-estimated, farmers with \(\eta_i < 1\) are fortunate and their
+water uses are under-estimated.
 
-Three different sets of the distribution of \(\eta\) are considered that vary in the degree of heterogeneity in \(\eta\): low, medium, and high.
-For all the sets, \(E[\eta] = 1\) (or equivalently \(E[\mu] = 0\)), meaning that water use estimation is ubiased.
-A sample of the empirical (realized) distribution of \(\eta\) for each of the sets is presented in Figure \ref{fig:dist-eta}.
+Three different sets of the distribution of \(\eta\) are considered that
+vary in the degree of heterogeneity in \(\eta\): low, medium, and high.
+For all the sets, \(E[\eta] = 1\) (or equivalently \(E[\mu] = 0\)),
+meaning that water use estimation is ubiased. A sample of the empirical
+(realized) distribution of \(\eta\) for each of the sets is presented in
+\textbf{?@fig-dist-eta}.
 
-\subsection{Water use under quota and trading systems}\label{water-use-under-quota-and-trading-systems}
+\subsection{Water use under quota and trading
+systems}\label{water-use-under-quota-and-trading-systems}
 
-Under both water and proxy quota systems without trading, the same amount of quota is allocated to all the farmers.
-(this is realistic with insufficient information available to the administrator).
-For a given water quota of \(\overline{w}\), farmer \(i\)'s water use would be \(min\{w^*, \overline{w}\}\).
-Under the proxy quota system, the same amount of proxy quota (\(\overline{p}\)) is allocated to all the farmers.
-However, the effective limit on water use varies by farmer.
-Given the proxy quota of \(\overline{p}\), the effective water use limit for farmer \(i\) is \(\overline{p} / \eta_i\), and uses \(min\{w^*, \overline{p} / \eta_i\}\).
+Under both water and proxy quota systems without trading, the same
+amount of quota is allocated to all the farmers. (this is realistic with
+insufficient information available to the administrator). For a given
+water quota of \(\overline{w}\), farmer \(i\)'s water use would be
+\(min\{w^*, \overline{w}\}\). Under the proxy quota system, the same
+amount of proxy quota (\(\overline{p}\)) is allocated to all the
+farmers. However, the effective limit on water use varies by farmer.
+Given the proxy quota of \(\overline{p}\), the effective water use limit
+for farmer \(i\) is \(\overline{p} / \eta_i\), and uses
+\(min\{w^*, \overline{p} / \eta_i\}\).
 
-Assumptions:
-+ farmers: has learned the degree of under- or over-estimation of water use compared to actual over the years and has learned how to irrigate up to the water quota
+Assumptions: + farmers: has learned the degree of under- or
+over-estimation of water use compared to actual over the years and has
+learned how to irrigate up to the water quota
 
-Under a water trading system, the same amount of water quota is first allocated to all the farmers just like water quota system.
-However, farmers are now allowed to sell or buy water quota under a water trading system.
-Assuming no transaction cost of trading, water quota will be traded until the marginal profit of water at their respective level of water uses is equated across the farmers.
-Let \(\pi_i(w)\) denote farmer \(i\)'s profit: \(P_c \cdot f_i(w) - P_w \cdot w\).
-Conditional on water quota of \(\overline{w}\), individual water uses for the farmers can be identified by finding a series of water use values (\(w_1, w_2, \dots, w_N\)) that satisfy the following conditions:
+Under a water trading system, the same amount of water quota is first
+allocated to all the farmers just like water quota system. However,
+farmers are now allowed to sell or buy water quota under a water trading
+system. Assuming no transaction cost of trading, water quota will be
+traded until the marginal profit of water at their respective level of
+water uses is equated across the farmers. Let \(\pi_i(w)\) denote farmer
+\(i\)'s profit: \(P_c \cdot f_i(w) - P_w \cdot w\). Conditional on water
+quota of \(\overline{w}\), individual water uses for the farmers can be
+identified by finding a series of water use values
+(\(w_1, w_2, \dots, w_N\)) that satisfy the following conditions:
 
@@
 
-Under a proxy trading system, proxy quota will be traded until the marginal profit of proxy (not water) at their respective level of effective water (or equivalently proxy) uses is equated across the farmers.
-Conditional on proxy quota of \(\overline{p}\), individual proxy use for the farmers can be identified by finding a series of proxy use values (\(p_1, p_2, \dots, p_N\)) that satisfy the following conditions:
+Under a proxy trading system, proxy quota will be traded until the
+marginal profit of proxy (not water) at their respective level of
+effective water (or equivalently proxy) uses is equated across the
+farmers. Conditional on proxy quota of \(\overline{p}\), individual
+proxy use for the farmers can be identified by finding a series of proxy
+use values (\(p_1, p_2, \dots, p_N\)) that satisfy the following
+conditions:
 
@@
 
-\subsection{Data and Code Availability}\label{data-and-code-availability}
+\subsection{Data and Code
+Availability}\label{data-and-code-availability}
 
-The datasets created in this article are all computer-generated using R (citation).
-All the codes and datasets are available at \href{https://github.com/tmieno2/Measurement-Error-Water-Management}{this GitHub repository}.
-Instructions for reproducing all the outputs presented in this article are provided at the bottom of the page.
+The datasets created in this article are all computer-generated using R
+(citation). All the codes and datasets are available at
+\href{https://github.com/tmieno2/Measurement-Error-Water-Management}{this
+GitHub repository}. Instructions for reproducing all the outputs
+presented in this article are provided at the bottom of the page.
 
-\clearpage
+\section*{(APPENDIX) Appendix}\label{appendix-appendix}
+\addcontentsline{toc}{section}{(APPENDIX) Appendix}
 
-\appendix
-
-\subsection{Distribution of optimal water use under no water use constraints}\label{distribution-of-optimal-water-use-under-no-water-use-constraints}
+\subsection{Distribution of optimal water use under no water use
+constraints}\label{distribution-of-optimal-water-use-under-no-water-use-constraints}
 
@@
 
-{\centering \includegraphics{figures/g_opt_w_dist}
+\centering{
+
+\includegraphics[width=1.6in,height=\textheight]{figures/g_opt_w_dist.png}
 
@@
 
-\caption{Distribution of optimal water use under no water use constraints}\label{fig:dist-opt-w}
-\end{figure}
+\caption{\label{fig-dist-opt-w}Distribution of optimal water use under
+no water use constraints}
 
-\subsection{Distribution of water-proxy conversion factor}\label{distribution-of-water-proxy-conversion-factor}
+\end{figure}%
 
-\clearpage
+\subsection*{Distribution of water-proxy conversion
+factor}\label{distribution-of-water-proxy-conversion-factor}
+\addcontentsline{toc}{subsection}{Distribution of water-proxy conversion
+factor}
 
-  \bibliography{DRA.bib}
+\phantomsection\label{refs}
+\begin{CSLReferences}{1}{0}
+\bibitem[\citeproctext]{ref-grafton2018paradox}
+Grafton, R. Q., J. Williams, C. J. Perry, F. Molle, C. Ringler, P.
+Steduto, B. Udall, et al. 2018. {``The Paradox of Irrigation
+Efficiency.''} \emph{Science} 361 (6404): 748--50.
+
+\end{CSLReferences}
 

### 2024-11-13 Writing/manuscript.tex
Updates from Overleaf

@@
 \item
-  shed lights on unintentional consequences of using estiamtes rather than actual measurements
+  shed light on unintentional consequences of using estimates rather than actual measurements.
 \end{itemize}
@@
 
-Figure \ref{fig:profit-quota-water-het} below compares profit from agricultural production as a function of actual water use between water and proxy quota across three different production heterogeneity levels and the size of the measurement errors.
+Figure \ref{fig:profit-quota-water-het} below compares the profit from agricultural production as a function of actual water use between the water and proxy quota at three different levels of production heterogeneity and the size of the measurement errors.
 When there is no heterogeneity in farmers' production function, water quota is the most cost effective way to achieve a water use reduction goal (highest profit achievable for a given level of actual water use).
@@
 However, as production heterogeneity increases, water quota loses its comparative advantage over proxy quota.
-It can be shown that water quota always outperforms proxy quota on average irrespective of the degere of production heterogeneity when measurement error is independent and production function is concave (show proof in appendix).
+It can be shown that water quota always outperforms proxy quota on average irrespective of the degree of production heterogeneity when measurement error is independent and production function is concave (show proof in appendix).
 Not surprisingly, profit losses of using proxy quota increase as measurement error size increases.
@@
 
-We now look at simple two-farm examles to build intuition behind the profit loss due to the use of proxy quota in place of water quota.
-Figure \ref{fig:illust-homegeneous} presents a case with two homegeneous farmers under water and proxy quota.
+We now look at simple two-farm exams to build intuition behind the profit loss due to the use of proxy quota in place of water quota.
+Figure \ref{fig:illust-homegeneous} presents a case with two homogeneous farmers under water and proxy quota.
 The red dotted lines indicate the effective water quota.

### 2024-11-13 Writing/manuscript_typst.qmd
minor edits

@@
 
-We now look at simple two-farm examles to build intuition behind the profit loss due to the use of proxy quota in place of water quota.
-@fig-illust-homegeneous presents a case with two homegeneous farmers under water and proxy quota.
+We now look at simple two-farm examples to build intuition behind the profit loss due to the use of proxy quota in place of water quota.
+@fig-illust-homogeneous presents a case with two homogeneous farmers under water and proxy quota.
 The red dotted lines indicate the effective water quota.
@@
 However, measurement error in proxy quota resulted in effective water quota of 4 and 10 inches for farmer A and B, respectively.
-Both farmers use their allocated amout of water.
+Both farmers use their allocated amount of water.
 Under both proxy and water quota systems, the total water use is 14 inches.
@@
 However, Farmer A makes `r -pi_dif_1` more under the water quota system compared to the proxy quota system.
-This comes from an important nature of crop production with respsect to water: declining marginal impact of water on crop yield.
-As can be seen in the profit-water relationship, removing an inch of water from 6 inches has much larger negative impact compared to revmoing an inch of water from 10 inches.
+This comes from an important nature of crop production with respect to water: declining marginal impact of water on crop yield.
+As can be seen in the profit-water relationship, removing an inch of water from 6 inches has much larger negative impact compared to removing an inch of water from 10 inches.
 
 ```{r}
-#| label: fig-illust-homegeneous
-#| fig-cap: "Illustration of profit loss due to the use of proxy for quota-based regulation: a case of homegeneous producers"
+#| label: fig-illust-homogeneous
+#| fig-cap: "Illustration of profit loss due to the use of proxy for quota-based regulation: a case of homogeneous producers"
 #| warning: false
@@
 
-@fig-trading-profit-illustration illustrates the impact of allowing for trading proxy quota using the case of two homogeneous farmers illustrated in @fig-illust-homegeneous.
+@fig-trading-profit-illustration illustrates the impact of allowing for trading proxy quota using the case of two homogeneous farmers illustrated in @fig-illust-homogeneous.
 In this illustration, the same water quota of 7 is allocated for both farmers under the water-based systems.
@@
 Under the proxy-base quota system, proxy quota of 7 is allocated for both farmers, but the effective water quota for farmers A and B are 4 and 7, respectively.
-Once trading of proxy quota is alllowed, farmer A would buy `r farmer_A_purchase` proxy quota from farmer B.
-At these production levels, the marginal profit of quota (not water) are equated acros the farmers and no further transfer between them would happen.
+Once trading of proxy quota is allowed, farmer A would buy `r farmer_A_purchase` proxy quota from farmer B.
+At these production levels, the marginal profit of quota (not water) are equated across the farmers and no further transfer between them would happen.
 Trading of proxy quota improves the overall profit to `r profit_after_trade_proxy` $/acre from `r profit_before_trade_quota` $/acre.
@@
 In other words, to achieve a certain water use goal, water-quota trading is always to more cost-effective than proxy-quota trading.
-Under water-quota trading, the margial profit of water is equalized across the farmers, which is a necessary condition to achieve the highest profit for a given level of total water use.
-Under proxy-quota trading, the marginal profit of proxy is equalized across the farmers, not the margial profit of water (See Appendix ...
+Under water-quota trading, the marginal profit of water is equalized across the farmers, which is a necessary condition to achieve the highest profit for a given level of total water use.
+Under proxy-quota trading, the marginal profit of proxy is equalized across the farmers, not the marginal profit of water (See Appendix ...
 for a mathematical proof).
@@
 
-@fig-trading-profit presents the simualtion results of proxy-quota and water-quota trading systems added to @fig-profit-quota-water-het.
-As you can see at all levels of production heterogeneity levels and the degres of measurement errors, proxy-quota and water-quota trading systems perform almost identical at all levels of realized water use (water-quota trading is always slightly better than proxy-quota trading as explained earlier).
+@fig-trading-profit presents the simulation results of proxy-quota and water-quota trading systems added to @fig-profit-quota-water-het.
+As you can see at all levels of production heterogeneity levels and the degree of measurement errors, proxy-quota and water-quota trading systems perform almost identical at all levels of realized water use (water-quota trading is always slightly better than proxy-quota trading as explained earlier).
 Not surprisingly, the benefit of allowing for trading is greater when the degree of measurement errors is larger.
@@
 If farmers make just as much profit under proxy-based regulation compared to water-based regulation, then the cumulative probability line would be a vertical line at 1.
-For example, under the high degree of measurement error and medium heterogenenity scenario, some farmers would make about the half of what they would make under the water quota system.
-At the lower end of the distribution are farmers who would be constrained severely by water quota, but whose water use estiamtes are much higher than their actual water use.
-At the higher end of the distribution are farmers who would be constrained by water quota, but whose water use estiamtes are much lower than their actual water use.
+For example, under the high degree of measurement error and medium heterogeneity scenario, some farmers would make about the half of what they would make under the water quota system.
+At the lower end of the distribution are farmers who would be constrained severely by water quota, but whose water use estimates are much higher than their actual water use.
+At the higher end of the distribution are farmers who would be constrained by water quota, but whose water use estimates are much lower than their actual water use.
 Famres who suffer significantly under the quota system can develop strong dissatisfaction of the quota-based regulation system, which in turn may lead to installing water meter themselves.
 If they discover the over-estimation of their water use, they may appeal to legal actions against the administrator for their unfair treatment.
-Allowind quota trading greatly diminishes the distributional inequality, though not completely.
+Allowing quota trading greatly diminishes the distributional inequality, though not completely.
 This is because unfortunate farmers who suffered from over-estimation of their water use can now at least purchase proxy quota to increase their production level.

### 2024-11-13 Writing/manuscript_typst.tex
minor edits

@@
 
-We now look at simple two-farm examles to build intuition behind the
+We now look at simple two-farm examples to build intuition behind the
 profit loss due to the use of proxy quota in place of water quota.
-Figure~\ref{fig-illust-homegeneous} presents a case with two homegeneous
+Figure~\ref{fig-illust-homogeneous} presents a case with two homogeneous
 farmers under water and proxy quota. The red dotted lines indicate the
@@
 and 10 inches for farmer A and B, respectively. Both farmers use their
-allocated amout of water. Under both proxy and water quota systems, the
+allocated amount of water. Under both proxy and water quota systems, the
 total water use is 14 inches. Farmer B makes 29.9 less under the water
@@
 system. This comes from an important nature of crop production with
-respsect to water: declining marginal impact of water on crop yield. As
+respect to water: declining marginal impact of water on crop yield. As
 can be seen in the profit-water relationship, removing an inch of water
-from 6 inches has much larger negative impact compared to revmoing an
+from 6 inches has much larger negative impact compared to removing an
 inch of water from 10 inches.
@@
 
-\caption{\label{fig-illust-homegeneous}Illustration of profit loss due
-to the use of proxy for quota-based regulation: a case of homegeneous
+\caption{\label{fig-illust-homogeneous}Illustration of profit loss due
+to the use of proxy for quota-based regulation: a case of homogeneous
 producers}
@@
 allowing for trading proxy quota using the case of two homogeneous
-farmers illustrated in Figure~\ref{fig-illust-homegeneous}. In this
+farmers illustrated in Figure~\ref{fig-illust-homogeneous}. In this
 illustration, the same water quota of 7 is allocated for both farmers
@@
 farmers, but the effective water quota for farmers A and B are 4 and 7,
-respectively. Once trading of proxy quota is alllowed, farmer A would
-buy 1.85 proxy quota from farmer B. At these production levels, the
-marginal profit of quota (not water) are equated acros the farmers and
-no further transfer between them would happen. Trading of proxy quota
+respectively. Once trading of proxy quota is allowed, farmer A would buy
+1.85 proxy quota from farmer B. At these production levels, the marginal
+profit of quota (not water) are equated across the farmers and no
+further transfer between them would happen. Trading of proxy quota
 improves the overall profit to 920.08 \$/acre from 831.94 \$/acre.
@@
 water-quota trading is always to more cost-effective than proxy-quota
-trading. Under water-quota trading, the margial profit of water is
+trading. Under water-quota trading, the marginal profit of water is
 equalized across the farmers, which is a necessary condition to achieve
@@
 proxy-quota trading, the marginal profit of proxy is equalized across
-the farmers, not the margial profit of water (See Appendix \ldots{} for
+the farmers, not the marginal profit of water (See Appendix \ldots{} for
 a mathematical proof). However, it is worth emphasizing that the
@@
 
-Figure~\ref{fig-trading-profit} presents the simualtion results of
+Figure~\ref{fig-trading-profit} presents the simulation results of
 proxy-quota and water-quota trading systems added to
 Figure~\ref{fig-profit-quota-water-het}. As you can see at all levels of
-production heterogeneity levels and the degres of measurement errors,
+production heterogeneity levels and the degree of measurement errors,
 proxy-quota and water-quota trading systems perform almost identical at
@@
 example, under the high degree of measurement error and medium
-heterogenenity scenario, some farmers would make about the half of what
+heterogeneity scenario, some farmers would make about the half of what
 they would make under the water quota system. At the lower end of the
 distribution are farmers who would be constrained severely by water
-quota, but whose water use estiamtes are much higher than their actual
+quota, but whose water use estimates are much higher than their actual
 water use. At the higher end of the distribution are farmers who would
-be constrained by water quota, but whose water use estiamtes are much
+be constrained by water quota, but whose water use estimates are much
 lower than their actual water use. Famres who suffer significantly under
@@
 they may appeal to legal actions against the administrator for their
-unfair treatment. Allowind quota trading greatly diminishes the
+unfair treatment. Allowing quota trading greatly diminishes the
 distributional inequality, though not completely. This is because
